---
title: "H3K27ac CATD DEPGS Analysis"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: false
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(gprofiler2)
library(DESeq2)
library(ggplot2)
library(clusterProfiler)
library(biomaRt)
library(ReactomePA)
library(DOSE)
options(connectionObserver = NULL)
library(org.Mm.eg.db)
library(tximport)
library(ggsci)
library(pheatmap)
library(genefilter)
library(RColorBrewer)
library(GO.db)
library(topGO)
library(dplyr)
library(gage)
library(pathview)
library(WGCNA)
library(tidyr)
library(enrichplot)
library(ggnewscale)
library(SPIA)
library(ggpubr)
library(apeglm)
library(GOSemSim)
library(edgeR)
library(tweeDEseqCountData)
library(statmod)
library(org.Mm.eg.db)
library(tidyverse)
library(pheatmap)
library(gplots)
library(Mus.musculus)
library(Glimma)
library(RColorBrewer)
library(clusterProfiler)
library(ReactomePA)
library(enrichplot)
library(ggnewscale)
library(knitr)
library(tables)
library(vidger)
library(kableExtra)
library(regionReport)

#remotes::install_github("YuLab-SMU/clusterProfiler") 

```



# DESeq2 Analysis for H3K27ac
## Loading in required files -- Comes from analysis/index3.Rmd

Building DESeq2 input files from peak count matrix generated by counting number of reads from BAM files that fell into significantly called peaks and then mapping the chromosomal locations to the respective gene.


```{r DESeq2 Build, message=FALSE, warning=FALSE, include=FALSE}
## Run DEeq2 from Matrix output using Stringtie to compare all groups

setwd("/home/avm27/Documents/Raw_Sequencing_Data/BrainRegionMicroglia/RegionalMicroglialTranscriptomicsandEpigenomics")
basepath="/home/avm27/Documents/Raw_Sequencing_Data/BrainRegionMicroglia/RegionalMicroglialTranscriptomicsandEpigenomics/"
colData <- read.csv(paste0(basepath, "data/CATD_DESeq_Data/sample_info_K27ac.csv"), sep = ",", row.names = 1)

countData <-as.matrix(read.csv(paste0(basepath, "data/CATD_DESeq_Data/peak_count_matrix_CATD_Final_K27ac.csv"), row.names = "gene_id"))

sum(is.na(countData))
colnames(countData)
rownames(colData)
all(rownames(colData) %in% colnames(countData))
countData <- countData[, rownames(colData)]
all(rownames(colData) == colnames(countData))

```


```{r DESeq2 Analysis, echo=FALSE, message=FALSE, warning=FALSE}

dds <- DESeqDataSetFromMatrix(countData = countData, colData = colData, design = ~condition)
dds2 <- DESeqDataSetFromMatrix(countData = countData, colData = colData, design = ~condition)
dds3 <- DESeqDataSetFromMatrix(countData = countData, colData = colData, design = ~condition)
dds4 <- DESeqDataSetFromMatrix(countData = countData, colData = colData, design = ~condition)
dds5 <- DESeqDataSetFromMatrix(countData = countData, colData = colData, design = ~condition)

## Filter out counts less than 10 across the rows
keep <- rowSums(counts(dds)) >= 35
dds <- dds[keep,]

keep2 <- rowSums(counts(dds2)) >= 35
dds2 <- dds2[keep2,]

keep3 <- rowSums(counts(dds3)) >= 35
dds3 <- dds3[keep3,]

keep4 <- rowSums(counts(dds4)) >= 35
dds4 <- dds4[keep4,]

keep5 <- rowSums(counts(dds5)) >= 35
dds5 <- dds5[keep5,]



dds$condition <- relevel(dds$condition, ref = "Cortex")
dds <- DESeq(dds)

dds2$condition <- relevel(dds2$condition, ref = "Hippocampus")
dds2 <- DESeq(dds2)

dds3$condition <- relevel(dds3$condition, ref = "Striatum")
dds3 <- DESeq(dds3)

dds4$condition <- relevel(dds4$condition, ref = "PreFrontalCortex")
dds4 <- DESeq(dds4)

dds5$condition <- relevel(dds5$condition, ref = "VTA")
dds5 <- DESeq(dds5)
```

# Plot Estimates from Results

```{r Results, echo=FALSE, results='asis'}

res1 <- results(dds, contrast = c("condition", "Hippocampus", "Cortex"))
res2 <- results(dds, contrast = c("condition", "PreFrontalCortex", "Cortex"))
res3 <- results(dds4, contrast = c("condition", "Striatum", "PreFrontalCortex"))
res4 <- results(dds, contrast = c("condition", "Striatum", "Cortex"))
res5 <- results(dds3, contrast = c("condition", "Hippocampus", "Striatum"))
res6 <- results(dds5, contrast = c("condition", "Hippocampus", "VTA"))
res7 <- results(dds5, contrast = c("condition", "Striatum", "VTA"))
res8 <- results(dds5, contrast = c("condition", "PreFrontalCortex", "VTA"))
res9 <- results(dds5, contrast = c("condition", "Cortex", "VTA"))
res10 <- results(dds4, contrast = c("condition", "Hippocampus", "PreFrontalCortex"))


#summary(res1)
#summary(res2)
#summary(res3)
#summary(res4)
#summary(res5)
#summary(res6)
#summary(res7)
#summary(res8)
#summary(res9)
#summary(res10)

```

# Annotate Results Files


```{r Annotate Results, message=FALSE, warning=FALSE, include=FALSE, results='asis'}
## Make new rownames file and split based on pipe from dds file

library(dplyr)
library(tidyr)

# Create a list to store the result objects
result_list <- list()

# Define the number of results
num_results <- 10

# Loop through each result
for (i in 1:num_results) {
  # Get the result object name
  result_name <- paste0("res", i)
  
  # Get the DESeq2 result object
  result_obj <- get(result_name)
  
  # Add symbol column
  result_obj$symbol <- row.names(result_obj)
  
  # Map symbol to gene description
  result_obj$description <- mapIds(x = org.Mm.eg.db,
                                    keys = result_obj$symbol,
                                    column = "GENENAME",
                                    keytype = "SYMBOL",
                                    multiVals = "first")
  
  # Add ENTREZ ID
  result_obj$entrez <- mapIds(x = org.Mm.eg.db,
                               keys = result_obj$symbol,
                               column = "ENTREZID",
                               keytype = "SYMBOL",
                               multiVals = "first")
  
  # Add ENSEMBL ID
  result_obj$ensembl <- mapIds(x = org.Mm.eg.db,
                                keys = result_obj$entrez,
                                column = "ENSEMBL",
                                keytype = "ENTREZID",
                                multiVals = "first")
  
  # Store the result object in the list
  result_list[[i]] <- result_obj

      # Write out the subsetted result object to a variable with name results_sig_i
  assign(paste0("res", i), result_obj)
}
```


After annotation results are subset to only view the significantly differentially expressed peaks in genes with an adjusted p-value \> 0.05.

```{r Subset Significant Results, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
## Subset for significant genes only

# Define the number of results
num_results <- 10

# Create a list to store the subsetted result objects
results_sig_list <- list()

# Loop through each result object
for (i in 1:num_results) {
  # Get the result object name
  result_name <- paste0("res", i)
  
  # Get the DESeq2 result object
  result_obj <- get(result_name)
  
  # Subset the result object based on padj < 0.05
  subset_result <- subset(result_obj, padj < 0.05)
  
  # Check if there are any significant results
  if (nrow(subset_result) > 0) {
    # Store the subsetted result object in the list
    results_sig_list[[i]] <- subset_result
    
    # Write out the subsetted result object to a variable with name results_sig_i
    assign(paste0("results_sig", i), subset_result)
  }
}


```

```{r Save Significant Results, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}

#write_csv((as.data.frame(results_sig1)), paste0(basepath, "output/CATD_DEPGs/H3K27ac/Sig_Res_DEPGs_K27ac_HPP_vs_CTX.csv"))
#write_csv((as.data.frame(results_sig2)), paste0(basepath, "output/CATD_DEPGs/H3K27ac/Sig_Res_DEPGs_K27ac_PFC_vs_CTX.csv"))
#write_csv((as.data.frame(results_sig3)), paste0(basepath, "output/CATD_DEPGs/H3K27ac/Sig_Res_DEPGs_K27ac_STR_vs_PFC.csv"))
#write_csv((as.data.frame(results_sig4)), paste0(basepath, "output/CATD_DEPGs/H3K27ac/Sig_Res_DEPGs_K27ac_STR_vs_CTX.csv"))
#write_csv((as.data.frame(results_sig5)), paste0(basepath, "output/CATD_DEPGs/H3K27ac/Sig_Res_DEPGs_K27ac_HPP_vs_STR.csv"))
#write_csv((as.data.frame(results_sig6)), paste0(basepath, "output/CATD_DEPGs/H3K27ac/Sig_Res_DEPGs_K27ac_HPP_vs_VTA.csv"))
#write_csv((as.data.frame(results_sig7)), paste0(basepath, "output/CATD_DEPGs/H3K27ac/Sig_Res_DEPGs_K27ac_STR_vs_VTA.csv"))
#write_csv((as.data.frame(results_sig8)), paste0(basepath, "output/CATD_DEPGs/H3K27ac/Sig_Res_DEPGs_K27ac_PFC_vs_VTA.csv"))
#write_csv((as.data.frame(results_sig9)), paste0(basepath, "output/CATD_DEPGs/H3K27ac/Sig_Res_DEPGs_K27ac_CTX_vs_VTA.csv"))
#write_csv((as.data.frame(results_sig10)), paste0(basepath, "output/CATD_DEPGs/H3K27ac/Sig_Res_DEPGs_K27ac_HPP_vs_PFC.csv"))
          
```

```{r eval=FALSE, include=FALSE}
# Not run, but useful for individual results comparisons
print_output <- function(output, cex = 0.7) {
  tmp <- capture.output(output)
  plot.new()
  text(0, 1, paste(tmp, collapse='\n'), adj = c(0,1), family = 'mono', cex = cex)
  box()
}

#pdf(paste0(basepath, "output/CATD_DEPGs/H3K27ac/SummaryTables_ResSigDEPGs_H3K27ac_Final.pdf"))
print_output(c("Results Sig 1: Significant H3K27ac DEPGs Hippocampus vs Cortex", summary(results_sig1, alpha = 0.05)))
print_output(c("Results Sig 2: Significant H3K27ac DEPGs PreFrontalCortex vs Cortex", summary(results_sig1, alpha = 0.05)))
print_output(c("Results Sig 3: Significant H3K27ac DEPGs Striatum vs PreFrontalCortex", summary(results_sig3, alpha = 0.05)))
print_output(c("Results Sig 4: Significant H3K27ac DEPGs Striatum vs Cortex", summary(results_sig4, alpha = 0.05)))
print_output(c("Results Sig 5: Significant H3K27ac DEPGs Hippocampus vs Striatum", summary(results_sig5, alpha = 0.05)))
print_output(c("Results Sig 6: Significant H3K27ac DEPGs Hippocampus vs VTA", summary(results_sig6, alpha = 0.05)))
print_output(c("Results Sig 7: Significant H3K27ac DEPGs Striatum vs VTA", summary(results_sig7, alpha = 0.05)))
print_output(c("Results Sig 8: Significant H3K27ac DEPGs PreFrontalCortex vs VTA", summary(results_sig8, alpha = 0.05)))
print_output(c("Results Sig 9: Significant H3K27ac DEPGs Cortex vs VTA", summary(results_sig9, alpha = 0.05)))
print_output(c("Results Sig 10: Significant H3K27ac DEPGs Hippocampus vs PreFrontalCortex", summary(results_sig10, alpha = 0.05)))
#dev.off()

```

## Write all Results to a CSV for Supplement

```{r}

# Define the number of results
num_results <- 10

# Create a list to store the subsetted and filtered result objects
results_sig_list <- list()

# Loop through each result object
for (i in 1:num_results) {
  # Get the result object name
  result_name <- paste0("res", i)
  
  # Get the DESeq2 result object
  result_obj <- get(result_name)
  
  # Subset the result object based on padj < 0.05
  subset_result <- subset(result_obj, padj < 0.05)
  
  # Check if there are any significant results
  if (nrow(subset_result) > 0) {
    # Sort the subsetted result object by log2FoldChange in increasing order
    sorted_result <- subset_result[order(subset_result$log2FoldChange), ]
    
    # Get the bottom 50 (smallest log2FoldChange) and top 50 (largest log2FoldChange)
    bottom50 <- sorted_result
    top50 <- sorted_result
    
    # Combine the top 50 and bottom 50 rows
    combined_result <- rbind(top50, bottom50)
    
    # Add a new column "result" with the name of the result file
    combined_result$result <- paste0("results_sig", i)
    
    # Store the combined result object in the list
    results_sig_list[[i]] <- combined_result
    
    # Write out the combined result object to a variable with name results_sig_i
    assign(paste0("results_sig", i), combined_result)

  } else {
    # If no significant results, store an empty data frame
    results_sig_list[[i]] <- data.frame()
  }
}

# Filter out empty data frames
filtered_results_sig_list <- results_sig_list[sapply(results_sig_list, nrow) > 0]

# Combining all non-empty results_sig objects into a single data frame (optional)
if (length(filtered_results_sig_list) > 0) {
  all_combined_results <- do.call(rbind, filtered_results_sig_list)
  
  # Assign the combined results to an environment variable if needed
  assign("env_variable_combined_results", all_combined_results)
}




sigres_coded <- c(
  results_sig1 = "HPP_vs_CTX_H3K27ac",
  results_sig2 = "PFC_vs_CTX_H3K27ac",
  results_sig3 = "STR_vs_PFC_H3K27ac",
  results_sig4 = "STR_vs_CTX_H3K27ac",
  results_sig5 = "HPP_vs_STR_H3K27ac",
  results_sig6 = "HPP_vs_VTA_H3K27ac",
  results_sig7 = "STR_vs_VTA_H3K27ac",
  results_sig8 = "PFC_vs_VTA_H3K27ac",
  results_sig9 = "CTX_vs_VTA_H3K27ac",
  results_sig10 = "HPP_vs_PFC_H3K27ac"
)



# after you build all_combined_results
if (exists("all_combined_results")) {
  all_combined_results$result <- ifelse(
    all_combined_results$result %in% names(sigres_coded),
    sigres_coded[all_combined_results$result],
    all_combined_results$result
  )
}

#write.csv(as.data.frame(all_combined_results), paste0(basepath, "output/CATD_DEPGs/H3K27ac/Merged_All_SignifcantResults_CATD_DEseq2_H3K27ac_BRMic.csv"), row.names = FALSE)


```


# Visualizing Differentially Deposited Peaks in Genes

## Matrices
```{r Matrix of Differentially Expressed Peaks in genes across groups, echo=FALSE, fig.height=12, fig.width=20, message=FALSE, warning=FALSE}

## Matrix Visualizaattion
x <- vsDEGMatrix(
    data = dds, padj = 0.05, d.factor = 'condition', 
    type = 'deseq', title = TRUE, legend = TRUE, grid = TRUE
)

#pdf(paste0(basepath, 'output/CATD_DEPGs/H3K27ac/DEGs_Flower_Matrix_BRMIC_CATD_K27ac_Experiment_05.pdf'))
x
#dev.off()

```

## UpsetPlots
```{r}
comparison_regions <- c(
  HPP_vs_CTX = "HPP_vs_CTX",
  PFC_vs_CTX = "PFC_vs_CTX",
  STR_vs_PFC = "STR_vs_PFC",
  STR_vs_CTX = "STR_vs_CTX",
  HPP_vs_STR = "HPP_vs_STR",
  HPP_vs_VTA = "HPP_vs_VTA",
  STR_vs_VTA = "STR_vs_VTA",
  PFC_vs_VTA = "PFC_vs_VTA",
  CTX_vs_VTA = "CTX_vs_VTA",
  HPP_vs_PFC = "HPP_vs_PFC"
)

get_up_genes <- function(res) {
  rownames(subset(res, padj < 0.05 & log2FoldChange > 0))
}

get_down_genes <- function(res) {
  rownames(subset(res, padj < 0.05 & log2FoldChange < 0))
}

deg_lists_up <- list(
  HPP_vs_CTX = get_up_genes(res1),
  PFC_vs_CTX  = get_up_genes(res2),
  STR_vs_PFC = get_up_genes(res3),
  STR_vs_CTX  = get_up_genes(res4),
  HPP_vs_STR = get_up_genes(res5),
  HPP_vs_VTA = get_up_genes(res6),
  STR_vs_VTA = get_up_genes(res7),
  PFC_vs_VTA = get_up_genes(res8),
  CTX_vs_VTA = get_up_genes(res9),
  HPP_vs_PFC = get_up_genes(res10)
)

deg_lists_down <- list(
  HPP_vs_CTX  = get_down_genes(res1),
  PFC_vs_CTX  = get_down_genes(res2),
  STR_vs_PFC = get_down_genes(res3),
  STR_vs_CTX  = get_down_genes(res4),
  HPP_vs_STR = get_down_genes(res5),
  HPP_vs_VTA = get_down_genes(res6),
  STR_vs_VTA = get_down_genes(res7),
  PFC_vs_VTA = get_down_genes(res8),
  CTX_vs_VTA = get_down_genes(res9),
  HPP_vs_PFC = get_down_genes(res10)
)

all_genes_up <- unique(unlist(deg_lists_up))
up_mat <- as.data.frame(sapply(deg_lists_up, function(g) all_genes_up %in% g))
rownames(up_mat) <- all_genes_up

all_genes_down <- unique(unlist(deg_lists_down))
down_mat <- as.data.frame(sapply(deg_lists_down, function(g) all_genes_down %in% g))
rownames(down_mat) <- all_genes_down

up_mat_tbl <- as_tibble(up_mat)
down_mat_tbl <- as_tibble(down_mat)

UpSetUpregulated <- upset(
  up_mat_tbl,
  min_size=15,
  intersect = colnames(up_mat_tbl),
  name = "Upregulated Genes",
  base_annotations = list("Intersection size" = intersection_size()),
  height_ratio = 0.5,
  width_ratio = 0.25
) +
  theme_bw(base_size = 4) +  
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 12),
    axis.text.y = element_text(size = 12),  
    plot.title = element_text(size = 16, face = "bold"),
    plot.subtitle = element_text(size = 14),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 13, face = "bold")
  ) +
  labs(
    title = "H3K27ac Enriched Genes Across Brain Regions",
    subtitle = "Significant enrichment of depositions in genes (padj < 0.05, log2FC > 0)",
    x = "Comparison",
    y = "Intersection Size"
  )



UpSetDownregulated <-upset(
  down_mat_tbl,
  min_size=15,
  intersect = colnames(down_mat_tbl),
  name = "Downregulated Genes",
  base_annotations = list("Intersection size" = intersection_size()),
  height_ratio = 1,
  width_ratio = 0.25
) +

  theme_bw(base_size = 4) + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 12),
    axis.text.y = element_text(size = 12),  
    plot.title = element_text(size = 16, face = "bold"),
    plot.subtitle = element_text(size = 14),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 13, face = "bold")
  ) +
  labs(
    title = "H3K27ac Depleted Genes Across Brain Regions",
    subtitle = "Significant depletion of depositions in genes (padj < 0.05, log2FC < 0)",
    x = "Comparison",
    y = "Intersection Size"
  )


#pdf(paste0(basepath,"output/CATD_DEPGs/H3K27ac/BRMic_Upset_K27ac_Upregulated_Downregulated_Final.pdf"), width = 8, height = 8)

UpSetUpregulated
UpSetDownregulated

#dev.off()
```

## Heatmaps {.tabset}
```{r PheatMap, echo=FALSE, message=FALSE, warning=FALSE}
# Load required packages
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggrepel)
library(RColorBrewer)
library(pheatmap)
library(DEGreport)
library(reshape2)

level_order <- c('Striatum', 'PreFrontalCorex', 'Hippocampus', 'VTA', 'Cortex') 

# Define custom colors for each condition
custom_colors <- c("Cortex" = "#FF9289", 
                   "Hippocampus" = "#FF8AFF", 
                   "PreFrontalCortex" = "#00DB98", 
                   "Striatum" = "#00CBFF", 
                   "VTA" = "#BEC100")

custom_colors <- c("CTX" = "#FF9289", 
                   "HPP" = "#FF8AFF", 
                   "PFC" = "#00DB98", 
                   "STR" = "#00CBFF", 
                   "VTA" = "#BEC100")

group_conditions <- function(condition) {
  ifelse(grepl("CTX", condition), "CTX",
         ifelse(grepl("HPP", condition), "HPP",
                ifelse(grepl("PFC", condition), "PFC",
                       ifelse(grepl("STR", condition), "STR",
                              ifelse(grepl("VTA", condition), "VTA", NA)))))
}

```

To generate the heatmaps we selected for any significant DEPGs with a L2FC \> 1.50 or an L2FC \< -1.50 with a L2FC Standard Error \< 1.00. We then plot these using a wards D correlation clustering method and generate both supervised and unsupervised clusters (by group). Rows are scaled based on a correlation z-score.

```{r}

ressig1 <- as.data.frame(results_sig1)
ressig2 <- as.data.frame(results_sig2)
ressig3 <- as.data.frame(results_sig3)
ressig4 <- as.data.frame(results_sig4)
ressig5 <- as.data.frame(results_sig5)
ressig6 <- as.data.frame(results_sig6)
ressig7 <- as.data.frame(results_sig7)
ressig8 <- as.data.frame(results_sig8)
ressig9 <- as.data.frame(results_sig9)
ressig10 <- as.data.frame(results_sig10)



ressig1$Comparison <- "HPP_vs_CTX"
ressig2$Comparison <- "PFC_vs_CTX"
ressig3$Comparison <- "STR_vs_PFC"
ressig4$Comparison <- "STR_vs_CTX"
ressig5$Comparison <- "HPP_vs_STR"
ressig6$Comparison <- "HPP_vs_VTA"
ressig7$Comparison <- "STR_vs_VTA"
ressig8$Comparison <- "PFC_vs_VTA"
ressig9$Comparison <- "CTX_vs_VTA"
ressig10$Comparison <- "HPP_vs_PFC"




ressig1_highlfc_pos <- ressig1[ressig1$log2FoldChange >= 1.50, ]
ressig1_highlfc_neg <- ressig1[ressig1$log2FoldChange <= -1.50, ]
ressig2_highlfc_pos <- ressig2[ressig2$log2FoldChange >= 1.50, ]
ressig2_highlfc_neg <- ressig2[ressig2$log2FoldChange <= -1.50, ]
ressig3_highlfc_pos <- ressig3[ressig3$log2FoldChange >= 1.50, ]
ressig3_highlfc_neg <- ressig3[ressig3$log2FoldChange <= -1.50, ]
ressig4_highlfc_pos <- ressig4[ressig4$log2FoldChange >= 1.50, ]
ressig4_highlfc_neg <- ressig4[ressig4$log2FoldChange <= -1.50, ]
ressig5_highlfc_pos <- ressig5[ressig5$log2FoldChange >= 1.50, ]
ressig5_highlfc_neg <- ressig5[ressig5$log2FoldChange <= -1.50, ]
ressig6_highlfc_pos <- ressig6[ressig6$log2FoldChange >= 1.50, ]
ressig6_highlfc_neg <- ressig6[ressig6$log2FoldChange <= -1.50, ]
ressig7_highlfc_pos <- ressig7[ressig7$log2FoldChange >= 1.50, ]
ressig7_highlfc_neg <- ressig7[ressig7$log2FoldChange <= -1.50, ]
ressig8_highlfc_pos <- ressig8[ressig8$log2FoldChange >= 1.50, ]
ressig8_highlfc_neg <- ressig8[ressig8$log2FoldChange <= -1.50, ]
ressig9_highlfc_pos <- ressig9[ressig9$log2FoldChange >= 1.50, ]
ressig9_highlfc_neg <- ressig9[ressig9$log2FoldChange <= -1.50, ]
ressig10_highlfc_pos <- ressig10[ressig10$log2FoldChange >= 1.50, ]
ressig10_highlfc_neg <- ressig10[ressig10$log2FoldChange <= -1.50, ]

temp_sigdegshm <- rbind(ressig1_highlfc_pos, ressig1_highlfc_neg)
temp_sigdegshm2 <- rbind(temp_sigdegshm, ressig2_highlfc_pos)
temp_sigdegshm3 <- rbind(temp_sigdegshm2, ressig2_highlfc_neg)
temp_sigdegshm4 <- rbind(temp_sigdegshm3, ressig3_highlfc_pos)
temp_sigdegshm5 <- rbind(temp_sigdegshm4, ressig3_highlfc_neg)
temp_sigdegshm6 <- rbind(temp_sigdegshm5, ressig4_highlfc_pos)
temp_sigdegshm7 <- rbind(temp_sigdegshm6, ressig4_highlfc_neg)
temp_sigdegshm8 <- rbind(temp_sigdegshm7, ressig5_highlfc_pos)
temp_sigdegshm9 <- rbind(temp_sigdegshm8, ressig5_highlfc_neg)
temp_sigdegshm10 <- rbind(temp_sigdegshm9, ressig6_highlfc_pos)
temp_sigdegshm11 <- rbind(temp_sigdegshm10, ressig6_highlfc_neg)
temp_sigdegshm12 <- rbind(temp_sigdegshm11, ressig7_highlfc_pos)
temp_sigdegshm13 <- rbind(temp_sigdegshm12, ressig7_highlfc_neg)
temp_sigdegshm14 <- rbind(temp_sigdegshm13, ressig8_highlfc_pos)
temp_sigdegshm15 <- rbind(temp_sigdegshm14, ressig8_highlfc_neg)
temp_sigdegshm16 <- rbind(temp_sigdegshm15, ressig9_highlfc_pos)
temp_sigdegshm17 <- rbind(temp_sigdegshm16, ressig9_highlfc_neg)
temp_sigdegshm18 <- rbind(temp_sigdegshm17, ressig10_highlfc_pos)
temp_sigdegshm19 <- rbind(temp_sigdegshm18, ressig10_highlfc_neg)

temp_sigdegshm20 <- temp_sigdegshm19[temp_sigdegshm19$lfcSE <= 1.00, ]

temp_sigdegshm21 <- temp_sigdegshm20[order(temp_sigdegshm20$log2FoldChange, decreasing = TRUE), ]

library(dplyr)
library(conflicted)
library(viridis)

ddsMat_rlog <- rlog(dds, blind = FALSE)


dup_rows <- duplicated(temp_sigdegshm21$symbol)
sum(duplicated(temp_sigdegshm21$symbol))
data_dedup <- temp_sigdegshm21[!dup_rows, ]

rows <- rownames(data_dedup)

select <- order(rowMeans(counts(dds, normalized = TRUE)),
  decreasing = TRUE
)

mat <- assay(ddsMat_rlog)[select, ]

data_mod <- mat[rownames(mat) %in% rows, ]

matrownames_data_mod <- data.frame(rownames(data_mod))

samples <- as.tibble(read.csv(paste0(basepath, "data/CATD_DESeq_Data/sample_info_K27ac.csv"), sep = ","))

annot_col <- samples %>%
  column_to_rownames("samplename") %>%
  as.data.frame()

ann_colors <- list(
  condition = as.factor(c(PreFrontalCortex = "slateblue2", Striatum = "limegreen", VTA = "violetred2", Cortex = "lightblue3", Hippocampus = "pink")),
  Group = as.factor(c(PreFrontalCortex = "slateblue2", Striatum = "limegreen", VTA = "violetred2", Cortex = "lightblue3", Hippocampus = "pink"))
)


```

### Unsupervised Clustering and Condensed

```{r Filter Heatmaps by DEGs3, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
pheatmap::pheatmap(
  mat = data_mod,
  color = colorRampPalette(rev(brewer.pal(11, "RdYlBu")))(155),
  scale = "row", 
  annotation_col = annot_col,
  fontsize = 8,
  show_colnames = F,
  cluster_rows = T,
  cluster_cols = T,
  annotation_legend = T,
  legend = T,
  show_rownames = T,
  clustering_distance_rows = "correlation",
  clustering_method = "ward.D",
  main = "Heatmap of Significant DEPGs -- K27ac --Unsupervised and Condensed",
  cluster_row_slices = TRUE,
  show_row_dend = FALSE,
  gaps_col = c(2, 4,6,8),
  cutree_rows = 4,
  cutree_cols = 4,
  treeheight_row = 15,
  treeheight_col = 10,
  #filename = paste0(basepath, "output/CATD_DEPGs/H3K27ac/K27ac_MICBRCATD_Heatmap_DEPGs_Final--UNSupervisedcluster--Condensed---FORPAPER.pdf"),
  legend_labels = c("PreFrontalCortex", "Striatum", "VTA", "Cortex", "Hippocampus"),
)

```

### Supervised Clustering and Condensed

```{r Filter Heatmaps by DEGs3, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
pheatmap::pheatmap(
  mat = data_mod,
  color = colorRampPalette(rev(brewer.pal(11, "RdYlBu")))(155),
  scale = "row",
  annotation_col = annot_col,
  fontsize = 8,
  show_colnames = F,
  cluster_rows = T,
  cluster_cols = F,
  annotation_legend = T,
  legend = T,
  show_rownames = T,
  clustering_distance_rows = "correlation",
  clustering_method = "ward.D",
  main = "Heatmap of Significant DEPGs -- K27ac --Unsupervised and Condensed",
  cluster_row_slices = TRUE,
  show_row_dend = FALSE,
  gaps_col = c(2, 4,6,8),
  cutree_rows = 4,
  cutree_cols = 4,
  treeheight_row = 15,
  treeheight_col = 10,
  #filename = paste0(basepath, "output/CATD_DEPGs/H3K27ac/K27ac_MICBRCATD_Heatmap_DEPGs_Final--Supervisedcluster--Condensed---FORPAPER.pdf"),
  legend_labels = c("PreFrontalCortex", "Striatum", "VTA", "Cortex", "Hippocampus"),
)

```

## Gene Ontology Analysis

To generate GO analysis we first created a background of deposition of peaks in genes using any genes containing peaks that met the original DESEQ2 filtering criteria and had a mappable entrez ID. This generates the necessary background to ensure that we are not just detecting microlgial pathways as we are utilizing this specific cell type. We then filter our genes that have L2FC \< 0 or L2FC \> 0 to determine directionality of the affected GO pathways. GO enrich is then used to conduct the pathway analysis utiziling the entrez IDs as inputs and an "FDR" multiple testing correction.

### Prepare DEPGs and Generate GO terms

```{r}

# Generate Background for GO

length(dds)
length(res1$entrez)

background_mm10 <- subset(res1, is.na(entrez) == FALSE)
gene_matrix_background <- unique(sort(background_mm10$entrez))

# Remove any genes that do not have any entrez identifiers

results_sig_entrez <- subset(results_sig1, is.na(entrez) == FALSE)
results_sig_entrez2 <- subset(results_sig2, is.na(entrez) == FALSE)
results_sig_entrez3 <- subset(results_sig3, is.na(entrez) == FALSE)
results_sig_entrez4 <- subset(results_sig4, is.na(entrez) == FALSE)
results_sig_entrez5 <- subset(results_sig5, is.na(entrez) == FALSE)
results_sig_entrez6 <- subset(results_sig6, is.na(entrez) == FALSE)
results_sig_entrez7 <- subset(results_sig7, is.na(entrez) == FALSE)
results_sig_entrez8 <- subset(results_sig8, is.na(entrez) == FALSE)
results_sig_entrez9 <- subset(results_sig9, is.na(entrez) == FALSE)
results_sig_entrez10 <- subset(results_sig10, is.na(entrez) == FALSE)



# Create a matrix of gene log2 fold changes
gene_matrix <- results_sig_entrez$log2FoldChange
gene_matrix2 <- results_sig_entrez2$log2FoldChange
gene_matrix3 <- results_sig_entrez3$log2FoldChange
gene_matrix4 <- results_sig_entrez4$log2FoldChange
gene_matrix5 <- results_sig_entrez5$log2FoldChange
gene_matrix6 <- results_sig_entrez6$log2FoldChange
gene_matrix7 <- results_sig_entrez7$log2FoldChange
gene_matrix8 <- results_sig_entrez8$log2FoldChange
gene_matrix9 <- results_sig_entrez9$log2FoldChange
gene_matrix10 <- results_sig_entrez10$log2FoldChange


# Add the entrezID's as names for each logFC entry
names(gene_matrix) <- results_sig_entrez$entrez
names(gene_matrix2) <- results_sig_entrez2$entrez
names(gene_matrix3) <- results_sig_entrez3$entrez
names(gene_matrix4) <- results_sig_entrez4$entrez
names(gene_matrix5) <- results_sig_entrez5$entrez
names(gene_matrix6) <- results_sig_entrez6$entrez
names(gene_matrix7) <- results_sig_entrez7$entrez
names(gene_matrix8) <- results_sig_entrez8$entrez
names(gene_matrix9) <- results_sig_entrez9$entrez
names(gene_matrix10) <- results_sig_entrez10$entrez



# Pull only the  Highly Enriched samples  (<1.5 LFC)

gene_matrix_enrich <- gene_matrix[which(gene_matrix > 0)]
gene_matrix_enrich2 <- gene_matrix2[which(gene_matrix2 > 0)]
gene_matrix_enrich3 <- gene_matrix3[which(gene_matrix3 > 0)]
gene_matrix_enrich4 <- gene_matrix4[which(gene_matrix4 > 0)]
gene_matrix_enrich5 <- gene_matrix5[which(gene_matrix5 > 0)]
gene_matrix_enrich6 <- gene_matrix6[which(gene_matrix6 > 0)]
gene_matrix_enrich7 <- gene_matrix7[which(gene_matrix7 > 0)]
gene_matrix_enrich8 <- gene_matrix8[which(gene_matrix8 > 0)]
gene_matrix_enrich9 <- gene_matrix9[which(gene_matrix9 > 0)]
gene_matrix_enrich10 <- gene_matrix10[which(gene_matrix10 > 0)]
gene_matrix_enrich11 <- gene_matrix[which(gene_matrix < 0)]
gene_matrix_enrich12 <- gene_matrix2[which(gene_matrix2 < 0)]
gene_matrix_enrich13 <- gene_matrix3[which(gene_matrix3 < 0)]
gene_matrix_enrich14 <- gene_matrix4[which(gene_matrix4 < 0)]
gene_matrix_enrich15 <- gene_matrix5[which(gene_matrix5 < 0)]
gene_matrix_enrich16 <- gene_matrix6[which(gene_matrix6 < 0)]
gene_matrix_enrich17 <- gene_matrix7[which(gene_matrix7 < 0)]
gene_matrix_enrich18 <- gene_matrix8[which(gene_matrix8 < 0)]
gene_matrix_enrich19 <- gene_matrix9[which(gene_matrix9 < 0)]
gene_matrix_enrich20 <- gene_matrix10[which(gene_matrix10 < 0)]


go_enrich1 <- enrichGO(gene = names(gene_matrix_enrich),
                      OrgDb = 'org.Mm.eg.db', 
                      readable = T,
                      universe = gene_matrix_background,
                      ont = "ALL",
                      pAdjustMethod = "fdr",
                      pvalueCutoff = 0.05, 
                      qvalueCutoff = 0.05)

go_enrich2 <- enrichGO(gene = names(gene_matrix_enrich2),
                      OrgDb = 'org.Mm.eg.db', 
                      readable = T,
                      universe = gene_matrix_background,
                      ont = "ALL",
                      pAdjustMethod = "fdr",
                      pvalueCutoff = 0.05, 
                      qvalueCutoff = 0.05)

go_enrich3 <- enrichGO(gene = names(gene_matrix_enrich3),
                      OrgDb = 'org.Mm.eg.db', 
                      readable = T,
                      universe = gene_matrix_background,
                      ont = "ALL",
                      pAdjustMethod = "fdr",
                      pvalueCutoff = 0.05, 
                      qvalueCutoff = 0.05)

go_enrich4 <- enrichGO(gene = names(gene_matrix_enrich4),
                      OrgDb = 'org.Mm.eg.db', 
                      readable = T,
                      universe = gene_matrix_background,
                      ont = "ALL",
                      pAdjustMethod = "fdr",
                      pvalueCutoff = 0.05, 
                      qvalueCutoff = 0.05)

go_enrich5 <- enrichGO(gene = names(gene_matrix_enrich5),
                      OrgDb = 'org.Mm.eg.db', 
                      readable = T,
                      universe = gene_matrix_background,
                      ont = "ALL",
                      pAdjustMethod = "fdr",
                      pvalueCutoff = 0.05, 
                      qvalueCutoff = 0.05)

go_enrich6 <- enrichGO(gene = names(gene_matrix_enrich6),
                      OrgDb = 'org.Mm.eg.db', 
                      readable = T,
                      universe = gene_matrix_background,
                      ont = "ALL",
                      pAdjustMethod = "fdr",
                      pvalueCutoff = 0.05, 
                      qvalueCutoff = 0.05)

go_enrich7 <- enrichGO(gene = names(gene_matrix_enrich7),
                      OrgDb = 'org.Mm.eg.db', 
                      readable = T,
                      universe = gene_matrix_background,
                      ont = "ALL",
                      pAdjustMethod = "fdr",
                      pvalueCutoff = 0.05, 
                     qvalueCutoff = 0.05)

go_enrich8 <- enrichGO(gene = names(gene_matrix_enrich8),
                      OrgDb = 'org.Mm.eg.db', 
                      readable = T,
                      universe = gene_matrix_background,
                      ont = "ALL",
                      pAdjustMethod = "fdr",
                      pvalueCutoff = 0.05, 
                      qvalueCutoff = 0.05)

go_enrich9 <- enrichGO(gene = names(gene_matrix_enrich9),
                      OrgDb = 'org.Mm.eg.db', 
                      readable = T,
                      universe = gene_matrix_background,
                      ont = "ALL",
                      pAdjustMethod = "fdr",
                      pvalueCutoff = 0.05, 
                      qvalueCutoff = 0.050)

go_enrich10 <- enrichGO(gene = names(gene_matrix_enrich10),
                      OrgDb = 'org.Mm.eg.db', 
                      readable = T,
                      universe = gene_matrix_background,
                      ont = "ALL",
                      pAdjustMethod = "fdr",
                      pvalueCutoff = 0.05, 
                      qvalueCutoff = 0.05)

go_enrich11 <- enrichGO(gene = names(gene_matrix_enrich11),
                      OrgDb = 'org.Mm.eg.db', 
                      readable = T,
                      universe = gene_matrix_background,
                      ont = "ALL",
                      pAdjustMethod = "fdr",
                      pvalueCutoff = 0.05, 
                      qvalueCutoff = 0.05)

go_enrich12 <- enrichGO(gene = names(gene_matrix_enrich12),
                      OrgDb = 'org.Mm.eg.db', 
                      readable = T,
                      universe = gene_matrix_background,
                      ont = "ALL",
                      pAdjustMethod = "fdr",
                      pvalueCutoff = 0.05, 
                      qvalueCutoff = 0.05)

go_enrich13 <- enrichGO(gene = names(gene_matrix_enrich13),
                      OrgDb = 'org.Mm.eg.db', 
                      readable = T,
                      universe = gene_matrix_background,
                      ont = "ALL",
                      pAdjustMethod = "fdr",
                      pvalueCutoff = 0.05, 
                      qvalueCutoff = 0.05)

go_enrich14 <- enrichGO(gene = names(gene_matrix_enrich14),
                      OrgDb = 'org.Mm.eg.db', 
                      readable = T,
                      universe = gene_matrix_background,
                      ont = "ALL",
                      pAdjustMethod = "fdr",
                      pvalueCutoff = 0.05, 
                      qvalueCutoff = 0.05)

go_enrich15 <- enrichGO(gene = names(gene_matrix_enrich15),
                      OrgDb = 'org.Mm.eg.db', 
                      readable = T,
                      universe = gene_matrix_background,
                      ont = "ALL",
                      pAdjustMethod = "fdr",
                      pvalueCutoff = 0.05, 
                      qvalueCutoff = 0.05)

go_enrich16 <- enrichGO(gene = names(gene_matrix_enrich16),
                      OrgDb = 'org.Mm.eg.db', 
                      readable = T,
                      universe = gene_matrix_background,
                      ont = "ALL",
                      pAdjustMethod = "fdr",
                      pvalueCutoff = 0.05, 
                      qvalueCutoff = 0.05)

go_enrich17 <- enrichGO(gene = names(gene_matrix_enrich17),
                      OrgDb = 'org.Mm.eg.db', 
                      readable = T,
                      universe = gene_matrix_background,
                      ont = "ALL",
                      pAdjustMethod = "fdr",
                      pvalueCutoff = 0.05, 
                      qvalueCutoff = 0.05)

go_enrich18 <- enrichGO(gene = names(gene_matrix_enrich18),
                      OrgDb = 'org.Mm.eg.db', 
                      readable = T,
                      universe = gene_matrix_background,
                      ont = "ALL",
                      pAdjustMethod = "fdr",
                      pvalueCutoff = 0.05, 
                      qvalueCutoff = 0.05)

go_enrich19 <- enrichGO(gene = names(gene_matrix_enrich19),
                      OrgDb = 'org.Mm.eg.db', 
                      readable = T,
                      universe = gene_matrix_background,
                      ont = "ALL",
                      pAdjustMethod = "fdr",
                      pvalueCutoff = 0.05, 
                      qvalueCutoff = 0.05)

go_enrich20 <- enrichGO(gene = names(gene_matrix_enrich20),
                      OrgDb = 'org.Mm.eg.db', 
                      readable = T,
                      universe = gene_matrix_background,
                      ont = "ALL",
                      pAdjustMethod = "fdr",
                      pvalueCutoff = 0.05, 
                      qvalueCutoff = 0.05)


```

### Prepare GO terms for simplification

We then merged the data frames to prepare for simplification of GO terms and plotting, including only results that showed signficant GO pathways.

```{r Prepare GO Results for Simplification, fig.height=6, fig.width=8, message=FALSE, warning=FALSE, include=FALSE}

go_enrich_dataset1 <- as.data.frame(go_enrich1)
#go_enrich_dataset2 <- as.data.frame(go_enrich2)
go_enrich_dataset3 <- as.data.frame(go_enrich3)
go_enrich_dataset4 <- as.data.frame(go_enrich4)
go_enrich_dataset5 <- as.data.frame(go_enrich5)
go_enrich_dataset6 <- as.data.frame(go_enrich6)
#go_enrich_dataset7 <- as.data.frame(go_enrich7)
#go_enrich_dataset8 <- as.data.frame(go_enrich8)
#go_enrich_dataset9 <- as.data.frame(go_enrich9)
go_enrich_dataset10 <- as.data.frame(go_enrich10)
go_enrich_dataset11 <- as.data.frame(go_enrich11)
go_enrich_dataset12 <- as.data.frame(go_enrich12)
go_enrich_dataset13 <- as.data.frame(go_enrich13)
go_enrich_dataset14 <- as.data.frame(go_enrich14)
#go_enrich_dataset15 <- as.data.frame(go_enrich15)
#go_enrich_dataset16 <- as.data.frame(go_enrich16)
#go_enrich_dataset17 <- as.data.frame(go_enrich17)
go_enrich_dataset18 <- as.data.frame(go_enrich18)
go_enrich_dataset19 <- as.data.frame(go_enrich19)
#go_enrich_dataset20 <- as.data.frame(go_enrich20)


go_enrich_dataset1$Dataset <- "HPP vs CTX"
#go_enrich_dataset2$Dataset <- "PFC vs CTX"
go_enrich_dataset3$Dataset <- "STR vs PFC"
go_enrich_dataset4$Dataset <- "STR vs CTX"
go_enrich_dataset5$Dataset <- "HPP vs STR"
go_enrich_dataset6$Dataset <- "HPP vs VTA"
#go_enrich_dataset7$Dataset <- "STR vs VTA"
#go_enrich_dataset8$Dataset <- "PFC vs VTA"
#go_enrich_dataset9$Dataset <- "CTX vs VTA"
go_enrich_dataset10$Dataset <- "HPP vs PFC"
go_enrich_dataset11$Dataset <- "CTX vs HPP"
go_enrich_dataset12$Dataset <- "CTX vs PFC"
go_enrich_dataset13$Dataset <- "PFC vs STR"
go_enrich_dataset14$Dataset <- "CTX vs STR"
#go_enrich_dataset15$Dataset <- "STR vs HPP"
#go_enrich_dataset16$Dataset <- "VTA vs HPP"
#go_enrich_dataset17$Dataset <- "VTA vs STR"
go_enrich_dataset18$Dataset <- "VTA vs PFC"
go_enrich_dataset19$Dataset <- "VTA vs CTX"
#go_enrich_dataset20$Dataset <- "PFC vs HPP"


go_enrich_dataset1$Region <- "HPP"
#go_enrich_dataset2$Region <- "PFC"
go_enrich_dataset3$Region <- "STR"
go_enrich_dataset4$Region <- "STR"
go_enrich_dataset5$Region <- "HPP"
go_enrich_dataset6$Region <- "HPP"
#go_enrich_dataset7$Region <- "STR"
#go_enrich_dataset8$Region <- "PFC"
#go_enrich_dataset9$Region <- "CTX"
go_enrich_dataset10$Region <- "HPP"
go_enrich_dataset11$Region <- "CTX"
go_enrich_dataset12$Region <- "CTX"
go_enrich_dataset13$Region <- "PFC"
go_enrich_dataset14$Region <- "CTX"
#go_enrich_dataset15$Region <- "STR"
#go_enrich_dataset16$Region <- "VTA"
#go_enrich_dataset17$Region <- "VTA"
go_enrich_dataset18$Region <- "VTA"
go_enrich_dataset19$Region <- "VTA"
#go_enrich_dataset20$Region <- "PFC"


go_enrich_dataset1$Comparison <- "CTX"
#go_enrich_dataset2$Comparison <- "CTX"
go_enrich_dataset3$Comparison <- "PFC"
go_enrich_dataset4$Comparison <- "CTX"
go_enrich_dataset5$Comparison <- "STR"
go_enrich_dataset6$Comparison <- "VTA"
#go_enrich_dataset7$Comparison <- "VTA"
#go_enrich_dataset8$Comparison <- "VTA"
#go_enrich_dataset9$Comparison <- "VTA"
go_enrich_dataset10$Comparison <- "PFC"
go_enrich_dataset11$Comparison <- "HPP"
go_enrich_dataset12$Comparison <- "PFC"
go_enrich_dataset13$Comparison <- "STR"
go_enrich_dataset14$Comparison <- "STR"
#go_enrich_dataset15$Comparison <- "HPP"
#go_enrich_dataset16$Comparison <- "HPP"
#go_enrich_dataset17$Comparison <- "STR"
go_enrich_dataset18$Comparison <- "PFC"
go_enrich_dataset19$Comparison <- "CTX"
#go_enrich_dataset20$Comparison <- "HPP"


go_enrich_dataset_MERGED1 <- merge(go_enrich_dataset1, go_enrich_dataset3, all=TRUE)
go_enrich_dataset_MERGED2 <- merge(go_enrich_dataset_MERGED1, go_enrich_dataset4, all=TRUE)
go_enrich_dataset_MERGED3 <- merge(go_enrich_dataset_MERGED2, go_enrich_dataset5, all=TRUE)
go_enrich_dataset_MERGED4 <- merge(go_enrich_dataset_MERGED3, go_enrich_dataset6, all=TRUE)
go_enrich_dataset_MERGED5 <- merge(go_enrich_dataset_MERGED4, go_enrich_dataset10, all=TRUE)
go_enrich_dataset_MERGED6 <- merge(go_enrich_dataset_MERGED5, go_enrich_dataset11, all=TRUE)
go_enrich_dataset_MERGED7 <- merge(go_enrich_dataset_MERGED6, go_enrich_dataset12, all=TRUE)
go_enrich_dataset_MERGED8 <- merge(go_enrich_dataset_MERGED7, go_enrich_dataset13, all=TRUE)
go_enrich_dataset_MERGED9 <- merge(go_enrich_dataset_MERGED8, go_enrich_dataset14, all=TRUE)
go_enrich_dataset_MERGED10 <- merge(go_enrich_dataset_MERGED9, go_enrich_dataset18, all=TRUE)
go_enrich_dataset_MERGED11 <- merge(go_enrich_dataset_MERGED10, go_enrich_dataset19, all=TRUE)

#write.csv(go_enrich_dataset_MERGED11, paste0(basepath, "output/CATD_DEPGs/H3K27ac/GO_Analysis/GO_NonMinimized_AllComps_Plot_BRMIC_CATD_H3k27ac_barplot_Table.csv"))


```

### Simplify GO Terms


We then simplify the GO terms using the package rrvgo to better clarify the results, grouping GO terms based on parent terms. This specific analysis uses the "Rel" method with a 0.5 threshold. Any results with too few terms to simplify were left out.

```{r Simplifying GO Terms, echo=TRUE, fig.height=10, fig.width=14, message=FALSE, warning=FALSE}

# Functions
conflicts_prefer(dplyr::summarise)
### Trying Yet Again

#BiocManager::install("rrvgo")
library(rrvgo)

## Make Files Readable for REVIGO

# Iterate over each data frame to make them accessible to REVIGO. Separating each frame by a specific Gene Ontology
for (i in 1:20) {
  
  # Check if the dataset exists
  if (exists(paste0("go_enrich_dataset", i))) {
    
    # Get the current dataset
    current_dataset <- get(paste0("go_enrich_dataset", i))
    
    # Check if the dataset has data
    if (!is.null(current_dataset) && nrow(current_dataset) > 0) {
      
      # Subset rows containing "BP" in the column "ONTOLOGY"
      BP_subset <- current_dataset[current_dataset$ONTOLOGY == "BP", ]
      assign(paste0("go_enrich_dataset", i, "_BP", i), BP_subset)
      
      # Subset rows containing "CC" in the column "ONTOLOGY"
      CC_subset <- current_dataset[current_dataset$ONTOLOGY == "CC", ]
      assign(paste0("go_enrich_dataset", i, "_CC", i), CC_subset)
      
      # Subset rows containing "MF" in the column "ONTOLOGY"
      MF_subset <- current_dataset[current_dataset$ONTOLOGY == "MF", ]
      assign(paste0("go_enrich_dataset", i, "_MF", i), MF_subset)
      
    } else {
      cat("Dataset go_enrich_dataset", i, "does not exist or is empty.\n")
      next # Move to the next iteration
    }
  } else {
    cat("Dataset go_enrich_dataset", i, "does not exist.\n")
    next # Move to the next iteration
  }
}



process_enrichment_data_BP <- function(dataset_num) {
    dataset_name <- paste0("go_enrich_dataset", dataset_num, "_BP", dataset_num)
    cat("Processing dataset:", dataset_name, "\n")
    
    # Check if the dataset exists and has data
    if (exists(dataset_name) && !is.null(get(dataset_name)) && nrow(get(dataset_name)) > 1) {
        # Calculate similarity matrix
        simMatrix_BP <- calculateSimMatrix(get(dataset_name)$ID,
                                           orgdb = "org.Mm.eg.db",
                                           ont = "BP",
                                           method = "Rel")
        
        # Set scores
        scores_BP <- setNames(-log10(get(dataset_name)$p.adjust),
                               get(dataset_name)$ID)
        
        # Reduce terms
        reducedTerms_BP <- reduceSimMatrix(simMatrix_BP,
                                           scores_BP,
                                           threshold = 0.5,
                                           orgdb = "org.Mm.eg.db")
        
        # Assign the reduced terms as a variable in R
        assign(paste0("reducedTerms_go_enrich_dataset", dataset_num, "_BP", dataset_num), reducedTerms_BP, envir = .GlobalEnv)
        
    } else {
        # If dataset doesn't exist or has no data, print a message and return NULL
        cat("Skipping dataset", dataset_num, "as it doesn't exist or has no data.\n")
    }
}


process_enrichment_data_CC <- function(dataset_num) {
    dataset_name <- paste0("go_enrich_dataset", dataset_num, "_CC", dataset_num)
    cat("Processing dataset:", dataset_name, "\n")
    
    # Check if the dataset exists and has data
    if (exists(dataset_name) && nrow(get(dataset_name)) > 1) {
        # Calculate similarity matrix
        simMatrix_CC <- calculateSimMatrix(get(dataset_name)$ID,
                                           orgdb = "org.Mm.eg.db",
                                           ont = "CC",
                                           method = "Rel")
        
        # Set scores
        scores_CC <- setNames(-log10(get(dataset_name)$p.adjust),
                               get(dataset_name)$ID)
        
        # Reduce terms
        reducedTerms_CC <- reduceSimMatrix(simMatrix_CC,
                                           scores_CC,
                                           threshold = 0.5,
                                           orgdb = "org.Mm.eg.db")
        
        # Assign the reduced terms as a variable in R
        assign(paste0("reducedTerms_go_enrich_dataset", dataset_num, "_CC", dataset_num), reducedTerms_CC, envir = .GlobalEnv)
        
    } else {
        # If dataset doesn't exist or has no data, print a message and return NULL
        cat("Skipping dataset", dataset_num, "as it doesn't exist or has no data.\n")
    }
}


process_enrichment_data_MF <- function(dataset_num) {
    dataset_name <- paste0("go_enrich_dataset", dataset_num, "_MF", dataset_num)
    cat("Processing dataset:", dataset_name, "\n")
    
    
    # Check if the dataset exists and has data
    if (exists(dataset_name) && nrow(get(dataset_name)) > 1) {
        # Calculate similarity matrix
        simMatrix_MF <- calculateSimMatrix(get(dataset_name)$ID,
                                           orgdb = "org.Mm.eg.db",
                                           ont = "MF",
                                           method = "Rel")
        
        # Set scores
        scores_MF <- setNames(-log10(get(dataset_name)$p.adjust),
                               get(dataset_name)$ID)
        
        # Reduce terms
        reducedTerms_MF <- reduceSimMatrix(simMatrix_MF,
                                           scores_MF,
                                           threshold = 0.5,
                                           orgdb = "org.Mm.eg.db")
        
        # Assign the reduced terms as a variable in R
        assign(paste0("reducedTerms_go_enrich_dataset", dataset_num, "_MF", dataset_num), reducedTerms_MF, envir = .GlobalEnv)
        
    } else {
        # If dataset doesn't exist or has no data, print a message and return NULL
        cat("Skipping dataset", dataset_num, "as it doesn't exist or has no data.\n")
    }
}




library(dplyr)

process_final_terms <- function(dataset_num) {
    # List of ontologies
    ontologies <- c("BP", "CC", "MF")
    
    # Initialize a list to store the final terms dataframes for each ontology
    final_terms_list <- list()
    
    # Loop through ontologies
    for (ont in ontologies) {
        # Construct the dataframe name
        df_name <- paste0("reducedTerms_go_enrich_dataset", dataset_num, "_", ont, dataset_num)
        
        # Check if the dataframe exists
        if (!exists(df_name)) {
            cat("Skipping", df_name, "as it doesn't exist.\n")
            next  # Skip to the next iteration if the dataframe doesn't exist
        }
        
        # Read the dataframe
        df <- get(df_name)
        
        # Perform the operation if the dataframe is not empty
        tryCatch({
            # Group by 'parent' and select the row with the maximum 'score'
            final_terms <- df %>%
                group_by(parent) %>%
                summarise(score = max(score), parentTerm = dplyr::first(parentTerm)) %>%
                ungroup()
            
            # Append the final terms dataframe to the list
            final_terms_list[[ont]] <- final_terms
            
            # Print a message indicating successful processing
            cat("Final terms for", df_name, "have been processed.\n")
        }, error = function(e) {
            cat("Error processing", df_name, ": ", conditionMessage(e), "\n")
        })
    }
    
    # Merge final terms dataframes for all ontologies
    final_terms_merged <- bind_rows(final_terms_list, .id = "ontology")
    
    # Assign the merged final terms dataframe to a new variable
    assign(paste0("FinalTerms_go_enrich_dataset", dataset_num), final_terms_merged, envir = .GlobalEnv)
}

# Loop through all "BP" Datasets
for (i in 1:20) {
    # Process the current dataset
    process_enrichment_data_BP(i)
}

# Loop through all "CC" Datasets
for (i in 1:20) {
    # Process the current dataset
    process_enrichment_data_CC(i)
}

# Loop through all "MF" Datasets
for (i in 1:20) {
    # Process the current dataset
    process_enrichment_data_MF(i)
}

# Loop through all datasets and apply the function
for (i in 1:20) {
    process_final_terms(i)
}

```

We then prepared the simplified results for plotting by assigning proper labels, merging and selecting for the top results.

```{r Prepare Simplified Terms for Plotting, echo=TRUE, message=FALSE, warning=FALSE}


FinalTerms_go_enrich_dataset1$Dataset <- "HPP vs CTX"
FinalTerms_go_enrich_dataset2$Dataset <- "PFC vs CTX"
FinalTerms_go_enrich_dataset3$Dataset <- "STR vs PFC"
FinalTerms_go_enrich_dataset4$Dataset <- "STR vs CTX"
FinalTerms_go_enrich_dataset5$Dataset <- "HPP vs STR"
FinalTerms_go_enrich_dataset6$Dataset <- "HPP vs VTA"
FinalTerms_go_enrich_dataset7$Dataset <- "STR vs VTA"
FinalTerms_go_enrich_dataset8$Dataset <- "PFC vs VTA"
FinalTerms_go_enrich_dataset9$Dataset <- "CTX vs VTA"
FinalTerms_go_enrich_dataset10$Dataset <- "HPP vs PFC"
FinalTerms_go_enrich_dataset11$Dataset <- "CTX vs HPP"
FinalTerms_go_enrich_dataset12$Dataset <- "CTX vs PFC"
FinalTerms_go_enrich_dataset13$Dataset <- "PFC vs STR"
FinalTerms_go_enrich_dataset14$Dataset <- "CTX vs STR"
FinalTerms_go_enrich_dataset15$Dataset <- "STR vs HPP"
FinalTerms_go_enrich_dataset16$Dataset <- "VTA vs HPP"
FinalTerms_go_enrich_dataset17$Dataset <- "VTA vs STR"
FinalTerms_go_enrich_dataset18$Dataset <- "VTA vs PFC"
FinalTerms_go_enrich_dataset19$Dataset <- "VTA vs CTX"
FinalTerms_go_enrich_dataset20$Dataset <- "PFC vs HPP"


FinalTerms_go_enrich_dataset1$Region <- "HPP"
FinalTerms_go_enrich_dataset2$Region <- "PFC"
FinalTerms_go_enrich_dataset3$Region <- "STR"
FinalTerms_go_enrich_dataset4$Region <- "STR"
FinalTerms_go_enrich_dataset5$Region <- "HPP"
FinalTerms_go_enrich_dataset6$Region <- "HPP"
FinalTerms_go_enrich_dataset7$Region <- "STR"
FinalTerms_go_enrich_dataset8$Region <- "PFC"
FinalTerms_go_enrich_dataset9$Region <- "CTX"
FinalTerms_go_enrich_dataset10$Region <- "HPP"
FinalTerms_go_enrich_dataset11$Region <- "CTX"
FinalTerms_go_enrich_dataset12$Region <- "CTX"
FinalTerms_go_enrich_dataset13$Region <- "PFC"
FinalTerms_go_enrich_dataset14$Region <- "CTX"
FinalTerms_go_enrich_dataset15$Region <- "STR"
FinalTerms_go_enrich_dataset16$Region <- "VTA"
FinalTerms_go_enrich_dataset17$Region <- "VTA"
FinalTerms_go_enrich_dataset18$Region <- "VTA"
FinalTerms_go_enrich_dataset19$Region <- "VTA"
FinalTerms_go_enrich_dataset20$Region <- "PFC"


FinalTerms_go_enrich_dataset1$Comparison <- "CTX"
FinalTerms_go_enrich_dataset2$Comparison <- "CTX"
FinalTerms_go_enrich_dataset3$Comparison <- "PFC"
FinalTerms_go_enrich_dataset4$Comparison <- "CTX"
FinalTerms_go_enrich_dataset5$Comparison <- "STR"
FinalTerms_go_enrich_dataset6$Comparison <- "VTA"
FinalTerms_go_enrich_dataset7$Comparison <- "VTA"
FinalTerms_go_enrich_dataset8$Comparison <- "VTA"
FinalTerms_go_enrich_dataset9$Comparison <- "VTA"
FinalTerms_go_enrich_dataset10$Comparison <- "PFC"
FinalTerms_go_enrich_dataset11$Comparison <- "HPP"
FinalTerms_go_enrich_dataset12$Comparison <- "PFC"
FinalTerms_go_enrich_dataset13$Comparison <- "STR"
FinalTerms_go_enrich_dataset14$Comparison <- "STR"
FinalTerms_go_enrich_dataset15$Comparison <- "HPP"
FinalTerms_go_enrich_dataset16$Comparison <- "HPP"
FinalTerms_go_enrich_dataset17$Comparison <- "STR"
FinalTerms_go_enrich_dataset18$Comparison <- "PFC"
FinalTerms_go_enrich_dataset19$Comparison <- "CTX"
FinalTerms_go_enrich_dataset20$Comparison <- "HPP"

######################################################################### Cortex ##############################################################################################



CTX1 <- merge(FinalTerms_go_enrich_dataset9, FinalTerms_go_enrich_dataset11, all=TRUE)
CTX2 <- merge(CTX1, FinalTerms_go_enrich_dataset12, all=TRUE)
CTX3 <- merge(CTX2, FinalTerms_go_enrich_dataset14, all=TRUE)

HPP1 <- merge(FinalTerms_go_enrich_dataset1, FinalTerms_go_enrich_dataset5, all=TRUE)
HPP2 <- merge(HPP1, FinalTerms_go_enrich_dataset6, all=TRUE)
HPP3 <- merge(HPP2, FinalTerms_go_enrich_dataset10, all=TRUE)

STR1 <- merge(FinalTerms_go_enrich_dataset3, FinalTerms_go_enrich_dataset4, all=TRUE)
STR2 <- merge(STR1, FinalTerms_go_enrich_dataset7, all=TRUE)
STR3 <- merge(STR2, FinalTerms_go_enrich_dataset15, all=TRUE)

PFC1 <- merge(FinalTerms_go_enrich_dataset2, FinalTerms_go_enrich_dataset8, all=TRUE)
PFC2 <- merge(PFC1, FinalTerms_go_enrich_dataset13, all=TRUE)
PFC3 <- merge(PFC2, FinalTerms_go_enrich_dataset20, all=TRUE)

VTA1 <- merge(FinalTerms_go_enrich_dataset16, FinalTerms_go_enrich_dataset17, all=TRUE)
VTA2 <- merge(VTA1, FinalTerms_go_enrich_dataset18, all=TRUE)
VTA3 <- merge(VTA2, FinalTerms_go_enrich_dataset19, all=TRUE)


AllGoMerged1 <- merge(CTX3, HPP3, all = TRUE)
AllGoMerged2 <- merge(AllGoMerged1, STR3, all = TRUE)
AllGoMerged3 <- merge(AllGoMerged2, PFC3, all = TRUE)
AllGoMerged4 <- merge(AllGoMerged3, VTA3, all = TRUE)


# Convert pvalue to -log scale
CTX3$log_pvalue <- CTX3$score
HPP3$log_pvalue <- HPP3$score
STR3$log_pvalue <- STR3$score
PFC3$log_pvalue <- PFC3$score
VTA3$log_pvalue <- VTA3$score

# Adjust Text Wrapping for the GO Description and Take the top 12

top_10_CTX <- head(CTX3[order(CTX3$log_pvalue, decreasing = TRUE), ], 12)
top_10_CTX$parentTerm <- str_wrap(top_10_CTX$parentTerm, width = 25)
top_10_HPP <- head(HPP3[order(HPP3$log_pvalue, decreasing = TRUE), ], 12)
top_10_HPP$parentTerm <- str_wrap(top_10_HPP$parentTerm, width = 25)
top_10_STR <- head(STR3[order(STR3$log_pvalue, decreasing = TRUE), ], 12)
top_10_STR$parentTerm <- str_wrap(top_10_STR$parentTerm, width = 25)
top_10_PFC <- head(PFC3[order(PFC3$log_pvalue, decreasing = TRUE), ], 12)
top_10_PFC$parentTerm <- str_wrap(top_10_PFC$parentTerm, width = 25)
top_10_VTA <- head(VTA3[order(VTA3$log_pvalue, decreasing = TRUE), ], 12)
top_10_VTA$parentTerm <- str_wrap(top_10_VTA$parentTerm, width = 25)

Merge1 <- merge(top_10_HPP, top_10_CTX, all=TRUE)
Merge2 <- merge(Merge1, top_10_VTA, all=TRUE)
Merge3 <- merge(Merge2, top_10_STR, all=TRUE)
Merge4 <- merge(Merge3, top_10_PFC, all=TRUE)

library(stringr)

Merge4$parentTerm <- str_wrap(Merge4$parentTerm, width = 60)
Merge4$parentTerm <- str_to_sentence(Merge4$parentTerm)

#write.csv(Merge4, paste0(basepath, "output/CATD_DEPGs//H3K27ac/GO_Analysis/GO_Minimized_AllComps_Plot_BRMIC_CATD_H3K27ac_barplot_Table.csv"))


```

### Plot Simplified GO Terms 
We then plot the simplified terms for each comparison

#### All GO terms
```{r Plotting Simplified GO Terms, echo=TRUE}

Merged_GOPlots <- ggplot(Merge4, aes(x = parentTerm, y = log_pvalue, fill = Comparison)) +
  theme_classic()+
  geom_bar(stat = "identity", position = position_dodge2(width = 1, preserve = "single"), width = 2) +  
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8, color = "black"),  
        plot.margin = unit(c(2, 2, 2, 2), "cm"), 
        axis.text = element_text(margin = margin(1, unit("cm", "cm"), 1, 1))) + 
  labs(x = "Gene Ontology Pathways", y = "-log(pvalue)", fill = "Dataset") +
  ggtitle("Top 10 GeneOntology Pathways By Comparison") +
  scale_fill_manual(values = custom_colors)+
  facet_grid(. ~ Region, scales = "free")

#pdf(paste0(basepath, "output/CATD_DEPGs/H3K27ac/GO_Analysis/GO_Minimized_AllComps_BarPlot_BRMIC_CATD_H3K27ac.pdf"), width = 20, height = 15)
Merged_GOPlots
#dev.off()

```

#### Selected Simplified GO TERMS {.tabset}

##### All GO Terms
```{r Generate DotPlots of SImplified GO Pathways, echo=TRUE, fig.height=15, fig.width=15}

AllMerged4_Ordered <- if (exists("AllMerged4_Ordered")) {
  AllMerged4_Ordered
} else if (exists("AllMarged4_ordered")) {
  AllMarged4_ordered
} else {
  if (!exists("AllGoMerged4")) stop("AllGoMerged4 not found.")
  AllGoMerged4[order(AllGoMerged4$score, decreasing = TRUE), ]
}

## Ensure we have a -log10(p.adjust) column named log_pvalue
if (!("log_adjpvalue" %in% names(AllMerged4_Ordered))) {
  if ("score" %in% names(AllMerged4_Ordered)) {
    AllMerged4_Ordered$log_adjpvalue <- AllMerged4_Ordered$score
  } else {
    stop("Neither 'log_adjpvalue' nor 'score' found to write log_adjpvalue.")
  }
}

top_n <-5
plot_df <- AllMerged4_Ordered |>
  dplyr::filter(!is.na(parentTerm), !is.na(Region), !is.na(ontology)) |>
  dplyr::group_by(Region, ontology) |>
  dplyr::slice_max(order_by = log_adjpvalue, n = top_n, with_ties = FALSE) |>
  dplyr::ungroup()

term_levels <- plot_df |>
  dplyr::group_by(parentTerm) |>
  dplyr::summarise(max_logp = max(log_adjpvalue, na.rm = TRUE), .groups = "drop") |>
  dplyr::arrange(max_logp) |>
  dplyr::pull(parentTerm)

region_colors <- c(
  "CTX" = "#FF9289", 
  "HPP" = "#FF8AFF", 
  "PFC" = "#00DB98", 
  "STR" = "#00CBFF", 
  "VTA" = "#BEC100"
)


plot_df$Region <- factor(plot_df$Region, levels = names(region_colors))


p_ALL <- ggplot2::ggplot(
  plot_df,
  ggplot2::aes(x = Region, y = parentTerm, size = log_adjpvalue, color = Region)
) +
  ggplot2::geom_point(alpha = 0.9) +
  ggplot2::scale_size_continuous(name = expression(-log[10]("adj. p")), range = c(1, 4)) +
  ggplot2::scale_color_manual(
    name = "Region",
    values = region_colors,
    limits = names(region_colors),  
    drop = FALSE
  ) +
  ggplot2::labs(
    x = NULL, y = "Representative GO term",
    title = "GO term summary across brain regions K27ac (ALL Ontologies; RRVGO-reduced)",
    subtitle = paste0("Top ", top_n, " terms per Region × Ontology")
  ) +
  ggplot2::theme_bw(base_size = 4) +
  ggplot2::theme(
    axis.text.y = ggplot2::element_text(size = 4),
    legend.position = "right"
  )
  #ggplot2::facet_grid(ontology ~ Region, scales = "free", space = "free_y")

print(p_ALL)


#pdf(paste0(basepath, "output/CATD_DEPGs/H3K27ac/GO_Analysis/GO_Minimized_K27ac_Top10AllComps_DotPlot_AllOnt_BRMIC_Final.pdf"), width = 4, height = 6)
#print(p_ALL)
#dev.off()

```

##### BP Terms Only

```{r Generate DotPlots of BP Simplified GO Pathways, echo=TRUE, fig.height=15, fig.width=15}

## Remove MF and CC Ontologies
plot_df$Region <- factor(plot_df$Region, levels = names(region_colors))

plot_df2 <- plot_df |> 
  dplyr::filter(!(ontology == "MF"))

plot_df3 <- plot_df2 |> 
  dplyr::filter(!(ontology == "CC"))

p_BP <- ggplot2::ggplot(
  plot_df3,
  ggplot2::aes(x = Region, y = parentTerm, size = log_adjpvalue, color = Region)
) +
  ggplot2::geom_point(alpha = 0.9) +
  ggplot2::scale_size_continuous(name = expression(-log[10]("adj. p")), range = c(1, 4)) +
  ggplot2::scale_color_manual(
    name = "Region",
    values = region_colors,
    limits = names(region_colors), 
    drop = FALSE
  ) +
  ggplot2::labs(
    x = NULL, y = "Representative GO term",
    title = "GO term summary across brain regions K27ac (BP Only; RRVGO-reduced)",
    subtitle = paste0("Top ", top_n, " terms per Region × Ontology")
  ) +
  ggplot2::theme_bw(base_size = 4) +
  ggplot2::theme(
    axis.text.y = ggplot2::element_text(size = 4),
    legend.position = "right"
  ) 

print(p_BP)


#pdf(paste0(basepath,"output/CATD_DEPGs/H3K27ac/GO_Analysis/GO_Minimized_K27ac_Top10AllComps_DotPlot_BPOnly_BRMICRNASeq_Final.pdf"), width = 6, height = 6)
#print(p_BP)
#dev.off()

```

##### BP and MF Terms Only

```{r Generate DotPlots of BP and MF Simplified GO Pathways, echo=TRUE, fig.height=15, fig.width=15}

## Only Remove CC
plot_df$Region <- factor(plot_df$Region, levels = names(region_colors))

plot_df4 <- plot_df |> 
  dplyr::filter(!(ontology == "CC"))


p_BPMF <- ggplot2::ggplot(
  plot_df4,
  ggplot2::aes(x = Region, y = parentTerm, size = log_adjpvalue, color = Region)
) +
  ggplot2::geom_point(alpha = 1) +
  ggplot2::scale_size_continuous(name = expression(-log[10]("adj. p")), range = c(1, 4)) +
  ggplot2::scale_color_manual(
    name = "Region",
    values = region_colors,
    limits = names(region_colors),  
    drop = FALSE
  ) +
  ggplot2::labs(
    x = NULL, y = "Representative GO term",
    title = "GO term summary across brain regions K27ac (BP&MF; RRVGO-reduced)",
    subtitle = paste0("Top ", top_n, " terms per Region × Ontology")
  ) +
  ggplot2::theme_bw(base_size = 4) +
  ggplot2::theme(
    axis.text.y = ggplot2::element_text(size = 4),
    legend.position = "right"
  ) 


print(p_BPMF)


#pdf(paste0(basepath,"output/CATD_DEPGs/H3K27ac/GO_Analysis/GO_Minimized_K27ac_Top10AllComps_DotPlot_BPMFOntOnly_BRMICRNASeq_Final.pdf"), width = 6, height = 6)
#print(p_BPMF)
#dev.off()


```


# Session Info

```{r Print SessionInfo}

sessionInfo()

```

