---
title: "Overlapping Gene Expression with Epigenetic Features"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: false
editor_options:
  chunk_output_type: console
---

# Microglial Transcriptional And Epigenetic Profiling -- Looking at Overlapping Genes

All of these files stem either from the differential gene expression
analysis in the RNA Sequencing data or the differential deposition
analysis in the CATD data.

```{r}
knitr::opts_chunk$set(echo = TRUE)

library(conflicted)
library(kableExtra)
library(VennDiagram)
library(grid)
library(workflowr)
library(ggplot2)
library(dplyr)
library(stringr)

conflicts_prefer(base::intersect)

# Identify the repository root from the opened RStudio project
projdir <- normalizePath(".", winslash = "/", mustWork = TRUE)

project_file <- file.path(projdir, "RegionalMicroglialTranscriptomicsandEpigenomics.Rproj")

if (!file.exists(project_file)) {
  stop(
    paste(
      "The repository root could not be identified.",
      "Open RegionalMicroglialTranscriptomicsandEpigenomics.Rproj",
      "before running this analysis."
    )
  )
}

basepath <- paste0(projdir, "/")

# Define Required Input Directories
rna_results_dir <- file.path(projdir, "output", "RNASeq_DEGs", "Results_Sig_CSVs")
k27me3_results_dir <- file.path(projdir, "output", "CATD_DEPGs", "H3K27me3")
k27ac_results_dir <- file.path(projdir, "output", "CATD_DEPGs", "H3K27ac")

# Confirm Required Input Directories Exist
if (!dir.exists(rna_results_dir)) {
  stop(paste("Required RNA-seq results directory not found:", rna_results_dir))
}

if (!dir.exists(k27me3_results_dir)) {
  stop(paste("Required H3K27me3 results directory not found:", k27me3_results_dir))
}

if (!dir.exists(k27ac_results_dir)) {
  stop(paste("Required H3K27ac results directory not found:", k27ac_results_dir))
}

```

## Correlating Significant Genes with Genes known to be regulated by H3K27me3

### Read in and filter necessary files

```{r H3K37me3 Correlations with Signficantly Downregulated Genes Reading in Files}
PFCvsVTArna <- read.csv(paste0(basepath, "output/RNASeq_DEGs/Results_Sig_CSVs/Sig_Res_DEGs_PFC_vs_VTA.csv"), header = TRUE)
## Subset for Highly Significant Results (adjp < 0.05)
PFCvsVTArnaSig <- subset(PFCvsVTArna, padj < 0.05)
## Subset for Downregulated Genes (L2FC < 0)
PFCvsVTArnaDown <- subset(PFCvsVTArnaSig, log2FoldChange < 0)

PFCvsVTAcatd <- read.csv(paste0(basepath,"output/CATD_DEPGs/H3K27me3/Sig_Res_DEPGs_K27me3_PFC_vs_VTA.csv"), header = TRUE)
## Subset for Highly Significant Results (adjp < 0.05)
PFCvsVTAcatdSig <- subset(PFCvsVTAcatd, padj < 0.05)
## Subset for Downregulated Genes (L2FC < 0)
PFCvsVTAcatdSigUp <- subset(PFCvsVTAcatdSig, log2FoldChange > 0)

HPPvsSTRrna <- read.csv(paste0(basepath,"output/RNASeq_DEGs/Results_Sig_CSVs/Sig_Res_DEGs_HPP_vs_STR.csv"), header = TRUE)
## Subset for Highly Significant Results (adjp < 0.05)
HPPvsSTRrnaSig <- subset(HPPvsSTRrna, padj < 0.05)
## Subset for Downregulated Genes (L2FC < 0)
HPPvsSTRrnaDown <- subset(HPPvsSTRrnaSig, log2FoldChange < 0)

HPPvsSTRcatd <- read.csv(paste0(basepath,"output/CATD_DEPGs/H3K27me3/Sig_Res_DEPGs_K27me3_HPP_vs_STR.csv"), header = TRUE)
## Subset for Highly Significant Results (adjp < 0.05)
HPPvsSTRcatdSig <- subset(HPPvsSTRcatd, padj < 0.05)
## Subset for Downregulated Genes (L2FC < 0)
HPPvsSTRcatdSigUp <- subset(HPPvsSTRcatdSig, log2FoldChange > 0)

STRvsVTArna <- read.csv(paste0(basepath,"output/RNASeq_DEGs/Results_Sig_CSVs/Sig_Res_DEGs_STR_vs_VTA.csv"), header = TRUE)
## Subset for Highly Significant Results (adjp < 0.05)
STRvsVTArnaSig <- subset(STRvsVTArna, padj < 0.05)
## Subset for Downregulated Genes (L2FC < 0)
STRvsVTArnaDown <- subset(STRvsVTArnaSig, log2FoldChange < 0)

STRvsVTAcatd <- read.csv(paste0(basepath,"output/CATD_DEPGs/H3K27me3/Sig_Res_DEPGs_K27me3_STR_vs_VTA.csv"), header = TRUE)
## Subset for Highly Significant Results (adjp < 0.05)
STRvsVTAcatdSig <- subset(STRvsVTAcatd, padj < 0.05)
## Subset for Downregulated Genes (L2FC < 0)
STRvsVTAcatdSigUp <- subset(STRvsVTAcatdSig, log2FoldChange > 0)

HPPvsCTXrna <- read.csv(paste0(basepath,"output/RNASeq_DEGs/Results_Sig_CSVs/Sig_Res_DEGs_HPP_vs_Cortex.csv"), header = TRUE)
## Subset for Highly Significant Results (adjp < 0.05)
HPPvsCTXrnaSig <- subset(HPPvsCTXrna, padj < 0.05)
## Subset for Downregulated Genes (L2FC < 0)
HPPvsCTXrnaDown <- subset(HPPvsCTXrnaSig, log2FoldChange < 0)

HPPvsCTXcatd <- read.csv(paste0(basepath,"output/CATD_DEPGs/H3K27me3/Sig_Res_DEPGs_K27me3_HPP_vs_CTX.csv"), header = TRUE)
## Subset for Highly Significant Results (adjp < 0.05)
HPPvsCTXcatdSig <- subset(HPPvsCTXcatd, padj < 0.05)
## Subset for Downregulated Genes (L2FC < 0)
HPPvsCTXcatdSigUp <- subset(HPPvsCTXcatdSig, log2FoldChange > 0)

PFCvsCTXrna <- read.csv(paste0(basepath,"output/RNASeq_DEGs/Results_Sig_CSVs/Sig_Res_DEGs_PFC_vs_Cortex.csv"), header = TRUE)
## Subset for Highly Significant Results (adjp < 0.05)
PFCvsCTXrnaSig <- subset(PFCvsCTXrna, padj < 0.05)
## Subset for Downregulated Genes (L2FC < 0)
PFCvsCTXrnaDown <- subset(PFCvsCTXrnaSig, log2FoldChange < 0)

#PFCvsCTXcatd <- read.csv(paste0(basepath,"output/CATD_DEPGs/H3K27me3/Sig_Res_DEPGs_K27me3_PFC_vs_CTX.csv"), header = TRUE)
## Subset for Highly Significant Results (adjp < 0.05)
#PFCvsCTXcatdSig <- subset(PFCvsCTXcatd, padj < 0.05)
## Subset for Downregulated Genes (L2FC < 0)
#PFCvsCTXcatdSigUp <- subset(PFCvsCTXcatdSig, log2FoldChange > 0)

STRvsPFCrna <- read.csv(paste0(basepath,"output/RNASeq_DEGs/Results_Sig_CSVs/Sig_Res_DEGs_STR_vs_PFC.csv"), header = TRUE)
## Subset for Highly Significant Results (adjp < 0.05)
STRvsPFCrnaSig <- subset(STRvsPFCrna, padj < 0.05)
## Subset for Downregulated Genes (L2FC < 0)
STRvsPFCrnaDown <- subset(STRvsPFCrnaSig, log2FoldChange < 0)

STRvsPFCcatd <- read.csv(paste0(basepath,"output/CATD_DEPGs/H3K27me3/Sig_Res_DEPGs_K27me3_STR_vs_PFC.csv"), header = TRUE)
## Subset for Highly Significant Results (adjp < 0.05)
STRvsPFCcatdSig <- subset(STRvsPFCcatd, padj < 0.05)
## Subset for Downregulated Genes (L2FC < 0)
STRvsPFCcatdSigUp <- subset(STRvsPFCcatdSig, log2FoldChange > 0)

STRvsCTXrna <- read.csv(paste0(basepath,"output/RNASeq_DEGs/Results_Sig_CSVs/Sig_Res_DEGs_STR_vs_Cortex.csv"), header = TRUE)
## Subset for Highly Significant Results (adjp < 0.05)
STRvsCTXrnaSig <- subset(STRvsCTXrna, padj < 0.05)
## Subset for Downregulated Genes (L2FC < 0)
STRvsCTXrnaDown <- subset(STRvsCTXrnaSig, log2FoldChange < 0)

STRvsCTXcatd <- read.csv(paste0(basepath,"output/CATD_DEPGs/H3K27me3/Sig_Res_DEPGs_K27me3_STR_vs_CTX.csv"), header = TRUE)
## Subset for Highly Significant Results (adjp < 0.05)
STRvsCTXcatdSig <- subset(STRvsCTXcatd, padj < 0.05)
## Subset for Downregulated Genes (L2FC < 0)
STRvsCTXcatdSigUp <- subset(STRvsCTXcatdSig, log2FoldChange > 0)

HPPvsVTArna <- read.csv(paste0(basepath,"output/RNASeq_DEGs/Results_Sig_CSVs/Sig_Res_DEGs_HPP_vs_VTA.csv"), header = TRUE)
## Subset for Highly Significant Results (adjp < 0.05)
HPPvsVTArnaSig <- subset(HPPvsVTArna, padj < 0.05)
## Subset for Downregulated Genes (L2FC < 0)
HPPvsVTArnaDown <- subset(HPPvsVTArnaSig, log2FoldChange < 0)

HPPvsVTAcatd <- read.csv(paste0(basepath,"output/CATD_DEPGs/H3K27me3/Sig_Res_DEPGs_K27me3_HPP_vs_VTA.csv"), header = TRUE)
## Subset for Highly Significant Results (adjp < 0.05)
HPPvsVTAcatdSig <- subset(HPPvsVTAcatd, padj < 0.05)
## Subset for Downregulated Genes (L2FC < 0)
HPPvsVTAcatdSigUp <- subset(HPPvsVTAcatdSig, log2FoldChange > 0)

CTXvsVTArna <- read.csv(paste0(basepath,"output/RNASeq_DEGs/Results_Sig_CSVs/Sig_Res_DEGs_CTX_vs_VTA.csv"), header = TRUE)
## Subset for Highly Significant Results (adjp < 0.05)
CTXvsVTArnaSig <- subset(CTXvsVTArna, padj < 0.05)
## Subset for Downregulated Genes (L2FC < 0)
CTXvsVTArnaDown <- subset(CTXvsVTArnaSig, log2FoldChange < 0)

CTXvsVTAcatd <- read.csv(paste0(basepath,"output/CATD_DEPGs/H3K27me3/Sig_Res_DEPGs_K27me3_CTX_vs_VTA.csv"), header = TRUE)
## Subset for Highly Significant Results (adjp < 0.05)
CTXvsVTAcatdSig <- subset(CTXvsVTAcatd, padj < 0.05)
## Subset for Downregulated Genes (L2FC < 0)
CTXvsVTAcatdSigUp <- subset(CTXvsVTAcatdSig, log2FoldChange > 0)

HPPvsPFCrna <- read.csv(paste0(basepath,"output/RNASeq_DEGs/Results_Sig_CSVs/Sig_Res_DEGs_HPP_vs_PFC.csv"), header = TRUE)
## Subset for Highly Significant Results (adjp < 0.05)
HPPvsPFCrnaSig <- subset(HPPvsPFCrna, padj < 0.05)
## Subset for Downregulated Genes (L2FC < 0)
HPPvsPFCrnaDown <- subset(HPPvsPFCrnaSig, log2FoldChange < 0)

HPPvsPFCcatd <- read.csv(paste0(basepath,"output/CATD_DEPGs/H3K27me3/Sig_Res_DEPGs_K27me3_HPP_vs_PFC.csv"), header = TRUE)
## Subset for Highly Significant Results (adjp < 0.05)
HPPvsPFCcatdSig <- subset(HPPvsPFCcatd, padj < 0.05)
## Subset for Downregulated Genes (L2FC < 0)
HPPvsPFCcatdSigUp <- subset(HPPvsPFCcatdSig, log2FoldChange > 0)

```

### Check and Print All Overlaps based on Comparison for K27me3 {.tabset}

#### PFC vs VTA

```{r}

common_K27me3_PFCvsVTA <- intersect(PFCvsVTArnaDown$symbol, PFCvsVTAcatdSigUp$symbol)
kbl(common_K27me3_PFCvsVTA, col.names = "Genes Overlapping") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

a=length(PFCvsVTArnaDown$symbol)
b=length(PFCvsVTAcatdSigUp$symbol)
c=length(common_K27me3_PFCvsVTA)

RNA=a-c
CATD=b-c
COMMON=c

knitr::kables(
  list(
    knitr::kable(RNA, "rst", col.names = "DEGs Downregulated"),
    knitr::kable(COMMON, "rst", col.names = "Overlaps DEGs + DEPGs"),
    knitr::kable(CATD, "rst", col.names = "DEPGs Upregulated"))
)

```

#### HPP vs STR

```{r echo=TRUE}

common_K27me3_HPPvsSTR <- intersect(HPPvsSTRrnaDown$symbol, HPPvsSTRcatdSigUp$symbol)
knitr::kable(common_K27me3_HPPvsSTR, "rst", col.names = "Genes Overlapping") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

a=length(HPPvsSTRrnaDown$symbol)
b=length(HPPvsSTRcatdSigUp$symbol)
c=length(common_K27me3_HPPvsSTR)

RNA=a-c
CATD=b-c
COMMON=c

knitr::kables(
  list(
    knitr::kable(RNA, "rst", col.names = "DEGs Downregulated"),
    knitr::kable(COMMON, "rst", col.names = "Overlaps DEGs + DEPGs"),
    knitr::kable(CATD, "rst", col.names = "DEPGs Upregulated"))
)
```

#### STR vs VTA

```{r}
common_K27me3_STRvsVTA <- intersect(STRvsVTArnaDown$symbol, STRvsVTAcatdSigUp$symbol)
knitr::kable(common_K27me3_STRvsVTA, "rst", col.names = "Genes Overlapping") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

a=length(STRvsVTArnaDown$symbol)
b=length(STRvsVTAcatdSigUp$symbol)
c=length(common_K27me3_STRvsVTA)

RNA=a-c
CATD=b-c
COMMON=c

knitr::kables(
  list(
    knitr::kable(RNA, "rst", col.names = "DEGs Downregulated"),
    knitr::kable(COMMON, "rst", col.names = "Overlaps DEGs + DEPGs"),
    knitr::kable(CATD, "rst", col.names = "DEPGs Upregulated"))
)
```

#### HPP vs CTX

```{r}
common_K27me3_HPPvsCTX <- intersect(HPPvsCTXrnaDown$symbol, HPPvsCTXcatdSigUp$symbol)
knitr::kable(common_K27me3_HPPvsCTX, "rst", col.names = "Genes Overlapping") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

a=length(HPPvsCTXrnaDown$symbol)
b=length(HPPvsCTXcatdSigUp$symbol)
c=length(common_K27me3_HPPvsCTX)

RNA=a-c
CATD=b-c
COMMON=c

knitr::kables(
  list(
    knitr::kable(RNA, "rst", col.names = "DEGs Downregulated"),
    knitr::kable(COMMON, "rst", col.names = "Overlaps DEGs + DEPGs"),
    knitr::kable(CATD, "rst", col.names = "DEPGs Upregulated"))
)
```

#### PFC vs CTX

```{r}
#common_K27me3_PFCvsCTX <- intersect(PFCvsCTXrnaDown$symbol, PFCvsCTXcatdSigUp$symbol)
#knitr::kable(common_K27me3_PFCvsCTX, "rst", col.names = "Genes Overlapping") %>%
#  kable_styling(bootstrap_options = c("striped", "hover"))


#a=length(PFCvsCTXrnaDown$symbol)
#b=length(PFCvsCTXcatdSigUp$symbol)
#c=length(common_K27me3_PFCvsCTX)

#RNA=a-c
#CATD=b-c
#COMMON=c

#knitr::kables(
#  list(
#    knitr::kable(RNA, "rst", col.names = "DEGs Downregulated"),
#    knitr::kable(COMMON, "rst", col.names = "Overlaps DEGs + DEPGs"),
#    knitr::kable(CATD, "rst", col.names = "DEPGs Upregulated"))
#)
```

#### STR vs PFC

```{r}
common_K27me3_STRvsPFC <- intersect(STRvsPFCrnaDown$symbol, STRvsPFCcatdSigUp$symbol)
knitr::kable(common_K27me3_STRvsPFC, "rst", col.names = "Genes Overlapping") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

a=length(STRvsPFCrnaDown$symbol)
b=length(STRvsPFCcatdSigUp$symbol)
c=length(common_K27me3_STRvsPFC)

RNA=a-c
CATD=b-c
COMMON=c

knitr::kables(
  list(
    knitr::kable(RNA, "rst", col.names = "DEGs Downregulated"),
    knitr::kable(COMMON, "rst", col.names = "Overlaps DEGs + DEPGs"),
    knitr::kable(CATD, "rst", col.names = "DEPGs Upregulated"))
)

```

#### STR vs CTX

```{r}
common_K27me3_STRvsCTX <- intersect(STRvsCTXrnaDown$symbol, STRvsCTXcatdSigUp$symbol)
knitr::kable(common_K27me3_STRvsCTX, "rst", col.names = "Genes Overlapping") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

a=length(STRvsCTXrnaDown$symbol)
b=length(STRvsCTXcatdSigUp$symbol)
c=length(common_K27me3_STRvsCTX)

RNA=a-c
CATD=b-c
COMMON=c

knitr::kables(
  list(
    knitr::kable(RNA, "rst", col.names = "DEGs Downregulated"),
    knitr::kable(COMMON, "rst", col.names = "Overlaps DEGs + DEPGs"),
    knitr::kable(CATD, "rst", col.names = "DEPGs Upregulated"))
)

```

#### HPP vs VTA

```{r}
common_K27me3_HPPvsVTA <- intersect(HPPvsVTArnaDown$symbol, HPPvsVTAcatdSigUp$symbol)
knitr::kable(common_K27me3_HPPvsVTA, "rst", col.names = "Genes Overlapping") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

a=length(HPPvsVTArnaDown$symbol)
b=length(HPPvsVTAcatdSigUp$symbol)
c=length(common_K27me3_HPPvsVTA)

RNA=a-c
CATD=b-c
COMMON=c

knitr::kables(
  list(
    knitr::kable(RNA, "rst", col.names = "DEGs Downregulated"),
    knitr::kable(COMMON, "rst", col.names = "Overlaps DEGs + DEPGs"),
    knitr::kable(CATD, "rst", col.names = "DEPGs Upregulated"))
)
```

#### CTX vs VTA

```{r}
common_K27me3_CTXvsVTA <- intersect(CTXvsVTArnaDown$symbol, CTXvsVTAcatdSigUp$symbol)
knitr::kable(common_K27me3_CTXvsVTA, "rst", col.names = "Genes Overlapping") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

a=length(CTXvsVTArnaDown$symbol)
b=length(CTXvsVTAcatdSigUp$symbol)
c=length(common_K27me3_CTXvsVTA)

RNA=a-c
CATD=b-c
COMMON=c

knitr::kables(
  list(
    knitr::kable(RNA, "rst", col.names = "DEGs Downregulated"),
    knitr::kable(COMMON, "rst", col.names = "Overlaps DEGs + DEPGs"),
    knitr::kable(CATD, "rst", col.names = "DEPGs Upregulated"))
)

```

#### HPP vs PFC

```{r}
common_K27me3_HPPvsPFC <- intersect(HPPvsPFCrnaDown$symbol, HPPvsPFCcatdSigUp$symbol)
knitr::kable(common_K27me3_HPPvsPFC, "rst", col.names = "Genes Overlapping") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

a=length(HPPvsPFCrnaDown$symbol)
b=length(HPPvsPFCcatdSigUp$symbol)
c=length(common_K27me3_HPPvsPFC)

RNA=a-c
CATD=b-c
COMMON=c

knitr::kables(
  list(
    knitr::kable(RNA, "rst", col.names = "DEGs Downregulated"),
    knitr::kable(COMMON, "rst", col.names = "Overlaps DEGs + DEPGs"),
    knitr::kable(CATD, "rst", col.names = "DEPGs Upregulated"))
)

```

### Generate background lists for GO testing based on all significant results, regardless of overlaps for H3K27me3

```{r}

merged_data1 <- merge(PFCvsVTArnaSig, PFCvsVTAcatdSig, all = TRUE)
merged_data2 <- merge(HPPvsSTRrnaSig, HPPvsSTRcatdSig, all = TRUE)
merged_data3 <- merge(STRvsVTArnaSig, STRvsVTAcatdSig, all = TRUE)
merged_data4 <- merge(HPPvsCTXrnaSig, HPPvsCTXcatdSig, all = TRUE)
#merged_data5 <- merge(PFCvsCTXrnaSig, PFCvsCTXcatdSig, all = TRUE)
merged_data6 <- merge(STRvsPFCrnaSig, STRvsPFCcatdSig, all = TRUE)
merged_data7 <- merge(STRvsCTXrnaSig, STRvsCTXcatdSig, all = TRUE)
merged_data8 <- merge(HPPvsVTArnaSig, HPPvsVTAcatdSig, all = TRUE)
merged_data9 <- merge(CTXvsVTArnaSig, CTXvsVTAcatdSig, all = TRUE)
merged_data10 <- merge(HPPvsPFCrnaSig, HPPvsPFCcatdSig, all = TRUE)

merged_data11 <- merge(merged_data1, merged_data2, all = TRUE)
merged_data12 <- merge(merged_data11, merged_data3, all = TRUE)
merged_data13 <- merge(merged_data12, merged_data4, all = TRUE)
merged_data14 <- merged_data13 #merged_data5, all = TRUE)
merged_data15 <- merge(merged_data14, merged_data6, all = TRUE)
merged_data16 <- merge(merged_data15, merged_data7, all = TRUE)
merged_data17 <- merge(merged_data16, merged_data8, all = TRUE)
merged_data18 <- merge(merged_data17, merged_data9, all = TRUE)
merged_data19 <- merge(merged_data18, merged_data10, all = TRUE)


sum(is.na(merged_data19$entrez))
sum(duplicated(merged_data19$entrez))
length(rownames(merged_data19))

dup_rows <- duplicated(merged_data19$entrez)
merged_data_nodup <- merged_data19[!dup_rows, ]
na_rows <- is.na(merged_data_nodup$entrez)
merged_data_nodup_noNA <- merged_data_nodup[!na_rows, ]

sum(is.na(merged_data_nodup_noNA$entrez))
sum(duplicated(merged_data_nodup_noNA$entrez))
length(rownames(merged_data_nodup_noNA))

gene_matrix_background_K27me3 <- merged_data_nodup_noNA$entrez

```

## Correlating Significant Genes with Genes known to be regulated by H3K27ac
### Read in and filter necessary files

```{r}
PFCvsVTArna <- read.csv(paste0(basepath, "output/RNASeq_DEGs/Results_Sig_CSVs/Sig_Res_DEGs_PFC_vs_VTA.csv"), header = TRUE)
## Subset for Highly Significant Results (adjp < 0.05)
PFCvsVTArnaSig <- subset(PFCvsVTArna, padj < 0.05)
## Subset for Downregulated Genes (L2FC < 0)
PFCvsVTArnaSigUp <- subset(PFCvsVTArnaSig, log2FoldChange > 0)

PFCvsVTAcatd <- read.csv(paste0(basepath,"output/CATD_DEPGs/H3K27ac/Sig_Res_DEPGs_K27ac_PFC_vs_VTA.csv"), header = TRUE)
## Subset for Highly Significant Results (adjp < 0.05)
PFCvsVTAcatdSig <- subset(PFCvsVTAcatd, padj < 0.05)
## Subset for Downregulated Genes (L2FC < 0)
PFCvsVTAcatdSigUp <- subset(PFCvsVTAcatdSig, log2FoldChange > 0)

HPPvsSTRrna <- read.csv(paste0(basepath,"output/RNASeq_DEGs/Results_Sig_CSVs/Sig_Res_DEGs_HPP_vs_STR.csv"), header = TRUE)
## Subset for Highly Significant Results (adjp < 0.05)
HPPvsSTRrnaSig <- subset(HPPvsSTRrna, padj < 0.05)
## Subset for Downregulated Genes (L2FC < 0)
HPPvsSTRrnaSigUp <- subset(HPPvsSTRrnaSig, log2FoldChange > 0)

HPPvsSTRcatd <- read.csv(paste0(basepath,"output/CATD_DEPGs/H3K27ac/Sig_Res_DEPGs_K27ac_HPP_vs_STR.csv"), header = TRUE)
## Subset for Highly Significant Results (adjp < 0.05)
HPPvsSTRcatdSig <- subset(HPPvsSTRcatd, padj < 0.05)
## Subset for Downregulated Genes (L2FC < 0)
HPPvsSTRcatdSigUp <- subset(HPPvsSTRcatdSig, log2FoldChange > 0)

STRvsVTArna <- read.csv(paste0(basepath,"output/RNASeq_DEGs/Results_Sig_CSVs/Sig_Res_DEGs_STR_vs_VTA.csv"), header = TRUE)
## Subset for Highly Significant Results (adjp < 0.05)
STRvsVTArnaSig <- subset(STRvsVTArna, padj < 0.05)
## Subset for Downregulated Genes (L2FC < 0)
STRvsVTArnaSigUp <- subset(STRvsVTArnaSig, log2FoldChange > 0)

STRvsVTAcatd <- read.csv(paste0(basepath,"output/CATD_DEPGs/H3K27ac/Sig_Res_DEPGs_K27ac_STR_vs_VTA.csv"), header = TRUE)
## Subset for Highly Significant Results (adjp < 0.05)
STRvsVTAcatdSig <- subset(STRvsVTAcatd, padj < 0.05)
## Subset for Downregulated Genes (L2FC < 0)
STRvsVTAcatdSigUp <- subset(STRvsVTAcatdSig, log2FoldChange > 0)

HPPvsCTXrna <- read.csv(paste0(basepath,"output/RNASeq_DEGs/Results_Sig_CSVs/Sig_Res_DEGs_HPP_vs_Cortex.csv"), header = TRUE)
## Subset for Highly Significant Results (adjp < 0.05)
HPPvsCTXrnaSig <- subset(HPPvsCTXrna, padj < 0.05)
## Subset for Downregulated Genes (L2FC < 0)
HPPvsCTXrnaSigUp <- subset(HPPvsCTXrnaSig, log2FoldChange > 0)

HPPvsCTXcatd <- read.csv(paste0(basepath,"output/CATD_DEPGs/H3K27ac/Sig_Res_DEPGs_K27ac_HPP_vs_CTX.csv"), header = TRUE)
## Subset for Highly Significant Results (adjp < 0.05)
HPPvsCTXcatdSig <- subset(HPPvsCTXcatd, padj < 0.05)
## Subset for Downregulated Genes (L2FC < 0)
HPPvsCTXcatdSigUp <- subset(HPPvsCTXcatdSig, log2FoldChange > 0)

PFCvsCTXrna <- read.csv(paste0(basepath,"output/RNASeq_DEGs/Results_Sig_CSVs/Sig_Res_DEGs_PFC_vs_Cortex.csv"), header = TRUE)
## Subset for Highly Significant Results (adjp < 0.05)
PFCvsCTXrnaSig <- subset(PFCvsCTXrna, padj < 0.05)
## Subset for Downregulated Genes (L2FC < 0)
PFCvsCTXrnaSigUp <- subset(PFCvsCTXrnaSig, log2FoldChange > 0)

PFCvsCTXcatd <- read.csv(paste0(basepath,"output/CATD_DEPGs/H3K27ac/Sig_Res_DEPGs_K27ac_PFC_vs_CTX.csv"), header = TRUE)
## Subset for Highly Significant Results (adjp < 0.05)
PFCvsCTXcatdSig <- subset(PFCvsCTXcatd, padj < 0.05)
## Subset for Downregulated Genes (L2FC < 0)
PFCvsCTXcatdSigUp <- subset(PFCvsCTXcatdSig, log2FoldChange > 0)

STRvsPFCrna <-  read.csv(paste0(basepath,"output/RNASeq_DEGs/Results_Sig_CSVs/Sig_Res_DEGs_STR_vs_PFC.csv"), header = TRUE)
## Subset for Highly Significant Results (adjp < 0.05)
STRvsPFCrnaSig <- subset(STRvsPFCrna, padj < 0.05)
## Subset for Downregulated Genes (L2FC < 0)
STRvsPFCrnaSigUp <- subset(STRvsPFCrnaSig, log2FoldChange > 0)

STRvsPFCcatd <- read.csv(paste0(basepath,"output/CATD_DEPGs/H3K27ac/Sig_Res_DEPGs_K27ac_STR_vs_PFC.csv"), header = TRUE)
## Subset for Highly Significant Results (adjp < 0.05)
STRvsPFCcatdSig <- subset(STRvsPFCcatd, padj < 0.05)
## Subset for Downregulated Genes (L2FC < 0)
STRvsPFCcatdSigUp <- subset(STRvsPFCcatdSig, log2FoldChange > 0)

STRvsCTXrna <- read.csv(paste0(basepath,"output/RNASeq_DEGs/Results_Sig_CSVs/Sig_Res_DEGs_STR_vs_Cortex.csv"), header = TRUE)
## Subset for Highly Significant Results (adjp < 0.05)
STRvsCTXrnaSig <- subset(STRvsCTXrna, padj < 0.05)
## Subset for Downregulated Genes (L2FC < 0)
STRvsCTXrnaSigUp <- subset(STRvsCTXrnaSig, log2FoldChange > 0)

STRvsCTXcatd <- read.csv(paste0(basepath,"output/CATD_DEPGs/H3K27ac/Sig_Res_DEPGs_K27ac_STR_vs_CTX.csv"), header = TRUE)
## Subset for Highly Significant Results (adjp < 0.05)
STRvsCTXcatdSig <- subset(STRvsCTXcatd, padj < 0.05)
## Subset for Downregulated Genes (L2FC < 0)
STRvsCTXcatdSigUp <- subset(STRvsCTXcatdSig, log2FoldChange > 0)

HPPvsVTArna <- read.csv(paste0(basepath,"output/RNASeq_DEGs/Results_Sig_CSVs/Sig_Res_DEGs_HPP_vs_VTA.csv"), header = TRUE)
## Subset for Highly Significant Results (adjp < 0.05)
HPPvsVTArnaSig <- subset(HPPvsVTArna, padj < 0.05)
## Subset for Downregulated Genes (L2FC < 0)
HPPvsVTArnaSigUp <- subset(HPPvsVTArnaSig, log2FoldChange > 0)

HPPvsVTAcatd <- read.csv(paste0(basepath,"output/CATD_DEPGs/H3K27ac/Sig_Res_DEPGs_K27ac_HPP_vs_VTA.csv"), header = TRUE)
## Subset for Highly Significant Results (adjp < 0.05)
HPPvsVTAcatdSig <- subset(HPPvsVTAcatd, padj < 0.05)
## Subset for Downregulated Genes (L2FC < 0)
HPPvsVTAcatdSigUp <- subset(HPPvsVTAcatdSig, log2FoldChange > 0)

CTXvsVTArna <- read.csv(paste0(basepath,"output/RNASeq_DEGs/Results_Sig_CSVs/Sig_Res_DEGs_CTX_vs_VTA.csv"), header = TRUE)
## Subset for Highly Significant Results (adjp < 0.05)
CTXvsVTArnaSig <- subset(CTXvsVTArna, padj < 0.05)
## Subset for Downregulated Genes (L2FC < 0)
CTXvsVTArnaSigUp <- subset(CTXvsVTArnaSig, log2FoldChange > 0)

CTXvsVTAcatd <- read.csv(paste0(basepath,"output/CATD_DEPGs/H3K27ac/Sig_Res_DEPGs_K27ac_CTX_vs_VTA.csv"), header = TRUE)
## Subset for Highly Significant Results (adjp < 0.05)
CTXvsVTAcatdSig <- subset(CTXvsVTAcatd, padj < 0.05)
## Subset for Downregulated Genes (L2FC < 0)
CTXvsVTAcatdSigUp <- subset(CTXvsVTAcatdSig, log2FoldChange > 0)

HPPvsPFCrna <- read.csv(paste0(basepath,"output/RNASeq_DEGs/Results_Sig_CSVs/Sig_Res_DEGs_HPP_vs_PFC.csv"), header = TRUE)
## Subset for Highly Significant Results (adjp < 0.05)
HPPvsPFCrnaSig <- subset(HPPvsPFCrna, padj < 0.05)
## Subset for Downregulated Genes (L2FC < 0)
HPPvsPFCrnaSigUp <- subset(HPPvsPFCrnaSig, log2FoldChange > 0)

HPPvsPFCcatd <- read.csv(paste0(basepath,"output/CATD_DEPGs/H3K27ac/Sig_Res_DEPGs_K27ac_HPP_vs_PFC.csv"), header = TRUE)
## Subset for Highly Significant Results (adjp < 0.05)
HPPvsPFCcatdSig <- subset(HPPvsPFCcatd, padj < 0.05)
## Subset for Downregulated Genes (L2FC < 0)
HPPvsPFCcatdSigUp <- subset(HPPvsPFCcatdSig, log2FoldChange > 0)


```


### Check and Print All Overlaps based on Comparison for K27ac {.tabset}

#### PFC vs VTA

```{r echo=TRUE, paged.print=TRUE}
common_K27ac_PFCvsVTA <- intersect(PFCvsVTArnaSigUp$symbol, PFCvsVTAcatdSigUp$symbol)
knitr::kable(common_K27ac_PFCvsVTA, "rst", col.names = "Genes Overlapping") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

a=length(PFCvsVTArnaSigUp$symbol)
b=length(PFCvsVTAcatdSigUp$symbol)
c=length(common_K27ac_PFCvsVTA)

RNA=a-c
CATD=b-c
COMMON=c

knitr::kables(
  list(
    knitr::kable(RNA, "rst", col.names = "DEGs Upregulated"),
    knitr::kable(COMMON, "rst", col.names = "Overlaps DEGs + DEPGs"),
    knitr::kable(CATD, "rst", col.names = "DEPGs Upregulated"))
)

```

#### HPP vs STR

```{r}
common_K27ac_HPPvsSTR <- intersect(HPPvsSTRrnaSigUp$symbol, HPPvsSTRcatdSigUp$symbol)
knitr::kable(common_K27ac_HPPvsSTR, "rst", col.names = "Genes Overlapping") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

a=length(HPPvsSTRrnaSigUp$symbol)
b=length(HPPvsSTRcatdSigUp$symbol)
c=length(common_K27ac_HPPvsSTR)


RNA=a-c
CATD=b-c
COMMON=c

knitr::kables(
  list(
    knitr::kable(RNA, "rst", col.names = "DEGs Upregulated"),
    knitr::kable(COMMON, "rst", col.names = "Overlaps DEGs + DEPGs"),
    knitr::kable(CATD, "rst", col.names = "DEPGs Upregulated"))
)
```

#### STR vs VTA

```{r}
common_K27ac_STRvsVTA <- intersect(STRvsVTArnaSigUp$symbol, STRvsVTAcatdSigUp$symbol)
knitr::kable(common_K27ac_STRvsVTA, "rst", col.names = "Genes Overlapping") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

a=length(STRvsVTArnaSigUp$symbol)
b=length(STRvsVTAcatdSigUp$symbol)
c=length(common_K27ac_STRvsVTA)


RNA=a-c
CATD=b-c
COMMON=c

knitr::kables(
  list(
    knitr::kable(RNA, "rst", col.names = "DEGs Upregulated"),
    knitr::kable(COMMON, "rst", col.names = "Overlaps DEGs + DEPGs"),
    knitr::kable(CATD, "rst", col.names = "DEPGs Upregulated"))
)
```

#### HPP vs CTX

```{r}
common_K27ac_HPPvsCTX <- intersect(HPPvsCTXrnaSigUp$symbol, HPPvsCTXcatdSigUp$symbol)
knitr::kable(common_K27ac_HPPvsCTX, "rst", col.names = "Genes Overlapping") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

a=length(HPPvsCTXrnaSigUp$symbol)
b=length(HPPvsCTXcatdSigUp$symbol)
c=length(common_K27ac_HPPvsCTX)


RNA=a-c
CATD=b-c
COMMON=c

knitr::kables(
  list(
    knitr::kable(RNA, "rst", col.names = "DEGs Upregulated"),
    knitr::kable(COMMON, "rst", col.names = "Overlaps DEGs + DEPGs"),
    knitr::kable(CATD, "rst", col.names = "DEPGs Upregulated"))
)
```

#### PFC vs CTX

```{r}
common_K27ac_PFCvsCTX <- intersect(PFCvsCTXrnaSigUp$symbol, PFCvsCTXcatdSigUp$symbol)
knitr::kable(common_K27ac_PFCvsCTX, "rst", col.names = "Genes Overlapping") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

a=length(PFCvsCTXrnaSigUp$symbol)
b=length(PFCvsCTXcatdSigUp$symbol)
c=length(common_K27ac_PFCvsCTX)


RNA=a-c
CATD=b-c
COMMON=c

knitr::kables(
  list(
    knitr::kable(RNA, "rst", col.names = "DEGs Upregulated"),
    knitr::kable(COMMON, "rst", col.names = "Overlaps DEGs + DEPGs"),
    knitr::kable(CATD, "rst", col.names = "DEPGs Upregulated"))
)
```

#### STR vs PFC

```{r}
common_K27ac_STRvsPFC <- intersect(STRvsPFCrnaSigUp$symbol, STRvsPFCcatdSigUp$symbol)
knitr::kable(common_K27ac_STRvsPFC, "rst", col.names = "Genes Overlapping") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

a=length(STRvsPFCrnaSigUp$symbol)
b=length(STRvsPFCcatdSigUp$symbol)
c=length(common_K27ac_STRvsPFC)


RNA=a-c
CATD=b-c
COMMON=c

knitr::kables(
  list(
    knitr::kable(RNA, "rst", col.names = "DEGs Upregulated"),
    knitr::kable(COMMON, "rst", col.names = "Overlaps DEGs + DEPGs"),
    knitr::kable(CATD, "rst", col.names = "DEPGs Upregulated"))
)
```

#### STR vs CTX

```{r}
common_K27ac_STRvsCTX <- intersect(STRvsCTXrnaSigUp$symbol, STRvsCTXcatdSigUp$symbol)
knitr::kable(common_K27ac_STRvsCTX, "rst", col.names = "Genes Overlapping") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

a=length(STRvsCTXrnaSigUp$symbol)
b=length(STRvsCTXcatdSigUp$symbol)
c=length(common_K27ac_STRvsCTX)


RNA=a-c
CATD=b-c
COMMON=c

knitr::kables(
  list(
    knitr::kable(RNA, "rst", col.names = "DEGs Upregulated"),
    knitr::kable(COMMON, "rst", col.names = "Overlaps DEGs + DEPGs"),
    knitr::kable(CATD, "rst", col.names = "DEPGs Upregulated"))
)
```

#### HPP vs VTA

```{r}
common_K27ac_HPPvsVTA <- intersect(HPPvsVTArnaSigUp$symbol, HPPvsVTAcatdSigUp$symbol)
knitr::kable(common_K27ac_HPPvsVTA, "rst", col.names = "Genes Overlapping") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))


a=length(HPPvsVTArnaSigUp$symbol)
b=length(HPPvsVTAcatdSigUp$symbol)
c=length(common_K27ac_HPPvsVTA)


RNA=a-c
CATD=b-c
COMMON=c

knitr::kables(
  list(
    knitr::kable(RNA, "rst", col.names = "DEGs Upregulated"),
    knitr::kable(COMMON, "rst", col.names = "Overlaps DEGs + DEPGs"),
    knitr::kable(CATD, "rst", col.names = "DEPGs Upregulated"))
)
```

#### CTX vs VTA

```{r}
common_K27ac_CTXvsVTA <- intersect(CTXvsVTArnaSigUp$symbol, CTXvsVTAcatdSigUp$symbol)
knitr::kable(common_K27ac_CTXvsVTA, "rst", col.names = "Genes Overlapping") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

a=length(CTXvsVTArnaSigUp$symbol)
b=length(CTXvsVTAcatdSigUp$symbol)
c=length(common_K27ac_CTXvsVTA)


RNA=a-c
CATD=b-c
COMMON=c

knitr::kables(
  list(
    knitr::kable(RNA, "rst", col.names = "DEGs Upregulated"),
    knitr::kable(COMMON, "rst", col.names = "Overlaps DEGs + DEPGs"),
    knitr::kable(CATD, "rst", col.names = "DEPGs Upregulated"))
)
```

#### HPP vs PFC

```{r}
common_K27ac_HPPvsPFC <- intersect(HPPvsPFCrnaSigUp$symbol, HPPvsPFCcatdSigUp$symbol)
knitr::kable(common_K27ac_HPPvsPFC, "rst", col.names = "Genes Overlapping") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

a=length(HPPvsPFCrnaSigUp$symbol)
b=length(HPPvsPFCcatdSigUp$symbol)
c=length(common_K27ac_HPPvsPFC)


RNA=a-c
CATD=b-c
COMMON=c

knitr::kables(
  list(
    knitr::kable(RNA, "rst", col.names = "DEGs Upregulated"),
    knitr::kable(COMMON, "rst", col.names = "Overlaps DEGs + DEPGs"),
    knitr::kable(CATD, "rst", col.names = "DEPGs Upregulated"))
)
```

### Generate background lists for GO testing based on all significant results, regardless of overlaps for H3K27ac

```{r}
merged_data1 <- merge(PFCvsVTArnaSig, PFCvsVTAcatdSig, all = TRUE)
merged_data2 <- merge(HPPvsSTRrnaSig, HPPvsSTRcatdSig, all = TRUE)
merged_data3 <- merge(STRvsVTArnaSig, STRvsVTAcatdSig, all = TRUE)
merged_data4 <- merge(HPPvsCTXrnaSig, HPPvsCTXcatdSig, all = TRUE)
merged_data5 <- merge(PFCvsCTXrnaSig, PFCvsCTXcatdSig, all = TRUE)
merged_data6 <- merge(STRvsPFCrnaSig, STRvsPFCcatdSig, all = TRUE)
merged_data7 <- merge(STRvsCTXrnaSig, STRvsCTXcatdSig, all = TRUE)
merged_data8 <- merge(HPPvsVTArnaSig, HPPvsVTAcatdSig, all = TRUE)
merged_data9 <- merge(CTXvsVTArnaSig, CTXvsVTAcatdSig, all = TRUE)
merged_data10 <- merge(HPPvsPFCrnaSig, HPPvsPFCcatdSig, all = TRUE)

merged_data11 <- merge(merged_data1, merged_data2, all = TRUE)
merged_data12 <- merge(merged_data11, merged_data3, all = TRUE)
merged_data13 <- merge(merged_data12, merged_data4, all = TRUE)
merged_data14 <- merge(merged_data13, merged_data5, all = TRUE)
merged_data15 <- merge(merged_data14, merged_data6, all = TRUE)
merged_data16 <- merge(merged_data15, merged_data7, all = TRUE)
merged_data17 <- merge(merged_data16, merged_data8, all = TRUE)
merged_data18 <- merge(merged_data17, merged_data9, all = TRUE)
merged_data19 <- merge(merged_data18, merged_data10, all = TRUE)


sum(is.na(merged_data19$entrez))
sum(duplicated(merged_data19$entrez))
length(rownames(merged_data19))

dup_rows <- duplicated(merged_data19$entrez)
merged_data_nodup <- merged_data19[!dup_rows, ]
na_rows <- is.na(merged_data_nodup$entrez)
merged_data_nodup_noNA <- merged_data_nodup[!na_rows, ]

sum(is.na(merged_data_nodup_noNA$entrez))
sum(duplicated(merged_data_nodup_noNA$entrez))
length(rownames(merged_data_nodup_noNA))

gene_matrix_background_K27ac <- merged_data_nodup_noNA$entrez

```

## Selected Gene Ontology Analyses {.tabset}
### H3K27me3

```{r} 

length(gene_matrix_background_K27me3)
length(gene_matrix_background_K27ac)

df_common_K27me3_PFCvsVTA <- as.data.frame(common_K27me3_PFCvsVTA)
df_common_K27me3_PFCvsVTA$GeneID <- df_common_K27me3_PFCvsVTA$common_K27me3_PFCvsVTA

df_common_K27me3_HPPvsSTR <- as.data.frame(common_K27me3_HPPvsSTR)
df_common_K27me3_HPPvsSTR$GeneID <- df_common_K27me3_HPPvsSTR$common_K27me3_HPPvsSTR

df_common_K27me3_HPPvsCTX <- as.data.frame(common_K27me3_HPPvsCTX)
df_common_K27me3_HPPvsCTX$GeneID <- df_common_K27me3_HPPvsCTX$common_K27me3_HPPvsCTX

df_common_K27me3_HPPvsVTA <- as.data.frame(common_K27me3_HPPvsVTA)
df_common_K27me3_HPPvsVTA$GeneID <- df_common_K27me3_HPPvsVTA$common_K27me3_HPPvsVTA

df_common_K27me3_CTXvsVTA <- as.data.frame(common_K27me3_CTXvsVTA)
df_common_K27me3_CTXvsVTA$GeneID <- df_common_K27me3_CTXvsVTA$common_K27me3_CTXvsVTA

df_common_K27me3_HPPvsPFC <- as.data.frame(common_K27me3_HPPvsPFC)
df_common_K27me3_HPPvsPFC$GeneID <- df_common_K27me3_HPPvsPFC$common_K27me3_HPPvsPFC

df_common_K27me3_STRvsVTA <- as.data.frame(common_K27me3_STRvsVTA)
df_common_K27me3_STRvsVTA$GeneID <- df_common_K27me3_STRvsVTA$common_K27me3_STRvsVTA

#df_common_K27me3_PFCvsCTX <- as.data.frame(common_K27me3_PFCvsCTX)
#df_common_K27me3_PFCvsCTX$GeneID <- df_common_K27me3_PFCvsCTX$common_K27me3_PFCvsCTX

df_common_K27me3_STRvsPFC <- as.data.frame(common_K27me3_STRvsPFC)
df_common_K27me3_STRvsPFC$GeneID <- df_common_K27me3_STRvsPFC$common_K27me3_STRvsPFC

df_common_K27me3_STRvsCTX <- as.data.frame(common_K27me3_STRvsCTX)
df_common_K27me3_STRvsCTX$GeneID <- df_common_K27me3_STRvsCTX$common_K27me3_STRvsCTX

df_common_K27me3_PFCvsVTA$Entrez<- mapIds(x = org.Mm.eg.db, keys = df_common_K27me3_PFCvsVTA$GeneID, column = "ENTREZID", keytype = "SYMBOL", multiVals = "first")

df_common_K27me3_HPPvsSTR$Entrez<- mapIds(x = org.Mm.eg.db, keys = df_common_K27me3_HPPvsSTR$GeneID, column = "ENTREZID", keytype = "SYMBOL", multiVals = "first")

df_common_K27me3_HPPvsCTX$Entrez<- mapIds(x = org.Mm.eg.db, keys = df_common_K27me3_HPPvsCTX$GeneID, column = "ENTREZID", keytype = "SYMBOL", multiVals = "first")

df_common_K27me3_HPPvsVTA$Entrez<- mapIds(x = org.Mm.eg.db, keys = df_common_K27me3_HPPvsVTA$GeneID, column = "ENTREZID", keytype = "SYMBOL", multiVals = "first")

df_common_K27me3_CTXvsVTA$Entrez<- mapIds(x = org.Mm.eg.db, keys = df_common_K27me3_CTXvsVTA$GeneID, column = "ENTREZID", keytype = "SYMBOL", multiVals = "first")

df_common_K27me3_HPPvsPFC$Entrez<- mapIds(x = org.Mm.eg.db, keys = df_common_K27me3_HPPvsPFC$GeneID, column = "ENTREZID", keytype = "SYMBOL", multiVals = "first")

df_common_K27me3_STRvsVTA$Entrez<- mapIds(x = org.Mm.eg.db, keys = df_common_K27me3_STRvsVTA$GeneID, column = "ENTREZID", keytype = "SYMBOL", multiVals = "first")

#df_common_K27me3_PFCvsCTX$Entrez<- mapIds(x = org.Mm.eg.db, keys = df_common_K27me3_PFCvsCTX$GeneID, column = "ENTREZID", keytype = "SYMBOL", multiVals = "first")

#df_common_K27me3_STRvsPFC$Entrez<- mapIds(x = org.Mm.eg.db, keys = df_common_K27me3_STRvsPFC$GeneID, column = "ENTREZID", keytype = "SYMBOL", multiVals = "first")

#df_common_K27me3_STRvsCTX$Entrez<- mapIds(x = org.Mm.eg.db, keys = df_common_K27me3_STRvsCTX$GeneID, column = "ENTREZID", keytype = "SYMBOL", multiVals = "first")


go_df_common_K27me3_PFCvsVTA <- enrichGO(gene = df_common_K27me3_PFCvsVTA$Entrez, OrgDb = 'org.Mm.eg.db', readable = T, universe = gene_matrix_background_K27me3, ont = "ALL", pAdjustMethod = "fdr", pvalueCutoff = 0.05, qvalueCutoff = 0.10)

go_df_common_K27me3_HPPvsSTR <- enrichGO(gene = df_common_K27me3_HPPvsSTR$Entrez, OrgDb = 'org.Mm.eg.db', readable = T,universe = gene_matrix_background_K27me3, ont = "ALL", pAdjustMethod = "fdr", pvalueCutoff = 0.05, qvalueCutoff = 0.10)

go_df_common_K27me3_HPPvsCTX <- enrichGO(gene = df_common_K27me3_HPPvsCTX$Entrez, OrgDb = 'org.Mm.eg.db', readable = T, universe = gene_matrix_background_K27me3, ont = "ALL", pAdjustMethod = "fdr", pvalueCutoff = 0.05, qvalueCutoff = 0.10)

go_df_common_K27me3_HPPvsVTA <- enrichGO(gene = df_common_K27me3_HPPvsVTA$Entrez, OrgDb = 'org.Mm.eg.db', readable = T, universe = gene_matrix_background_K27me3, ont = "ALL", pAdjustMethod = "fdr", pvalueCutoff = 0.05, qvalueCutoff = 0.10)

go_df_common_K27me3_CTXvsVTA <- enrichGO(gene = df_common_K27me3_CTXvsVTA$Entrez, OrgDb = 'org.Mm.eg.db', readable = T, universe = gene_matrix_background_K27me3, ont = "ALL", pAdjustMethod = "fdr", pvalueCutoff = 0.05, qvalueCutoff = 0.10)

go_df_common_K27me3_HPPvsPFC <- enrichGO(gene = df_common_K27me3_HPPvsPFC$Entrez, OrgDb = 'org.Mm.eg.db', readable = T, universe = gene_matrix_background_K27me3, ont = "ALL", pAdjustMethod = "fdr", pvalueCutoff = 0.05, qvalueCutoff = 0.10)

go_df_common_K27me3_STRvsVTA <- enrichGO(gene = df_common_K27me3_STRvsVTA$Entrez, OrgDb = 'org.Mm.eg.db', readable = T, universe = gene_matrix_background_K27me3, ont = "ALL", pAdjustMethod = "fdr", pvalueCutoff = 0.05, qvalueCutoff = 0.10)

#go_df_common_K27me3_PFCvsCTX <- enrichGO(gene = df_common_K27me3_PFCvsCTX$Entrez, OrgDb = 'org.Mm.eg.db', readable = T, universe = gene_matrix_background_K27me3, ont = "ALL", pAdjustMethod = "fdr", pvalueCutoff = 0.05, qvalueCutoff = 0.10)

#go_df_common_K27me3_STRvsPFC <- enrichGO(gene = df_common_K27me3_STRvsPFC$Entrez, OrgDb = 'org.Mm.eg.db', readable = T, universe = gene_matrix_background_K27me3, ont = "ALL", pAdjustMethod = "fdr", pvalueCutoff = 0.05, qvalueCutoff = 0.10)

#go_df_common_K27me3_STRvsCTX <- enrichGO(gene = df_common_K27me3_STRvsCTX$Entrez, OrgDb = 'org.Mm.eg.db', readable = T, universe = gene_matrix_background_K27me3, ont = "ALL", pAdjustMethod = "fdr", pvalueCutoff = 0.05, qvalueCutoff = 0.10)


##################################################################################### 

go_enrich_dataset_K27me3_PFCvsVTA <- as.data.frame(go_df_common_K27me3_PFCvsVTA)
go_enrich_dataset_K27me3_HPPvsSTR <-as.data.frame(go_df_common_K27me3_HPPvsSTR)
go_enrich_dataset_K27me3_CTXvsVTA <- as.data.frame(go_df_common_K27me3_CTXvsVTA)
go_enrich_dataset_K27me3_HPPvsPFC <- as.data.frame(go_df_common_K27me3_HPPvsPFC)
go_enrich_dataset_K27me3_HPPvsCTX <- as.data.frame(go_df_common_K27me3_HPPvsCTX)
go_enrich_dataset_K27me3_HPPvsVTA <- as.data.frame(go_df_common_K27me3_HPPvsVTA)
go_enrich_dataset_K27me3_STRvsVTA <- as.data.frame(go_df_common_K27me3_STRvsVTA)
## No Enrichment results below
#go_enrich_dataset_K27me3_PFCvsCTX <- as.data.frame(go_df_common_K27me3_PFCvsCTX)
#go_enrich_dataset_K27me3_STRvsPFC <- as.data.frame(go_df_common_K27me3_STRvsPFC)
#go_enrich_dataset_K27me3_STRvsCTX <- as.data.frame(go_df_common_K27me3_STRvsCTX)

go_enrich_dataset_K27me3_PFCvsVTA$Comparison <- "PFCvsVTA"
go_enrich_dataset_K27me3_HPPvsSTR$Comparison <- "HPPvsSTR"
go_enrich_dataset_K27me3_CTXvsVTA$Comparison <- "CTXvsVTA"
go_enrich_dataset_K27me3_HPPvsPFC$Comparison <- "HPPvsPFC"
go_enrich_dataset_K27me3_HPPvsCTX$Comparison <- "HPPvsCTX"
go_enrich_dataset_K27me3_HPPvsVTA$Comparison <- "HPPvsVTA"
go_enrich_dataset_K27me3_STRvsVTA$Comparison <- "STRvsVTA"
#go_enrich_dataset_K27me3_PFCvsCTX$Comparison <- "PFCvsCTX"
#go_enrich_dataset_K27me3_STRvsPFC$Comparison <- "STRvsPFC"
#go_enrich_dataset_K27me3_STRvsCTX$Comparison <- "STRvsCTX"

go_enrich_dataset_K27me3_PFCvsVTA$Mark <- "H3K27me3"
go_enrich_dataset_K27me3_HPPvsSTR$Mark <- "H3K27me3"
go_enrich_dataset_K27me3_CTXvsVTA$Mark <- "H3K27me3"
go_enrich_dataset_K27me3_HPPvsPFC$Mark <- "H3K27me3"
go_enrich_dataset_K27me3_HPPvsCTX$Mark <- "H3K27me3"
go_enrich_dataset_K27me3_HPPvsVTA$Mark <- "H3K27me3"
go_enrich_dataset_K27me3_STRvsVTA$Mark <- "H3K27me3"
#go_enrich_dataset_K27me3_PFCvsCTX$Mark <- "H3K27me3"
#go_enrich_dataset_K27me3_STRvsPFC$Mark <- "H3K27me3"
#go_enrich_dataset_K27me3_STRvsCTX$Mark <- "H3K27me3"

GO_K27me3_Overlap_Combined1 <- rbind(go_enrich_dataset_K27me3_PFCvsVTA, go_enrich_dataset_K27me3_HPPvsSTR) 
GO_K27me3_Overlap_Combined2 <- rbind(GO_K27me3_Overlap_Combined1, go_enrich_dataset_K27me3_CTXvsVTA)
GO_K27me3_Overlap_Combined3 <- rbind(GO_K27me3_Overlap_Combined2, go_enrich_dataset_K27me3_HPPvsPFC) 
GO_K27me3_Overlap_Combined4 <- rbind(GO_K27me3_Overlap_Combined3, go_enrich_dataset_K27me3_HPPvsCTX)
GO_K27me3_Overlap_Combined5 <- rbind(GO_K27me3_Overlap_Combined4, go_enrich_dataset_K27me3_HPPvsVTA) 
GO_K27me3_Overlap_Final <- rbind(GO_K27me3_Overlap_Combined5, go_enrich_dataset_K27me3_STRvsVTA)

```

### H3K27ac

```{r}

df_common_K27ac_PFCvsVTA <- as.data.frame(common_K27ac_PFCvsVTA)
df_common_K27ac_PFCvsVTA$GeneID <- df_common_K27ac_PFCvsVTA$common_K27ac_PFCvsVTA

df_common_K27ac_HPPvsSTR <- as.data.frame(common_K27ac_HPPvsSTR)
df_common_K27ac_HPPvsSTR$GeneID <- df_common_K27ac_HPPvsSTR$common_K27ac_HPPvsSTR

df_common_K27ac_HPPvsCTX <- as.data.frame(common_K27ac_HPPvsCTX)
df_common_K27ac_HPPvsCTX$GeneID <- df_common_K27ac_HPPvsCTX$common_K27ac_HPPvsCTX

df_common_K27ac_HPPvsVTA <- as.data.frame(common_K27ac_HPPvsVTA)
df_common_K27ac_HPPvsVTA$GeneID <- df_common_K27ac_HPPvsVTA$common_K27ac_HPPvsVTA

df_common_K27ac_CTXvsVTA <- as.data.frame(common_K27ac_CTXvsVTA)
df_common_K27ac_CTXvsVTA$GeneID <- df_common_K27ac_CTXvsVTA$common_K27ac_CTXvsVTA

df_common_K27ac_HPPvsPFC <- as.data.frame(common_K27ac_HPPvsPFC)
df_common_K27ac_HPPvsPFC$GeneID <- df_common_K27ac_HPPvsPFC$common_K27ac_HPPvsPFC

df_common_K27ac_STRvsVTA <- as.data.frame(common_K27ac_STRvsVTA)
df_common_K27ac_STRvsVTA$GeneID <- df_common_K27ac_STRvsVTA$common_K27ac_STRvsVTA

df_common_K27ac_PFCvsCTX <- as.data.frame(common_K27ac_PFCvsCTX)
df_common_K27ac_PFCvsCTX$GeneID <- df_common_K27ac_PFCvsCTX$common_K27ac_PFCvsCTX

df_common_K27ac_STRvsPFC <- as.data.frame(common_K27ac_STRvsPFC)
df_common_K27ac_STRvsPFC$GeneID <- df_common_K27ac_STRvsPFC$common_K27ac_STRvsPFC

df_common_K27ac_STRvsCTX <- as.data.frame(common_K27ac_STRvsCTX)
df_common_K27ac_STRvsCTX$GeneID <- df_common_K27ac_STRvsCTX$common_K27ac_STRvsCTX

df_common_K27ac_PFCvsVTA$Entrez<- mapIds(x = org.Mm.eg.db, keys = df_common_K27ac_PFCvsVTA$GeneID, column = "ENTREZID", keytype = "SYMBOL", multiVals = "first")

df_common_K27ac_HPPvsSTR$Entrez<- mapIds(x = org.Mm.eg.db, keys = df_common_K27ac_HPPvsSTR$GeneID, column = "ENTREZID", keytype = "SYMBOL", multiVals = "first")

df_common_K27ac_HPPvsCTX$Entrez<- mapIds(x = org.Mm.eg.db, keys = df_common_K27ac_HPPvsCTX$GeneID, column = "ENTREZID", keytype = "SYMBOL", multiVals = "first")

df_common_K27ac_HPPvsVTA$Entrez<- mapIds(x = org.Mm.eg.db, keys = df_common_K27ac_HPPvsVTA$GeneID, column = "ENTREZID", keytype = "SYMBOL", multiVals = "first")

df_common_K27ac_CTXvsVTA$Entrez<- mapIds(x = org.Mm.eg.db, keys = df_common_K27ac_CTXvsVTA$GeneID, column = "ENTREZID", keytype = "SYMBOL", multiVals = "first")

df_common_K27ac_HPPvsPFC$Entrez<- mapIds(x = org.Mm.eg.db, keys = df_common_K27ac_HPPvsPFC$GeneID, column = "ENTREZID", keytype = "SYMBOL", multiVals = "first")

df_common_K27ac_STRvsVTA$Entrez<- mapIds(x = org.Mm.eg.db, keys = df_common_K27ac_STRvsVTA$GeneID, column = "ENTREZID", keytype = "SYMBOL", multiVals = "first")

#df_common_K27ac_PFCvsCTX$Entrez<- mapIds(x = org.Mm.eg.db, keys = df_common_K27ac_PFCvsCTX$GeneID, column = "ENTREZID", keytype = "SYMBOL", multiVals = "first")

df_common_K27ac_STRvsPFC$Entrez<- mapIds(x = org.Mm.eg.db, keys = df_common_K27ac_STRvsPFC$GeneID, column = "ENTREZID", keytype = "SYMBOL", multiVals = "first")

#df_common_K27ac_STRvsCTX$Entrez<- mapIds(x = org.Mm.eg.db, keys = df_common_K27ac_STRvsCTX$GeneID, column = "ENTREZID", keytype = "SYMBOL", multiVals = "first")

go_df_common_K27ac_PFCvsVTA <- enrichGO(gene = df_common_K27ac_PFCvsVTA$Entrez, OrgDb = 'org.Mm.eg.db', readable = T, universe = gene_matrix_background_K27ac, ont = "ALL", pAdjustMethod = "fdr", pvalueCutoff = 0.05, qvalueCutoff = 0.10)

go_df_common_K27ac_HPPvsSTR <- enrichGO(gene = df_common_K27ac_HPPvsSTR$Entrez, OrgDb = 'org.Mm.eg.db', readable = T, universe = gene_matrix_background_K27ac, ont = "ALL", pAdjustMethod = "fdr", pvalueCutoff = 0.05, qvalueCutoff = 0.10)

go_df_common_K27ac_HPPvsCTX <- enrichGO(gene = df_common_K27ac_HPPvsCTX$Entrez, OrgDb = 'org.Mm.eg.db', readable = T, universe = gene_matrix_background_K27ac, ont = "ALL", pAdjustMethod = "fdr", pvalueCutoff = 0.05, qvalueCutoff = 0.10)

go_df_common_K27ac_HPPvsVTA <- enrichGO(gene = df_common_K27ac_HPPvsVTA$Entrez, OrgDb = 'org.Mm.eg.db', readable = T, universe = gene_matrix_background_K27ac, ont = "ALL", pAdjustMethod = "fdr", pvalueCutoff = 0.05, qvalueCutoff = 0.10)

go_df_common_K27ac_CTXvsVTA <- enrichGO(gene = df_common_K27ac_CTXvsVTA$Entrez, OrgDb = 'org.Mm.eg.db', readable = T, universe = gene_matrix_background_K27ac, ont = "ALL", pAdjustMethod = "fdr", pvalueCutoff = 0.05, qvalueCutoff = 0.10)

go_df_common_K27ac_HPPvsPFC <- enrichGO(gene = df_common_K27ac_HPPvsPFC$Entrez, OrgDb = 'org.Mm.eg.db', readable = T, universe = gene_matrix_background_K27ac, ont = "ALL", pAdjustMethod = "fdr", pvalueCutoff = 0.05, qvalueCutoff = 0.10)

go_df_common_K27ac_STRvsVTA <- enrichGO(gene = df_common_K27ac_STRvsVTA$Entrez, OrgDb = 'org.Mm.eg.db', readable = T, universe = gene_matrix_background_K27ac, ont = "ALL", pAdjustMethod = "fdr", pvalueCutoff = 0.05, qvalueCutoff = 0.10)

#go_df_common_K27ac_PFCvsCTX <- enrichGO(gene = df_common_K27ac_PFCvsCTX$Entrez, OrgDb = 'org.Mm.eg.db', readable = T, universe = gene_matrix_background_K27ac, ont = "ALL", pAdjustMethod = "fdr", pvalueCutoff = 0.05, qvalueCutoff = 0.10)

go_df_common_K27ac_STRvsPFC <- enrichGO(gene = df_common_K27ac_STRvsPFC$Entrez, OrgDb = 'org.Mm.eg.db', readable = T, universe = gene_matrix_background_K27ac, ont = "ALL", pAdjustMethod = "fdr", pvalueCutoff = 0.05, qvalueCutoff = 0.10)

#go_df_common_K27ac_STRvsCTX <- enrichGO(gene = df_common_K27ac_STRvsCTX$Entrez, OrgDb = 'org.Mm.eg.db', readable = T, universe = gene_matrix_background_K27ac, ont = "ALL", pAdjustMethod = "fdr", pvalueCutoff = 0.05, qvalueCutoff = 0.10)

######################################################################################################################################## 

go_enrich_dataset_K27ac_PFCvsVTA <- as.data.frame(go_df_common_K27ac_PFCvsVTA)
go_enrich_dataset_K27ac_HPPvsSTR <- as.data.frame(go_df_common_K27ac_HPPvsSTR)
go_enrich_dataset_K27ac_CTXvsVTA <- as.data.frame(go_df_common_K27ac_CTXvsVTA)
go_enrich_dataset_K27ac_HPPvsPFC <- as.data.frame(go_df_common_K27ac_HPPvsPFC)
go_enrich_dataset_K27ac_HPPvsCTX <- as.data.frame(go_df_common_K27ac_HPPvsCTX)
go_enrich_dataset_K27ac_HPPvsVTA <- as.data.frame(go_df_common_K27ac_HPPvsVTA)
go_enrich_dataset_K27ac_STRvsVTA <- as.data.frame(go_df_common_K27ac_STRvsVTA)
go_enrich_dataset_K27ac_STRvsPFC <- as.data.frame(go_df_common_K27ac_STRvsPFC) 
## No Enrichment results below
#go_enrich_dataset_K27ac_PFCvsCTX <- as.data.frame(go_df_common_K27ac_PFCvsCTX)
#go_enrich_dataset_K27ac_STRvsCTX <- as.data.frame(go_df_common_K27ac_STRvsCTX)

#go_enrich_dataset_K27ac_PFCvsVTA$Comparison <- "PFCvsVTA"
go_enrich_dataset_K27ac_HPPvsSTR$Comparison <- "HPPvsSTR"
go_enrich_dataset_K27ac_CTXvsVTA$Comparison <- "CTXvsVTA"
go_enrich_dataset_K27ac_HPPvsPFC$Comparison <- "HPPvsPFC"
go_enrich_dataset_K27ac_HPPvsCTX$Comparison <- "HPPvsCTX"
go_enrich_dataset_K27ac_HPPvsVTA$Comparison <- "HPPvsVTA"
go_enrich_dataset_K27ac_STRvsVTA$Comparison <- "STRvsVTA"
go_enrich_dataset_K27ac_STRvsPFC$Comparison <- "STRvsPFC"
#go_enrich_dataset_K27ac_PFCvsCTX$Comparison <- "PFCvsCTX"
#go_enrich_dataset_K27ac_STRvsCTX$Comparison <- "STRvsCTX"

#go_enrich_dataset_K27ac_PFCvsVTA$Mark <- "H3K27ac"
go_enrich_dataset_K27ac_HPPvsSTR$Mark <- "H3K27ac"
go_enrich_dataset_K27ac_CTXvsVTA$Mark <- "H3K27ac"
go_enrich_dataset_K27ac_HPPvsPFC$Mark <- "H3K27ac"
go_enrich_dataset_K27ac_HPPvsCTX$Mark <- "H3K27ac"
go_enrich_dataset_K27ac_HPPvsVTA$Mark <- "H3K27ac"
go_enrich_dataset_K27ac_STRvsVTA$Mark <- "H3K27ac"
go_enrich_dataset_K27ac_STRvsPFC$Mark <- "H3K27ac"
#go_enrich_dataset_K27ac_PFCvsCTX$Mark <- "H3K27ac"
#go_enrich_dataset_K27ac_STRvsCTX$Mark <- "H3K27ac"

GO_K27ac_Overlap_Combined1 <- (go_enrich_dataset_K27ac_HPPvsSTR) 
GO_K27ac_Overlap_Combined2 <- rbind(GO_K27ac_Overlap_Combined1, go_enrich_dataset_K27ac_CTXvsVTA)
GO_K27ac_Overlap_Combined3 <- rbind(GO_K27ac_Overlap_Combined2, go_enrich_dataset_K27ac_HPPvsPFC) 
GO_K27ac_Overlap_Combined4 <- rbind(GO_K27ac_Overlap_Combined3, go_enrich_dataset_K27ac_HPPvsCTX)
GO_K27ac_Overlap_Combined5 <- rbind(GO_K27ac_Overlap_Combined4, go_enrich_dataset_K27ac_HPPvsVTA)
GO_K27ac_Overlap_Combined6 <- rbind(GO_K27ac_Overlap_Combined5, go_enrich_dataset_K27ac_STRvsVTA)
GO_K27ac_Overlap_Final <- rbind(GO_K27ac_Overlap_Combined6, go_enrich_dataset_K27ac_STRvsPFC)

```

### Combined Plots

```{r fig.height=12, fig.width=12}

########################################################################################################################################## 
GP_BothMarks_Overlap_Final <- rbind(GO_K27me3_Overlap_Final,GO_K27ac_Overlap_Final)
#write.csv(GP_BothMarks_Overlap_Final, "output/RNASeq_CATD_Overlaps/GOPathways_BothMarks_BasedonVennDiagrams_FullList.csv")

########################################################################################################################################## 

K27me3_filt <- GO_K27me3_Overlap_Final %>%
  dplyr::filter(Count >=5)

K27me3_top_desc <- K27me3_filt %>%
  group_by(Description) %>%
  summarise(best_p = min(p.adjust, na.rm = TRUE), .groups = "drop") %>%
  arrange(best_p, Description) %>%
  slice_head(n = 25) %>%
  pull(Description)

K27me3_result_top25_expand <- K27me3_filt %>%
  dplyr::filter(Description %in% K27me3_top_desc) %>%
  arrange(Description, p.adjust)

K27me3_summary_top25 <- K27me3_filt %>%
  dplyr::filter(Description %in% K27me3_top_desc) %>%
  group_by(Description) %>%
  summarise(
    best_p = min(p.adjust, na.rm = TRUE),
    n_rows = n(),                       
    n_comp = n_distinct(Comparison),    
    .groups = "drop"
  ) %>%
  arrange(best_p, Description)

########################################################################################################################################## 

K27ac_filt <- GO_K27ac_Overlap_Final %>%
  dplyr::filter(Count >=5)

K27ac_top_desc <- K27ac_filt %>%
  group_by(Description) %>%
  summarise(best_p = min(p.adjust, na.rm = TRUE), .groups = "drop") %>%
  arrange(best_p, Description) %>%
  slice_head(n = 25) %>%
  pull(Description)

K27ac_result_top25_expand <- K27ac_filt %>%
  dplyr::filter(Description %in% K27ac_top_desc) %>%
  arrange(Description, p.adjust)

K27ac_summary_top25 <- K27ac_filt %>%
  dplyr::filter(Description %in% K27ac_top_desc) %>%
  group_by(Description) %>%
  summarise(
    best_p = min(p.adjust, na.rm = TRUE),
    n_rows = n(),                     
    n_comp = n_distinct(Comparison),    
    .groups = "drop"
  ) %>%
  arrange(best_p, Description)

########################################################################################################################################## 

GO_BothMarks_Overlap_Final_Top25Each <- rbind(K27me3_result_top25_expand, K27ac_result_top25_expand)

#write.csv(GO_BothMarks_Overlap_Final_Top25Each, "output/RNASeq_CATD_Overlaps/GOPathways_BothMarks_BasedonVennDiagrams_FilteredTop25.csv")

########################################################################################################################################## 



GO_BothMarks_Overlap_Final_Top25Each$Description = str_to_sentence(GO_BothMarks_Overlap_Final_Top25Each$Description)

GO_BothMarks_Overlap_Final_Top25Each$Mark <- as.character(GO_BothMarks_Overlap_Final_Top25Each$Mark)
GO_BothMarks_Overlap_Final_Top25Each$Mark <- factor(GO_BothMarks_Overlap_Final_Top25Each$Mark, levels=unique(GO_BothMarks_Overlap_Final_Top25Each$Mark))
GO_BothMarks_Overlap_Final_Top25Each$Description <- as.character(GO_BothMarks_Overlap_Final_Top25Each$Description)
GO_BothMarks_Overlap_Final_Top25Each$Description <- factor(GO_BothMarks_Overlap_Final_Top25Each$Description, levels=unique(GO_BothMarks_Overlap_Final_Top25Each$Description))

S1 <- ggplot(GO_BothMarks_Overlap_Final_Top25Each, aes(x= Comparison, y=Description, size=Count, color=qvalue, group=Mark))+
  geom_point(alpha = 0.8) + 
  theme_bw()+ 
  theme(legend.position = "right", legend.direction = "vertical", legend.justification = "left")+
  facet_wrap(~Mark, scales = "free_y")

S1 = S1+scale_color_gradient(low = "mediumblue", high = "red2", space ="Lab") 
S1+scale_size(range = c(2, 5)) 

#pdf("output/RNASeq_CATD_Overlaps/GO_SignOverlaps_DotPlot_Filtered.pdf", width = 25, height = 15)
S1+scale_size(range = c(5, 10)) 
#dev.off()


```

# Package Versions

```{r Save Package Version Info, echo=TRUE, message=TRUE, warning=FALSE}

projdir <- "/home/avm27/Documents/Raw_Sequencing_Data/BrainRegionMicroglia/RegionalMicroglialTranscriptomicsandEpigenomics"

#Record Package Versions Used in this analysis
index7_packages <- c(
  "AnnotationDbi",
  "clusterProfiler",
  "conflicted",
  "dplyr",
  "ggplot2",
  "kableExtra",
  "knitr",
  "org.Mm.eg.db",
  "stringr",
  "workflowr"
)

# Retrieve Each Package Version
get_package_version <- function(package_name) {

  package_path <- find.package(
    package_name,
    quiet = TRUE
  )

  package_loaded <- package_name %in% loadedNamespaces()

  if (length(package_path) == 0L) {
    return(
      data.frame(
        package = package_name,
        installed = FALSE,
        loaded = FALSE,
        version = NA_character_,
        library_path = NA_character_,
        stringsAsFactors = FALSE
      )
    )
  }

  package_path <- package_path[[1]]

  data.frame(
    package = package_name,
    installed = TRUE,
    loaded = package_loaded,
    version = as.character(
      utils::packageVersion(
        package_name,
        lib.loc = dirname(package_path)
      )
    ),
    library_path = dirname(package_path),
    stringsAsFactors = FALSE
  )
}


# Collect Package and R Environment Versions
index7_package_versions <- do.call(
  rbind,
  lapply(
    index7_packages,
    get_package_version
  )
)

index7_environment_versions <- data.frame(
  R_version = paste(
    R.version$major,
    R.version$minor,
    sep = "."
  ),
  Bioconductor_version = if (
    requireNamespace("BiocManager", quietly = TRUE)
  ) {
    as.character(BiocManager::version())
  } else {
    NA_character_
  },
  platform = R.version$platform,
  stringsAsFactors = FALSE
)


# Save Version Records

utils::write.csv(
  index7_package_versions,
  file = paste0(projdir, "/code/RPackageVersions/index7_package_versions.csv"),
  row.names = FALSE
)

utils::write.csv(
  index7_environment_versions,
  file = paste0(projdir, "/code/RPackageVersions/index7_R_and_Bioconductor_versions.csv"),
  row.names = FALSE
)

capture.output(
  sessionInfo(),
  file = paste0(projdir, "/code/RPackageVersions/index7_sessionInfo.txt")
)



# Print Results
print(index7_environment_versions, row.names = FALSE)
print(index7_package_versions, row.names = FALSE)

```

# Session Info

```{r Print Session Info, echo=TRUE, message=TRUE, warning=FALSE}
sessionInfo()
```