---
title: "Combined H3K27me3 and H3K27ac DEPGs Analysis"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: false
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(gprofiler2)
library(DESeq2)
library(ggplot2)
library(clusterProfiler)
library(biomaRt)
library(ReactomePA)
library(DOSE)
options(connectionObserver = NULL)
library(org.Mm.eg.db)
library(tximport)
library(ggsci)
library(pheatmap)
library(genefilter)
library(RColorBrewer)
library(GO.db)
library(topGO)
library(dplyr)
library(gage)
library(pathview)
library(WGCNA)
library(tidyr)
library(enrichplot)
library(ggnewscale)
library(SPIA)
library(ggpubr)
library(apeglm)
library(GOSemSim)
library(edgeR)
library(tweeDEseqCountData)
library(statmod)
library(org.Mm.eg.db)
library(tidyverse)
library(pheatmap)
library(gplots)
library(Mus.musculus)
library(Glimma)
library(RColorBrewer)
library(clusterProfiler)
library(ReactomePA)
library(enrichplot)
library(ggnewscale)
library(knitr)
library(tables)
library(vidger)
library(kableExtra)
library(regionReport)

#remotes::install_github("YuLab-SMU/clusterProfiler") 

```



# DESeq2 Analysis for H3K27me3 and H3K27ac Combined
## Loading in required files -- Comes from analysis/index3.Rmd

Building DESeq2 input files from peak count matrix generated by counting number of reads from BAM files that fell into significantly called peaks and then mapping the chromosomal locations to the respective gene.

```{r DESeq2 Build, message=FALSE, warning=FALSE, include=FALSE}

setwd("/home/avm27/Documents/Raw_Sequencing_Data/BrainRegionMicroglia/RegionalMicroglialTranscriptomicsandEpigenomics")
basepath="/home/avm27/Documents/Raw_Sequencing_Data/BrainRegionMicroglia/RegionalMicroglialTranscriptomicsandEpigenomics/"

colData <- read.csv(paste0(basepath, "data/CATD_DESeq_Data/sample_info_combined.csv"), sep = ",", row.names = 1)
countData <-as.matrix(read.csv(paste0(basepath, "data/CATD_DESeq_Data/peak_count_matrix_CATD_Final.csv"), row.names = "gene_id", sep = ","))

sum(is.na(countData))
colnames(countData)
rownames(colData)
all(rownames(colData) %in% colnames(countData))
countData <- countData[, rownames(colData)]
all(rownames(colData) == colnames(countData))

```

```{r DESeq2 Analysis, echo=FALSE, message=FALSE, warning=FALSE}

dds <- DESeqDataSetFromMatrix(countData = countData, colData = colData, design = ~mark)

keep <- rowSums(counts(dds)) >= 15
dds <- dds[keep,]

dds$mark <- relevel(dds$mark, ref = "K27ac")
dds <- DESeq(dds)


```


# Plot Estimates from Results

```{r Results, echo=FALSE, results='asis'}
## Look at Results
res <- results(dds, name = "mark_K27me3_vs_K27ac")

#summary(res)

```

# Annotate Results Files

```{r Annotate Results, message=FALSE, warning=FALSE, include=FALSE, results='asis'}
## Make new rownames file and split based on pipe from dds file

library(dplyr)
library(tidyr)


res$symbol <- row.names(res)


res$description <- mapIds(x = org.Mm.eg.db,
                              keys = res$symbol,
                              column = "GENENAME",
                              keytype = "SYMBOL",
                              multiVals = "first")

    # Add ENTREZ ID
res$entrez <- mapIds(x = org.Mm.eg.db,
                      keys = res$symbol,
                     column = "ENTREZID",
                       keytype = "SYMBOL",
                       multiVals = "first")


    # Add ENSEMBL ID  
res$ensembl <- mapIds(x = org.Mm.eg.db,
                         keys = res$entrez,
                       column = "ENSEMBL",
                         keytype = "ENTREZID",
                         multiVals = "first")


```

After annotation results are subset to only view the significantly differentially expressed peaks in genes with an adjusted p-value \> 0.05.

```{r Subset Significant Results, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
## Subset for significant genes only
results_sig <- subset(res, padj < 0.05)
#summary(results_sig)

```

# Visualizing Differentially Deposited Peaks in Genes
## Heatmap

```{r Dual Heatmap, echo=FALSE, message=FALSE, warning=FALSE}

library(dplyr)
library(tidyr)
library(ggplot2)
library(ggrepel)
library(RColorBrewer)
library(pheatmap)
library(DEGreport)
library(reshape2)

level_order <- c('Striatum', 'PreFrontalCorex', 'Hippocampus', 'VTA', 'Cortex') 

# Define custom colors for each condition
custom_colors <- c("Cortex" = "#FF9289", 
                   "Hippocampus" = "#FF8AFF", 
                   "PreFrontalCortex" = "#00DB98", 
                   "Striatum" = "#00CBFF", 
                   "VTA" = "#BEC100")

custom_colors <- c("CTX" = "#FF9289", 
                   "HPP" = "#FF8AFF", 
                   "PFC" = "#00DB98", 
                   "STR" = "#00CBFF", 
                   "VTA" = "#BEC100")

group_conditions <- function(condition) {
  ifelse(grepl("CTX", condition), "CTX",
         ifelse(grepl("HPP", condition), "HPP",
                ifelse(grepl("PFC", condition), "PFC",
                       ifelse(grepl("STR", condition), "STR",
                              ifelse(grepl("VTA", condition), "VTA", NA)))))
}

```

To generate the heatmaps we selected for any significant DEPGs with a L2FC \> 1.50 or an L2FC \< -1.50 with a L2FC Standard Error \< 0.5 We then plot these using a wards D correlation clustering method and generate both supervised and unsupervised clusters (by group). Rows are scaled based on a correlation z-score.

```{r}

ressig1 <- as.data.frame(results_sig)

ressig1$Comparison <- "K27ac_vs_K27me3"

ressig1_highlfc_pos <- ressig1[ressig1$log2FoldChange >= 1.5, ]
ressig1_highlfc_neg <- ressig1[ressig1$log2FoldChange <= -1.5, ]

temp_sigdegshm <- rbind(ressig1_highlfc_pos, ressig1_highlfc_neg)

temp_sigdegshm20 <- temp_sigdegshm[temp_sigdegshm$lfcSE <= 0.5, ]

temp_sigdegshm21 <- temp_sigdegshm20[order(temp_sigdegshm20$log2FoldChange, decreasing = TRUE), ]

library(dplyr)
library(conflicted)
library(viridis)

ddsMat_rlog <- rlog(dds, blind = FALSE)

dup_rows <- duplicated(temp_sigdegshm21$symbol)
sum(duplicated(temp_sigdegshm21$symbol))
data_dedup <- temp_sigdegshm21[!dup_rows, ]

rows <- rownames(data_dedup)

select <- order(rowMeans(counts(dds, normalized = TRUE)),
  decreasing = TRUE
)

mat <- assay(ddsMat_rlog)[select, ]

data_mod <- mat[rownames(mat) %in% rows, ]

matrownames_data_mod <- data.frame(rownames(data_mod))

samples <- as.tibble(read.csv(paste0(basepath, "data/CATD_DESeq_Data/sample_info_combined.csv")), sep = ",")

annot_col <- samples %>%
  column_to_rownames("samplename") %>%
  as.data.frame()

custom_colors <- c("CTX" = "#FF9289", 
                   "HPP" = "#FF8AFF", 
                   "PFC" = "#00DB98", 
                   "STR" = "#00CBFF", 
                   "VTA" = "#BEC100")

ann_colors <- list(
  condition = (c(PreFrontalCortex = "#00DB98", Striatum = "#00CBFF", VTA = "#BEC100", Cortex = "#FF9289", Hippocampus = "#FF8AFF")),
  Group = (c(PreFrontalCortex = "#00DB98", Striatum = "#00CBFF", VTA = "#BEC100", Cortex = "#FF9289", Hippocampus = "#FF8AFF")),
  mark = (c(K27ac = "#FF4D00", K27me3 = "#9370DB"))
)


```

### Supervised Clustering and Condensed Heatmap

```{r Filter Heatmaps by DEGs3, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
pheatmap::pheatmap(
  mat = data_mod,
  color = colorRampPalette(rev(brewer.pal(10, "RdYlBu")))(130),
  scale = "row", 
  annotation_col = annot_col,
  annotation_colors = ann_colors,
  fontsize = 7, 
  show_colnames = F,
  cluster_rows = T,
  cluster_cols = F,
  annotation_legend = T,
  legend = T,
  show_rownames = F,
  clustering_distance_rows = "correlation",
  clustering_method = "ward.D",
  main = "Heatmap of Significant DEPGs -- Supervised and Condensed -- Combined",
  show_row_dend = FALSE,
  cutree_rows = 2,
  treeheight_row = 10,
  treeheight_col = 10,
  #filename = paste0(basepath, "output/CATD_DEPGs/Combined/BRMICCATD_Heatmap_Combined_DEPGs_Final--Supervised--Condensed--FORFIGURE.pdf"),
  legend_labels = c("PreFrontalCortex", "Striatum", "VTA", "Cortex", "Hippocampus")
)

```
# Session Info

```{r Print SessionInfo}

sessionInfo()

```