---
title: "IGV Style Plots"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: false
editor_options:
  chunk_output_type: console
---

# Using RtrackLayer to Generate IGV Style Plots for overlays of RNA Seq and CATD DataSets

First we merged bigWig files by biological replicate. As starting material we need the merged BAM files output following SAM conversion and replicate combination from alignment from both the RNA Sequencing and CUT&Tag Data. The script used below details how we obtained such files for visualization.

```{bash, eval=TRUE, engine="sh"}
#!/bin/bash

echo "Don't Run Me"

projPath="DataProcessing"
bamdir="BAMs"
bigwigdir="bigwig_withnorm"
bamCoverage="/home/avm27/anaconda3/envs/cutruntools2.1/bin/bamCoverage"
mm10blacklist="mm10-blacklist.v2.bed"
binsize=10
threads=12
effectiveGS=2652783500

echo "################################################################################
#####										######
##### 				Converting to BigWigs				######
#####			Using the Following Parameters: 			######
#####			Threads = $threads, BinSize = $binsize, 		######
#####			NormalizeUsing = RPCG,					######
#####			Effective genome size = 2652783500			######
#####										######
#######################################################################################"

echo 
echo ""

for histName in $(find ~/fastq -type f -name "*.fastq.gz" | while read F; do basename $F | rev | cut -c 28- | rev; done | sort | uniq)
do

	echo "Beginning BigWig Conversion For ${histName}"

   $bamCoverage --bam $bamdir/${histName}_merged_dupMarked_subsample.sorted.bam -o $bigwigdir/${histName}merged_dupMarked_subsample_raw_norm.bw --verbose --numberOfProcessors $threads --binSize $binsize --blackListFileName $mm10blacklist --normalizeUsing RPGC --effectiveGenomeSize $effectiveGS --ignoreForNormalization chrX --extendReads
	
	echo "Completed BigWig Conversion For ${histName}"
	
done

$bamCoverage --bam $bamdir/ALL_IgG_merged_dupMarked_subsample.sorted.bam -o $bigwigdir/ALL_IgG_merged_dupMarked_subsample_raw_norm.bw --verbose --numberOfProcessors $threads --binSize $binsize --blackListFileName $mm10blacklist --normalizeUsing RPGC --effectiveGenomeSize $effectiveGS --ignoreForNormalization chrX --extendReads

echo "################################################################################
#####										######
##### 		Now beginning to Merge BigWigs for Visualization		######
#####										######
#######################################################################################"

projPath="bigwig_withnorm"
outPath="bigwig_withnorm/merged"
outPathSort="bigwig_withnorm/merged/sorted"
outPathFinal="bigwig_withnorm/merged/final_bw"
chromSizes="/home/avm27/Desktop/CUT-RUNTools-2.0-master/assemblies/chrom.mm10"
bedgraphToBigWig="/home/avm27/UCSC/bedGraphToBigWig" ### Download UCSC Tools
bigWigMerge="/home/avm27/UCSC/bigWigMerge"


for histName in $(find ~/bigwig_withnorm -type f -name "*H3K27me3_merged_dupMarked_subsample_raw_norm.bw" | while read F; do basename $F | rev | cut -c 50- | rev; done | sort | uniq)
do 

	echo "Beginning BigWig Merge For ${histName} K27me3"
	
	$bigWigMerge $projPath/${histName}8_H3K27me3_merged_dupMarked_subsample_raw_norm.bw $projPath/${histName}9_H3K27me3_merged_dupMarked_subsample_raw_norm.bw $outPath/${histName}_H3K27me3.merged.raw.bedGraph
	
	echo "Completed BigWig Merge For ${histName} K27me3"
	
	echo "Beginning BigWig Merge For ${histName} K27ac"
	
	$bigWigMerge $projPath/${histName}8_H3K27ac_merged_dupMarked_subsample_raw_norm.bw $projPath/${histName}9_H3K27ac_merged_dupMarked_subsample_raw_norm.bw $outPath/${histName}_H3K27ac.merged.raw.bedGraph
	
	echo "Completed BigWig Merge For ${histName} K27ac"

done

for histName in $(find ~/bigwig_withnorm -type f -name "*.merged.raw.bedGraph" | while read F; do basename $F | rev | cut -c 21- | rev; done | sort | uniq)
do 

	sort -k1,1 -k2,2n ${outPath}/${histName}.merged.raw.bedGraph > ${outPathSort}/${histName}.sorted.merged.raw.bedGraph

done

for histName in $(find ~/bigwig_withnorm -type f -name "*.sorted.merged.raw.bedGraph" | while read F; do basename $F | rev | cut -c 28- | rev; done | sort | uniq)
do 

	$bedgraphToBigWig $outPathSort/${histName}.sorted.merged.raw.bedGraph $chromSizes/mm10.chrom.sizes $outPathFinal/${histName}.final.merged.bw

done


echo "################################################################################
#####										######
##### 		Now beginning to Make BigWigs for Visualization			######
#####			RNA-Sequencing Data					######
#######################################################################################"

projPath="FASTQ"
outPath="FASTQ/bigwig_new/merged"
outPathSort="FASTQ/bigwig_new/merged/sorted"
outPathFinal="FASTQ/bigwig_new/final_bw"
chromSizes="/home/avm27/Desktop/CUT-RUNTools-2.0-master/assemblies/chrom.mm10"
bedgraphToBigWig="/home/avm27/UCSC/bedGraphToBigWig"
bamCoverage="/home/avm27/anaconda3/envs/cutruntools2.1/bin/bamCoverage"
bigWigMerge="/home/avm27/UCSC/bigWigMerge"
cores=12

echo "
       Using SizeFactors Calculated by DESEQ2 (Use the inverse i.e. 1/[DESEQ2 Size Factor])

	MCTX8     MCTX9     MHPP8     MHPP9     MPFC8     MPFC9     MSTR8     MSTR9     MVTA8     MVTA9 
	0.9080702 1.1063354 1.1725299 1.0557908 0.8499803 1.2347647 0.9207111 1.1399865 0.8419090 0.9005661 

"

$bamCoverage --numberOfProcessors $cores -bs 1 --scaleFactor 1.101236446 --skipNonCoveredRegions --verbose -b $projPath/MCTX8.bam -o $projPath/bigwig_new/MCTX8_new.bw
$bamCoverage --numberOfProcessors $cores -bs 1 --scaleFactor 0.903885024 --skipNonCoveredRegions --verbose -b $projPath/MCTX9.bam -o $projPath/bigwig_new/MCTX9_new.bw
$bamCoverage --numberOfProcessors $cores -bs 1 --scaleFactor 0.852856716 --skipNonCoveredRegions --verbose -b $projPath/MHPP8.bam -o $projPath/bigwig_new/MHPP8_new.bw
$bamCoverage --numberOfProcessors $cores -bs 1 --scaleFactor 0.947157335 --skipNonCoveredRegions --verbose -b $projPath/MHPP9.bam -o $projPath/bigwig_new/MHPP9_new.bw
$bamCoverage --numberOfProcessors $cores -bs 1 --scaleFactor 1.176497855 --skipNonCoveredRegions --verbose -b $projPath/MPFC8.bam -o $projPath/bigwig_new/MPFC8_new.bw
$bamCoverage --numberOfProcessors $cores -bs 1 --scaleFactor 0.809870901 --skipNonCoveredRegions --verbose -b $projPath/MPFC9.bam -o $projPath/bigwig_new/MPFC9_new.bw
$bamCoverage --numberOfProcessors $cores -bs 1 --scaleFactor 1.086117024 --skipNonCoveredRegions --verbose -b $projPath/MSTR8.bam -o $projPath/bigwig_new/MSTR8_new.bw
$bamCoverage --numberOfProcessors $cores -bs 1 --scaleFactor 0.87720337 --skipNonCoveredRegions --verbose -b $projPath/MSTR9.bam -o $projPath/bigwig_new/MSTR9_new.bw
$bamCoverage --numberOfProcessors $cores -bs 1 --scaleFactor 1.187776826 --skipNonCoveredRegions --verbose -b $projPath/MVTA8.bam -o $projPath/bigwig_new/MVTA8_new.bw
$bamCoverage --numberOfProcessors $cores -bs 1 --scaleFactor 1.110412662 --skipNonCoveredRegions --verbose -b $projPath/MVTA9.bam -o $projPath/bigwig_new/MVTA9_new.bw




for regionName in $(find ~/FASTQ/bigwig_new -type f -name "*.bw" | while read F; do basename $F | rev | cut -c 9- | rev; done | sort | uniq)
do 

	$bigWigMerge $projPath/bigwig_new/${regionName}8_new.bw $projPath/bigwig_new/${regionName}9_new.bw $outPath/${regionName}.merged_new.bedGraph

done


for regionName in $(find ~/FASTQ/bigwig_new -type f -name "*.bw" | while read F; do basename $F | rev | cut -c 9- | rev; done | sort | uniq)
do 

	sort -k1,1 -k2,2n $outPath/${regionName}.merged_new.bedGraph > $outPathSort/${regionName}.sorted.merged_new.bedGraph

done

for regionName in $(find ~/FASTQ/bigwig_new -type f -name "*.bw" | while read F; do basename $F | rev | cut -c 9- | rev; done | sort | uniq)
do

	$bedgraphToBigWig $outPathSort/${regionName}.sorted.merged_new.bedGraph $chromSizes/mm10.chrom.sizes $outPathFinal/${regionName}.merged_new.bw

done

```


## Read in the necessary BigWig Files Generated Above

```{r eval=FALSE, include=FALSE}

# Load necessary libraries
if (!requireNamespace("GenomicRanges", quietly = TRUE)) {
  install.packages("GenomicRanges")
}
library(GenomicRanges)
if (!requireNamespace("rtracklayer", quietly = TRUE)) {
  BiocManager::install("rtracklayer")
}
library(rtracklayer)

devtools::install_github('yimingsun12138/TrackPlotR', force = TRUE)

library(ggplot2)
library(rtracklayer)
library(TrackPlotR)
library(patchwork)


bigWigs_ac = c( "/bigwig_withnorm/merged/final_bw/CTX_H3K27ac.final.merged.bw",
                "/bigwig_withnorm/merged/final_bw/HPP_H3K27ac.final.merged.bw", 
                "/bigwig_withnorm/merged/final_bw/PFC_H3K27ac.final.merged.bw",
                "/bigwig_withnorm/merged/final_bw/STR_H3K27ac.final.merged.bw",
                "/bigwig_withnorm/merged/final_bw/VTA_H3K27ac.final.merged.bw")

bigWigs_me3 = c("/bigwig_withnorm/merged/final_bw/CTX_H3K27me3.final.merged.bw",
                "/bigwig_withnorm/merged/final_bw/HPP_H3K27me3.final.merged.bw", 
                "/bigwig_withnorm/merged/final_bw/PFC_H3K27me3.final.merged.bw",
                "/bigwig_withnorm/merged/final_bw/STR_H3K27me3.final.merged.bw",
                "/bigwig_withnorm/merged/final_bw/VTA_H3K27me3.final.merged.bw")

bigWigs_IgG = c("/bigwig_withnorm/merged/final_bw/ALL_IgG.final.merged.bw")


coverage_info_RNA <- c("FASTQ/bigwig_new/final_bw/MCTX.merged_new.bw",
                        "FASTQ/bigwig_new/final_bw/MHPP.merged_new.bw", 
                        "FASTQ/bigwig_new/final_bw/MPFC.merged_new.bw",
                        "FASTQ/bigwig_new/final_bw/MSTR.merged_new.bw", 
                        "FASTQ/bigwig_new/final_bw/MVTA.merged_new.bw")

file.exists(bigWigs_ac)
file.exists(bigWigs_me3)
file.exists(bigWigs_IgG)
file.exists(coverage_info_RNA)


bigWigs_ac <- load_BigWig(file_path = bigWigs_ac, file_name = c("CTX_ac", "HPP_ac","PFC_ac","STR_ac","VTA_ac"))
bigWigs_me3 <- load_BigWig(file_path = bigWigs_me3, file_name = c("CTX_me3", "HPP_me3","PFC_me3","STR_me3","VTA_me3"))
bigWigs_IgG <- load_BigWig(file_path = bigWigs_IgG, file_name = c("IgG"))
coverage_info_RNA <- load_BigWig(file_path = coverage_info_RNA,file_name = c("CTX_rna",  "HPP_rna", "PFC_rna", "STR_rna", "VTA_rna"))

gtf_file <- "/home/avm27/Downloads/gencode.vM10.annotation.gff3"
file.exists(gtf_file)
mouse_anno <- import(gtf_file, format = "gff")

```


## Individual plots


```{r eval=FALSE, include=FALSE}
###########################################
###                                   #####
###         Plotting TNFa             #####
###                                   #####
###########################################

p1_bigWigs_ac_Tnf <- coverage_vis_gene(coverage_table = bigWigs_ac, gene_anno = mouse_anno, column_name = 'gene_name',gene = 'Tnf',y_lim = 220, up_extend = 2000,down_extend = 250,sample_order = c("CTX_ac","HPP_ac","PFC_ac", "STR_ac", "VTA_ac"),
                                   col_pal = c("#FF9289","#FF8AFF","#00DB98","#00CBFF","#BEC100"))
p1_bigWigs_me3_Tnf <- coverage_vis_gene(coverage_table = bigWigs_me3,gene_anno = mouse_anno, column_name = 'gene_name',gene = 'Tnf',y_lim = 220, up_extend = 2000, down_extend = 250,sample_order = c("CTX_me3", "HPP_me3","PFC_me3","STR_me3","VTA_me3"),
                                    col_pal = c("#FF9289","#FF8AFF","#00DB98","#00CBFF","#BEC100"))
p1_bigWigs_IgG_Tnf <- coverage_vis_gene(coverage_table = bigWigs_IgG,gene_anno = mouse_anno, column_name = 'gene_name',gene = 'Tnf',y_lim = 220, up_extend = 2000, down_extend = 250,sample_order = c("IgG"),
                                        col_pal = c("black"))
p1_coverage_info_RNA_Tnf <- coverage_vis_gene(coverage_table = coverage_info_RNA,gene_anno = mouse_anno, column_name = 'gene_name',gene = 'Tnf',up_extend = 2000,down_extend = 250, y_lim = 15000,sample_order = c("CTX_rna",  "HPP_rna", "PFC_rna", "STR_rna", "VTA_rna"),
                                      col_pal = c("#FF9289","#FF8AFF","#00DB98","#00CBFF","#BEC100"))
Tnf <- gene_track_vis(gene_anno = mouse_anno,column_name = 'gene_name',gene = 'Tnf',up_extend = 2000,down_extend = 250,show_only = FALSE)
p1_Tnf <- p1_bigWigs_ac_Tnf + theme(axis.ticks.x = element_blank(),axis.text.x = element_blank(),axis.title.x = element_blank())
p2_Tnf <- p1_bigWigs_me3_Tnf + theme(axis.ticks.x = element_blank(),axis.text.x = element_blank(),axis.title.x = element_blank(),legend.position = 'none')
p3_Tnf <- p1_bigWigs_IgG_Tnf + theme(axis.ticks.x = element_blank(),axis.text.x = element_blank(),axis.title.x = element_blank(),legend.position = 'none')
p4_Tnf <- p1_coverage_info_RNA_Tnf + theme(axis.ticks.x = element_blank(),axis.text.x = element_blank(),axis.title.x = element_blank())



TNFPlot <- print(p1_Tnf + p2_Tnf + p3_Tnf + p4_Tnf + Tnf + plot_layout(ncol = 1,heights = c(0.3,0.3,0.05,0.3,0.05)))

#pdf("CATD_IGV/IGVPlots_Tnfa.pdf", width = 8, height = 8)
TNFPlot
#dev.off()


###########################################
###                                   #####
###         Plotting Msx1             #####
###                                   #####
###########################################

p1_bigWigs_ac_Msx1 <- coverage_vis_gene(coverage_table = bigWigs_ac, 
                                          gene_anno = mouse_anno, 
                                          column_name = 'gene_name',
                                          gene = 'Msx1',
                                          y_lim = 50, 
                                          up_extend = 50,
                                          down_extend = 50,
                                          sample_order = c("CTX_ac","HPP_ac","PFC_ac", "STR_ac", "VTA_ac"),
                                          col_pal = c("#FF9289","#FF8AFF","#00DB98","#00CBFF","#BEC100"))

p1_bigWigs_me3_Msx1 <- coverage_vis_gene(coverage_table = bigWigs_me3,
                                           gene_anno = mouse_anno, 
                                           column_name = 'gene_name',
                                           gene = 'Msx1',
                                           y_lim = 50, 
                                           up_extend = 50, 
                                           down_extend = 50,
                                           sample_order = c("CTX_me3", "HPP_me3","PFC_me3","STR_me3","VTA_me3"),
                                           col_pal = c("#FF9289","#FF8AFF","#00DB98","#00CBFF","#BEC100"))

p1_bigWigs_IgG_Msx1 <- coverage_vis_gene(coverage_table = bigWigs_IgG,
                                           gene_anno = mouse_anno, 
                                           column_name = 'gene_name',
                                           gene = 'Msx1',
                                           y_lim = 50, 
                                           up_extend = 50, 
                                           down_extend = 50,
                                           sample_order = c("IgG"),
                                           col_pal = c("black"))

p1_coverage_info_RNA_Msx1 <- coverage_vis_gene(coverage_table = coverage_info_RNA,
                                                 gene_anno = mouse_anno, 
                                                 column_name = 'gene_name',
                                                 gene = 'Msx1',
                                                 up_extend = 50,
                                                 down_extend = 50, 
                                                 y_lim = 20000,
                                                 sample_order = c("CTX_rna",  "HPP_rna", "PFC_rna", "STR_rna", "VTA_rna"),
                                                 col_pal = c("#FF9289","#FF8AFF","#00DB98","#00CBFF","#BEC100"))


Msx1 <- gene_track_vis(gene_anno = mouse_anno,column_name = 'gene_name',gene = 'Msx1',up_extend = 50,down_extend = 50,show_only = FALSE)
p1_Msx1 <- p1_bigWigs_ac_Msx1 + theme(axis.ticks.x = element_blank(),axis.text.x = element_blank(),axis.title.x = element_blank(),legend.position = 'none')
p2_Msx1 <- p1_bigWigs_me3_Msx1 + theme(axis.ticks.x = element_blank(),axis.text.x = element_blank(),axis.title.x = element_blank(),legend.position = 'none')
p3_Msx1 <- p1_bigWigs_IgG_Msx1 + theme(axis.ticks.x = element_blank(),axis.text.x = element_blank(),axis.title.x = element_blank(),legend.position = 'none')
p4_Msx1 <- p1_coverage_info_RNA_Msx1 + theme(axis.ticks.x = element_blank(),axis.text.x = element_blank(),axis.title.x = element_blank())

Msx1Plot <- print(p1_Msx1 + p2_Msx1 + p3_Msx1 + p4_Msx1 + Msx1 + plot_layout(ncol = 1,heights = c(0.3,0.3,0.05,0.3,0.05)))


#pdf("CATD_IGV/IGVPlots_Msx1.pdf", width = 8, height = 8)
Msx1Plot
#dev.off()


###########################################
###                                   #####
###         Plotting Rbfox3           #####
###                                   #####
###########################################

p1_bigWigs_ac_Rbfox3 <- coverage_vis_gene(coverage_table = bigWigs_ac, 
                                           gene_anno = mouse_anno, 
                                           column_name = 'gene_name',
                                           gene = 'Rbfox3',
                                           y_lim = 100, 
                                           up_extend = 0,
                                           down_extend = 0,
                                           sample_order = c("CTX_ac","HPP_ac","PFC_ac", "STR_ac", "VTA_ac"),
                                           col_pal = c("#FF9289","#FF8AFF","#00DB98","#00CBFF","#BEC100"))

p1_bigWigs_me3_Rbfox3 <- coverage_vis_gene(coverage_table = bigWigs_me3,
                                            gene_anno = mouse_anno, 
                                            column_name = 'gene_name',
                                            gene = 'Rbfox3',
                                            y_lim = 100, 
                                            up_extend = 0, 
                                            down_extend = 0,
                                            sample_order = c("CTX_me3", "HPP_me3","PFC_me3","STR_me3","VTA_me3"),
                                            col_pal = c("#FF9289","#FF8AFF","#00DB98","#00CBFF","#BEC100"))

p1_bigWigs_IgG_Rbfox3 <- coverage_vis_gene(coverage_table = bigWigs_IgG,
                                            gene_anno = mouse_anno, 
                                            column_name = 'gene_name',
                                            gene = 'Rbfox3',
                                            y_lim = 100, 
                                            up_extend = 0, 
                                            down_extend = 0,
                                            sample_order = c("IgG"),
                                            col_pal = c("black"))

p1_coverage_info_RNA_Rbfox3 <- coverage_vis_gene(coverage_table = coverage_info_RNA,
                                                  gene_anno = mouse_anno, 
                                                  column_name = 'gene_name',
                                                  gene = 'Rbfox3',
                                                  up_extend = 0,
                                                  down_extend = 0, 
                                                  y_lim = 250,
                                                  sample_order = c("CTX_rna",  "HPP_rna", "PFC_rna", "STR_rna", "VTA_rna"),
                                                  col_pal = c("#FF9289","#FF8AFF","#00DB98","#00CBFF","#BEC100"))


Rbfox3 <- gene_track_vis(gene_anno = mouse_anno,column_name = 'gene_name',gene = 'Rbfox3',up_extend = 0,down_extend = 0,show_only = FALSE)
p1_Rbfox3 <- p1_bigWigs_ac_Rbfox3 + theme(axis.ticks.x = element_blank(),axis.text.x = element_blank(),axis.title.x = element_blank(),legend.position = 'none')
p2_Rbfox3 <- p1_bigWigs_me3_Rbfox3 + theme(axis.ticks.x = element_blank(),axis.text.x = element_blank(),axis.title.x = element_blank(),legend.position = 'none')
p3_Rbfox3 <- p1_bigWigs_IgG_Rbfox3 + theme(axis.ticks.x = element_blank(),axis.text.x = element_blank(),axis.title.x = element_blank(),legend.position = 'none')
p4_Rbfox3 <- p1_coverage_info_RNA_Rbfox3 + theme(axis.ticks.x = element_blank(),axis.text.x = element_blank(),axis.title.x = element_blank())

Rbfox3Plot <- print(p1_Rbfox3 + p2_Rbfox3 + p3_Rbfox3 + p4_Rbfox3 + Rbfox3 + plot_layout(ncol = 1,heights = c(0.3,0.3,0.05,0.3,0.1)))

#pdf("CATD_IGV/IGVPlots_Rbfox3.pdf", width = 8, height = 8)
Rbfox3Plot
#dev.off()


###########################################
###                                   #####
###         Plotting Il1a           #####
###                                   #####
###########################################

p1_bigWigs_ac_Il1a <- coverage_vis_gene(coverage_table = bigWigs_ac, 
                                          gene_anno = mouse_anno, 
                                          column_name = 'gene_name',
                                          gene = 'Il1a',
                                          y_lim = 400, 
                                          up_extend = 1000,
                                          down_extend = 1000,
                                          sample_order = c("CTX_ac","HPP_ac","PFC_ac", "STR_ac", "VTA_ac"),
                                          col_pal = c("#FF9289","#FF8AFF","#00DB98","#00CBFF","#BEC100"))

p1_bigWigs_me3_Il1a <- coverage_vis_gene(coverage_table = bigWigs_me3,
                                           gene_anno = mouse_anno, 
                                           column_name = 'gene_name',
                                           gene = 'Il1a',
                                           y_lim = 400, 
                                           up_extend = 1000, 
                                           down_extend = 1000,
                                           sample_order = c("CTX_me3", "HPP_me3","PFC_me3","STR_me3","VTA_me3"),
                                           col_pal = c("#FF9289","#FF8AFF","#00DB98","#00CBFF","#BEC100"))

p1_bigWigs_IgG_Il1a <- coverage_vis_gene(coverage_table = bigWigs_IgG,
                                           gene_anno = mouse_anno, 
                                           column_name = 'gene_name',
                                           gene = 'Il1a',
                                           y_lim = 400, 
                                           up_extend = 1000, 
                                           down_extend = 1000,
                                           sample_order = c("IgG"),
                                           col_pal = c("black"))

p1_coverage_info_RNA_Il1a <- coverage_vis_gene(coverage_table = coverage_info_RNA,
                                                 gene_anno = mouse_anno, 
                                                 column_name = 'gene_name',
                                                 gene = 'Il1a',
                                                 up_extend = 1000,
                                                 down_extend = 1000, 
                                                 y_lim = 50000,
                                                 sample_order = c("CTX_rna",  "HPP_rna", "PFC_rna", "STR_rna", "VTA_rna"),
                                                 col_pal = c("#FF9289","#FF8AFF","#00DB98","#00CBFF","#BEC100"))


Il1a <- gene_track_vis(gene_anno = mouse_anno,column_name = 'gene_name',gene = 'Il1a',up_extend = 1000,down_extend = 1000,show_only = FALSE)
p1_Il1a <- p1_bigWigs_ac_Il1a + theme(axis.ticks.x = element_blank(),axis.text.x = element_blank(),axis.title.x = element_blank(),legend.position = 'none')
p2_Il1a <- p1_bigWigs_me3_Il1a + theme(axis.ticks.x = element_blank(),axis.text.x = element_blank(),axis.title.x = element_blank(),legend.position = 'none')
p3_Il1a <- p1_bigWigs_IgG_Il1a + theme(axis.ticks.x = element_blank(),axis.text.x = element_blank(),axis.title.x = element_blank(),legend.position = 'none')
p4_Il1a <- p1_coverage_info_RNA_Il1a + theme(axis.ticks.x = element_blank(),axis.text.x = element_blank(),axis.title.x = element_blank())

Il1aPlot <- print(p1_Il1a + p2_Il1a + p3_Il1a + p4_Il1a + Il1a + plot_layout(ncol = 1,heights = c(0.3,0.3,0.05,0.3,0.1)))

#pdf("CATD_IGV/IGVPlots_Il1a.pdf", width = 8, height = 8)
Il1aPlot
#dev.off()

```

# Session Info

```{r Print Session Info, echo=TRUE, message=TRUE, warning=FALSE}
sessionInfo()
```
