---
title: "Combined H3K27me3 and H3K27ac DEPGs Analysis"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: false
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

options(connectionObserver = NULL)


library(DESeq2)
library(SummarizedExperiment)
library(AnnotationDbi)
library(org.Mm.eg.db)
library(dplyr)
library(tibble)
library(RColorBrewer)

```



# DESeq2 Analysis for H3K27me3 and H3K27ac Combined
## Loading in required files -- Comes from analysis/index3.Rmd

Building DESeq2 input files from peak count matrix generated by counting number of reads from BAM files that fell into significantly called peaks and then mapping the chromosomal locations to the respective gene.

```{r DESeq2 Build, message=FALSE, warning=FALSE, include=FALSE}

# Identify the repository root from the opened RStudio project
projdir <- normalizePath(".", winslash = "/", mustWork = TRUE)

project_file <- file.path(projdir, "RegionalMicroglialTranscriptomicsandEpigenomics.Rproj")

if (!file.exists(project_file)) {
  stop(
    paste(
      "The repository root could not be identified.",
      "Open RegionalMicroglialTranscriptomicsandEpigenomics.Rproj",
      "before running this analysis."
    )
  )
}

# Retain a trailing slash for compatibility with existing paste0() paths
basepath <- paste0(projdir, "/")

# Define Input Files
colData_file <- paste0(basepath, "data/CATD_DESeq_Data/sample_info_combined.csv")
countData_file <- paste0(basepath, "data/CATD_DESeq_Data/peak_count_matrix_CATD_Final.csv")

# Confirm Required Input Files Exist
if (!file.exists(colData_file)) {
  stop(paste("Required metadata file not found:", colData_file))
}

if (!file.exists(countData_file)) {
  stop(paste("Required count-matrix file not found:", countData_file))
}

# Read Input Files
colData <- read.csv(colData_file, sep = ",", row.names = 1)
countData <- as.matrix(read.csv(countData_file, row.names = "gene_id", sep = ","))

# Confirm Input Structure
sum(is.na(countData))
colnames(countData)
rownames(colData)
all(rownames(colData) %in% colnames(countData))

countData <- countData[, rownames(colData)]

all(rownames(colData) == colnames(countData))
```

```{r DESeq2 Analysis, echo=FALSE, message=FALSE, warning=FALSE}

dds <- DESeqDataSetFromMatrix(countData = countData, colData = colData, design = ~mark)

keep <- rowSums(counts(dds)) >= 15
dds <- dds[keep,]

dds$mark <- relevel(dds$mark, ref = "K27ac")
dds <- DESeq(dds)


```


# Plot Estimates from Results

```{r Results, echo=FALSE, results='asis'}
## Look at Results
res <- results(dds, name = "mark_K27me3_vs_K27ac")

#summary(res)

```

# Annotate Results Files

```{r Annotate Results, message=FALSE, warning=FALSE, include=FALSE, results='asis'}

res$symbol <- row.names(res)


res$description <- mapIds(x = org.Mm.eg.db,
                              keys = res$symbol,
                              column = "GENENAME",
                              keytype = "SYMBOL",
                              multiVals = "first")

    # Add ENTREZ ID
res$entrez <- mapIds(x = org.Mm.eg.db,
                      keys = res$symbol,
                     column = "ENTREZID",
                       keytype = "SYMBOL",
                       multiVals = "first")


    # Add ENSEMBL ID  
res$ensembl <- mapIds(x = org.Mm.eg.db,
                         keys = res$entrez,
                       column = "ENSEMBL",
                         keytype = "ENTREZID",
                         multiVals = "first")


```

After annotation results are subset to only view the significantly differentially expressed peaks in genes with an adjusted p-value \> 0.05.

```{r Subset Significant Results, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
## Subset for significant genes only
results_sig <- subset(res, padj < 0.05)
#summary(results_sig)

```

# Visualizing Differentially Deposited Peaks in Genes
## Heatmap

```{r Dual Heatmap, echo=FALSE, message=FALSE, warning=FALSE}


level_order <- c('Striatum', 'PreFrontalCorex', 'Hippocampus', 'VTA', 'Cortex') 

# Define custom colors for each condition
custom_colors <- c("Cortex" = "#FF9289", 
                   "Hippocampus" = "#FF8AFF", 
                   "PreFrontalCortex" = "#00DB98", 
                   "Striatum" = "#00CBFF", 
                   "VTA" = "#BEC100")

custom_colors <- c("CTX" = "#FF9289", 
                   "HPP" = "#FF8AFF", 
                   "PFC" = "#00DB98", 
                   "STR" = "#00CBFF", 
                   "VTA" = "#BEC100")

group_conditions <- function(condition) {
  ifelse(grepl("CTX", condition), "CTX",
         ifelse(grepl("HPP", condition), "HPP",
                ifelse(grepl("PFC", condition), "PFC",
                       ifelse(grepl("STR", condition), "STR",
                              ifelse(grepl("VTA", condition), "VTA", NA)))))
}

```

To generate the heatmaps we selected for any significant DEPGs with a L2FC \> 1.50 or an L2FC \< -1.50 with a L2FC Standard Error \< 0.5 We then plot these using a wards D correlation clustering method and generate both supervised and unsupervised clusters (by group). Rows are scaled based on a correlation z-score.

```{r}

ressig1 <- as.data.frame(results_sig)

ressig1$Comparison <- "K27ac_vs_K27me3"

ressig1_highlfc_pos <- ressig1[ressig1$log2FoldChange >= 1.5, ]
ressig1_highlfc_neg <- ressig1[ressig1$log2FoldChange <= -1.5, ]

temp_sigdegshm <- rbind(ressig1_highlfc_pos, ressig1_highlfc_neg)

temp_sigdegshm20 <- temp_sigdegshm[temp_sigdegshm$lfcSE <= 0.5, ]

temp_sigdegshm21 <- temp_sigdegshm20[order(temp_sigdegshm20$log2FoldChange, decreasing = TRUE), ]

ddsMat_rlog <- rlog(dds, blind = FALSE)

dup_rows <- duplicated(temp_sigdegshm21$symbol)
sum(duplicated(temp_sigdegshm21$symbol))
data_dedup <- temp_sigdegshm21[!dup_rows, ]

rows <- rownames(data_dedup)

select <- order(rowMeans(counts(dds, normalized = TRUE)),
  decreasing = TRUE
)

mat <- assay(ddsMat_rlog)[select, ]

data_mod <- mat[rownames(mat) %in% rows, ]

matrownames_data_mod <- data.frame(rownames(data_mod))

samples <- tibble::as.tibble(read.csv(paste0(basepath, "data/CATD_DESeq_Data/sample_info_combined.csv"), sep = ","))

annot_col <- samples %>%
  column_to_rownames("samplename") %>%
  as.data.frame()

custom_colors <- c("CTX" = "#FF9289", 
                   "HPP" = "#FF8AFF", 
                   "PFC" = "#00DB98", 
                   "STR" = "#00CBFF", 
                   "VTA" = "#BEC100")

ann_colors <- list(
  condition = (c(PreFrontalCortex = "#00DB98", Striatum = "#00CBFF", VTA = "#BEC100", Cortex = "#FF9289", Hippocampus = "#FF8AFF")),
  Group = (c(PreFrontalCortex = "#00DB98", Striatum = "#00CBFF", VTA = "#BEC100", Cortex = "#FF9289", Hippocampus = "#FF8AFF")),
  mark = (c(K27ac = "#FF4D00", K27me3 = "#9370DB"))
)


```

### Supervised Clustering and Condensed Heatmap

```{r Filter Heatmaps by DEGs3, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
pheatmap::pheatmap(
  mat = data_mod,
  color = colorRampPalette(rev(brewer.pal(10, "RdYlBu")))(130),
  scale = "row", 
  annotation_col = annot_col,
  annotation_colors = ann_colors,
  fontsize = 7, 
  show_colnames = F,
  cluster_rows = T,
  cluster_cols = F,
  annotation_legend = T,
  legend = T,
  show_rownames = F,
  clustering_distance_rows = "correlation",
  clustering_method = "ward.D",
  main = "Heatmap of Significant DEPGs -- Supervised and Condensed -- Combined",
  show_row_dend = FALSE,
  cutree_rows = 2,
  treeheight_row = 10,
  treeheight_col = 10,
  #filename = paste0(basepath, "output/CATD_DEPGs/Combined/BRMICCATD_Heatmap_Combined_DEPGs_Final--Supervised--Condensed--FORFIGURE.pdf"),
  legend_labels = c("PreFrontalCortex", "Striatum", "VTA", "Cortex", "Hippocampus")
)

```
# Package Versions

```{r Save Package Version Info, echo=TRUE, message=TRUE, warning=FALSE}

projdir <- "/home/avm27/Documents/Raw_Sequencing_Data/BrainRegionMicroglia/RegionalMicroglialTranscriptomicsandEpigenomics"

#Record Package Versions Used in this analysis
index6_packages <- c(
  "AnnotationDbi",
  "DESeq2",
  "dplyr",
  "knitr",
  "org.Mm.eg.db",
  "pheatmap",
  "RColorBrewer",
  "SummarizedExperiment",
  "tibble",
  "workflowr"
)

# Retrieve Each Package Version
get_package_version <- function(package_name) {

  package_path <- find.package(
    package_name,
    quiet = TRUE
  )

  package_loaded <- package_name %in% loadedNamespaces()

  if (length(package_path) == 0L) {
    return(
      data.frame(
        package = package_name,
        installed = FALSE,
        loaded = FALSE,
        version = NA_character_,
        library_path = NA_character_,
        stringsAsFactors = FALSE
      )
    )
  }

  package_path <- package_path[[1]]

  data.frame(
    package = package_name,
    installed = TRUE,
    loaded = package_loaded,
    version = as.character(
      utils::packageVersion(
        package_name,
        lib.loc = dirname(package_path)
      )
    ),
    library_path = dirname(package_path),
    stringsAsFactors = FALSE
  )
}


# Collect Package and R Environment Versions
index6_package_versions <- do.call(
  rbind,
  lapply(
    index6_packages,
    get_package_version
  )
)

index6_environment_versions <- data.frame(
  R_version = paste(
    R.version$major,
    R.version$minor,
    sep = "."
  ),
  Bioconductor_version = if (
    requireNamespace("BiocManager", quietly = TRUE)
  ) {
    as.character(BiocManager::version())
  } else {
    NA_character_
  },
  platform = R.version$platform,
  stringsAsFactors = FALSE
)


# Save Version Records

utils::write.csv(
  index6_package_versions,
  file = paste0(projdir, "/code/RPackageVersions/index6_package_versions.csv"),
  row.names = FALSE
)

utils::write.csv(
  index6_environment_versions,
  file = paste0(projdir, "/code/RPackageVersions/index6_R_and_Bioconductor_versions.csv"),
  row.names = FALSE
)

capture.output(
  sessionInfo(),
  file = paste0(projdir, "/code/RPackageVersions/index6_sessionInfo.txt")
)



# Print Results
print(index6_environment_versions, row.names = FALSE)
print(index6_package_versions, row.names = FALSE)

```

# Session Info

```{r Print Session Info, echo=TRUE, message=TRUE, warning=FALSE}
sessionInfo()
```