---
title: "Annotating Peaks For DESeq2"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: false
editor_options:
  chunk_output_type: console
---


```{r}

library(GenomicRanges)
library(IRanges)
library(S4Vectors)
library(ChIPpeakAnno)
library(ChIPseeker)
library(TxDb.Mmusculus.UCSC.mm10.knownGene)
library(chromVAR)
library(AnnotationDbi)
library(org.Mm.eg.db)
library(data.table)
library(plyr)
library(dplyr)
library(tibble)

# Identify the repository root from the opened RStudio project
projdir <- normalizePath(".", winslash = "/", mustWork = TRUE)

project_file <- file.path(projdir, "RegionalMicroglialTranscriptomicsandEpigenomics.Rproj")

if (!file.exists(project_file)) {
  stop(
    paste(
      "The repository root could not be identified.",
      "Open RegionalMicroglialTranscriptomicsandEpigenomics.Rproj",
      "before running this analysis."
    )
  )
}

```

# Please Read Below

In order to run this analysis, you must first download the corresponding peak files from https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE277753. You will need all peak bed files as well as associated BAM files placed into a folder in the data subdirectory, which you will need to create. The BAM files required to regenerate the peak-count matrices are not included in this repository because of their size. The upstream processing chunks are retained with eval = FALSE to document how the matrices were generated. To reproduce those steps, download the corresponding peak files from GEO and to regenerate the BAM files from FASTQ and then place them in the directories specified below. Otherwise, begin at “Skip to here if loading data” using the provided RData file or use the supplied peak-count matrices in the downstream analyses.

```{r Extract Significant Peaks, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

projPath <- file.path(projdir, "data", "CATD_Peaks")
mPeak <- GenomicRanges::GRanges()

histL <- c("PFC8-H3K27ac", "PFC9-H3K27ac", "STR8-H3K27ac", "STR9-H3K27ac", "HPP8-H3K27ac", "HPP9-H3K27ac", "VTA8-H3K27ac", "VTA9-H3K27ac", "CTX8-H3K27ac", "CTX9-H3K27ac", "PFC8-H3K27me3", "PFC9-H3K27me3", "STR8-H3K27me3", "STR9-H3K27me3", "HPP8-H3K27me3", "HPP9-H3K27me3", "VTA8-H3K27me3", "VTA9-H3K27me3", "CTX8-H3K27me3", "CTX9-H3K27me3")

for (hist in histL) {
  peak_file <- file.path(projPath, paste0(hist, "_dupMarked_merge_normalized_spikein_seacr_control.peaks.stringent.bed"))
  peakRes <- read.table(peak_file, header = FALSE, fill = TRUE)
  mPeak <- GenomicRanges::GRanges(seqnames = peakRes$V1, IRanges::IRanges(start = peakRes$V2, end = peakRes$V3), strand = "*") %>% append(mPeak, .)
}

masterPeak <- GenomicRanges::reduce(mPeak)

masterPeak

```

```{r Annotate Peaks, eval=FALSE, include=FALSE}

annoData <- toGRanges(TxDb.Mmusculus.UCSC.mm10.knownGene, feature="gene")

annot <- annotatePeakInBatch(masterPeak, 
                             AnnotationData=annoData,
                             output="overlapping",
                             PeakLocForDistance = "start",
                             select = "first")

peak.anno = annotatePeak(peak = annot,
                         tssRegion = c(-5000, 5000),
                         TxDb = TxDb.Mmusculus.UCSC.mm10.knownGene,
                         annoDb = "org.Mm.eg.db",
                         level = "gene",
                         overlap = "TSS")


dfPA = as.data.frame(peak.anno)

masterPeak.anno <- makeGRangesFromDataFrame(dfPA,
                                            keep.extra.columns=TRUE,
                                            ignore.strand=FALSE,
                                            seqinfo=NULL,
                                            seqnames.field=c("seqnames", "seqname",
                                                             "chromosome", "chrom",
                                                             "chr", "chromosome_name",
                                                             "seqid"),
                                            start.field="start",
                                            end.field=c("end", "stop"),
                                            strand.field="strand",
                                            starts.in.df.are.0based=FALSE)

plotAnnoPie(peak.anno)

```



```{r Extract Fragments in Peaks, eval=FALSE, include=FALSE}

bamDir="/home/avm27/Documents/Raw_Sequencing_Data/BR_Mic_CATD/HenikoffDataProcessing/alignment/bam"
bamFile= paste0(bamDir, "/", "PFC8-H3K27ac_merged_dupMarked_subsample.sorted.bam")
bamFile2= paste0(bamDir, "/", "PFC9-H3K27ac_merged_dupMarked_subsample.sorted.bam")
bamFile3= paste0(bamDir, "/", "STR8-H3K27ac_merged_dupMarked_subsample.sorted.bam")
bamFile4= paste0(bamDir, "/", "STR9-H3K27ac_merged_dupMarked_subsample.sorted.bam")
bamFile5= paste0(bamDir, "/", "HPP8-H3K27ac_merged_dupMarked_subsample.sorted.bam")
bamFile6= paste0(bamDir, "/", "HPP9-H3K27ac_merged_dupMarked_subsample.sorted.bam")
bamFile7= paste0(bamDir, "/", "VTA8-H3K27ac_merged_dupMarked_subsample.sorted.bam")
bamFile8= paste0(bamDir, "/", "VTA9-H3K27ac_merged_dupMarked_subsample.sorted.bam")
bamFile9= paste0(bamDir, "/", "CTX8-H3K27ac_merged_dupMarked_subsample.sorted.bam")
bamFile10= paste0(bamDir, "/", "CTX9-H3K27ac_merged_dupMarked_subsample.sorted.bam")
bamFile11= paste0(bamDir, "/", "PFC8-H3K27me3_merged_dupMarked_subsample.sorted.bam")
bamFile12= paste0(bamDir, "/", "PFC9-H3K27me3_merged_dupMarked_subsample.sorted.bam")
bamFile13= paste0(bamDir, "/", "STR8-H3K27me3_merged_dupMarked_subsample.sorted.bam")
bamFile14= paste0(bamDir, "/", "STR9-H3K27me3_merged_dupMarked_subsample.sorted.bam")
bamFile15= paste0(bamDir, "/", "HPP8-H3K27me3_merged_dupMarked_subsample.sorted.bam")
bamFile16= paste0(bamDir, "/", "HPP9-H3K27me3_merged_dupMarked_subsample.sorted.bam")
bamFile17= paste0(bamDir, "/", "VTA8-H3K27me3_merged_dupMarked_subsample.sorted.bam")
bamFile18= paste0(bamDir, "/", "VTA9-H3K27me3_merged_dupMarked_subsample.sorted.bam")
bamFile19= paste0(bamDir, "/", "CTX8-H3K27me3_merged_dupMarked_subsample.sorted.bam")
bamFile20= paste0(bamDir, "/", "CTX9-H3K27me3_merged_dupMarked_subsample.sorted.bam")


fragment_counts <- chromVAR::getCounts(c(bamFile, bamFile2, bamFile3, bamFile4, 
                                         bamFile5, bamFile6, bamFile7, bamFile8, 
                                         bamFile9, bamFile10, bamFile11, bamFile12, 
                                         bamFile13, bamFile14, bamFile15, bamFile16, 
                                         bamFile17, bamFile18, bamFile19, bamFile20), 
                                         masterPeak.anno, 
                                         paired = TRUE, by_rg = FALSE, format = "bam")


countMat = counts(fragment_counts)
head(countMat)

```

# Skip to here if loading data

```{r Load in Necessary R Data, eval=FALSE, include=FALSE}

rdata_file <- file.path(projdir, "data", "CATD_DESeq_Data", "GeneratingPeaksinFragments.RData")

# Save the generated objects when rebuilding the count matrices
#save(countMat, fragment_counts, file = rdata_file)

# Load the previously generated objects when skipping the upstream processing
load(rdata_file)

```


```{r Convert Fragments to Data Frame, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}

#' Convert a GenomicRanges into a data.table.
#'
#' @param GR A Granges object
#' @return A data.table object.
grToDt = function(GR) {
  DF=as.data.frame(elementMetadata(GR))
  if( ncol(DF) > 0) {
    DT = data.table(chr=as.vector(seqnames(GR)), 
                    start=start(GR), end=end(GR), DF)
  } else {
    DT = data.table(chr=as.vector(seqnames(GR)), 
                    start=start(GR), end=end(GR))
  }
  return(DT)
}


frag_counts_ft <- grToDt(fragment_counts)
dup_rows <- duplicated(frag_counts_ft$peak)
frag_counts_ft <- frag_counts_ft[!dup_rows, ]

```

```{r Assign Names and Peak Names to Gene Locations, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=TRUE}

rownames(countMat) = fragment_counts@rowRanges@elementMetadata@listData[["peak"]]

colnames(countMat) = paste(c("PFC8-H3K27ac","PFC9-H3K27ac",
                             "STR8-H3K27ac","STR9-H3K27ac", 
                             "HPP8-H3K27ac","HPP9-H3K27ac",
                             "VTA8-H3K27ac","VTA9-H3K27ac", 
                             "CTX8-H3K27ac", "CTX9-H3K27ac",
                             "PFC8-H3K27me3", "PFC9-H3K27me3",
                             "STR8-H3K27me3", "STR9-H3K27me3", 
                             "HPP8-H3K27me3", "HPP9-H3K27me3",
                             "VTA8-H3K27me3", "VTA9-H3K27me3",
                             "CTX8-H3K27me3", "CTX9-H3K27me3"))

countMatrownames <- data.frame(row.names(countMat))
countMatrownames$peak <- countMatrownames$row.names.countMat.
all(countMatrownames$peak == countMatrownames$row.names.countMat.)
newrownames <- merge(countMatrownames,frag_counts_ft,by="peak")
newrownames <- newrownames %>% dplyr::select(1,14,20,22:24)

dup_rows <- duplicated(newrownames$peak)
newrownames <- newrownames[!dup_rows, ]

countMat_df <- as.data.frame(as.matrix(countMat), rownames = FALSE)
countMat2 <- cbind(countMat_df, newrownames)

countMat_Anno <- countMat2
countMat_Anno_singleGenes <- countMat_Anno[,c(1:20,23,24,25)]

countMat_Anno_singleGenes_final <- plyr::ddply(countMat_Anno_singleGenes, "geneId", numcolwise(sum))

countMat_Anno_singleGenes_final$SYMBOL <- mapIds(x = org.Mm.eg.db,
                     keys = countMat_Anno_singleGenes_final$geneId,
                     column = "SYMBOL",
                     keytype = "ENTREZID",
                     multiVals = "first")

countMat_Anno_singleGenes_final2 <- countMat_Anno_singleGenes_final[complete.cases(countMat_Anno_singleGenes_final), ]
countMat_Anno_singleGenes_final_NOMATCH <- countMat_Anno_singleGenes_final[!complete.cases(countMat_Anno_singleGenes_final), ]

rownames(countMat_Anno_singleGenes_final2) <- countMat_Anno_singleGenes_final2$SYMBOL

countMat_Anno_singleGenes_final_ac <- countMat_Anno_singleGenes_final2[,c(2:11)]
countMat_Anno_singleGenes_final_me3 <- countMat_Anno_singleGenes_final2[,c(12:21)]
countMat_Anno_singleGenes_final_all <- countMat_Anno_singleGenes_final2[,c(2:21)]

dfac <- countMat_Anno_singleGenes_final_ac %>%
  rename_with(~ sub("-H3K27ac$", "", .x)) %>%
  dplyr::arrange(rownames(countMat_Anno_singleGenes_final_ac))


dfme3 <- countMat_Anno_singleGenes_final_me3 %>%
  rename_with(~ sub("-H3K27me3$", "", .x)) %>%
  dplyr::arrange(rownames(countMat_Anno_singleGenes_final_me3))

dfall <- countMat_Anno_singleGenes_final_all %>%
  dplyr::arrange(rownames(countMat_Anno_singleGenes_final_all))

colnames(dfall) <- sub("-", ".", colnames(dfall))

dfme3 <- dfme3 %>% 
  mutate(across(everything(), as.integer))
dfac <- dfac %>% 
  mutate(across(everything(), as.integer))
dfall <- dfall %>% 
  mutate(across(everything(), as.integer)) 

dfac_final_countmat <- dfac %>%
  rownames_to_column(var="gene_id")

dfme3_final_countmat <- dfme3 %>%
  rownames_to_column(var="gene_id")

dfall_final_countmat <- dfall %>%
  rownames_to_column(var="gene_id")

head(dfme3_final_countmat)
head(dfac_final_countmat)
head(dfall_final_countmat)

```

```{r Write Results for Use with DESeq2, eval=FALSE, include=FALSE}

#write.csv(dfac_final_countmat, "data/CATD_DESeq_Data/peak_count_matrix_CATD_Final_K27ac.csv", row.names = FALSE)
#write.csv(dfme3_final_countmat, "data/CATD_DESeq_Data/peak_count_matrix_CATD_Final_K27me3.csv", row.names = FALSE)
#write.csv(dfall_final_countmat, "data/CATD_DESeq_Data/peak_count_matrix_CATD_Final.csv", row.names = FALSE)

```

# Plot Combined PCA

```{r}

sample_names = c("PFC8.H3K27ac","PFC9.H3K27ac",
                 "STR8.H3K27ac","STR9.H3K27ac",
                 "HPP8.H3K27ac","HPP9.H3K27ac",
                 "VTA8.H3K27ac","VTA9.H3K27ac",
                 "CTX8.H3K27ac","CTX9.H3K27ac",
                 "PFC8.H3K27me3","PFC9.H3K27me3",
                 "STR8.H3K27me3","STR9.H3K27me3",
                 "HPP8.H3K27me3","HPP9.H3K27me3",
                 "VTA8.H3K27me3","VTA9.H3K27me3",
                 "CTX8.H3K27me3","CTX9.H3K27me3")

colnames(countMat) = sample_names

# Load Sample Information

colData <- read.csv(paste0(basepath,"data/CATD_DESeq_Data/sample_info_combined.csv"),
                    sep = ",", row.names = 1)

# Match Count Matrix and Sample Information

all(rownames(colData) %in% colnames(countMat))

peak_counts <- countMat[,rownames(colData)]

all(rownames(colData) == colnames(peak_counts))

# Remove Empty Peaks

keep_peak <- rowSums(peak_counts) > 0

peak_counts <- peak_counts[keep_peak,]

# Create DESeq2 Object and Normalize Counts

dds_peak <- DESeq2::DESeqDataSetFromMatrix(countData = peak_counts,
                                           colData = colData,
                                           design = ~mark)

dds_peak <- DESeq2::estimateSizeFactors(dds_peak)

peak_raw <- as.matrix(DESeq2::counts(dds_peak, normalized = FALSE))

peak_normalized <- as.matrix(DESeq2::counts(dds_peak, normalized = TRUE))

# Calculate Peak Variance

peak_variance <- matrixStats::rowVars(peak_raw)

keep_variance <- is.finite(peak_variance) & peak_variance > 0

peak_variance <- peak_variance[keep_variance]

peak_normalized_use <- peak_normalized[keep_variance,]

# Select Top 100 Variable Peaks

ntop = 100

top_idx <- order(peak_variance, decreasing = TRUE)[1:ntop]

top_peak_names <- rownames(peak_normalized_use)[top_idx]

pca_matrix <- peak_normalized_use[top_idx,]

# Run PCA

pca <- stats::prcomp(t(pca_matrix),
                     center = TRUE,
                     scale. = FALSE)

percent_var <- 100 * (pca$sdev^2 / sum(pca$sdev^2))

pca_data <- data.frame(sample = rownames(pca$x),
                       PC1 = pca$x[,"PC1"],
                       PC2 = pca$x[,"PC2"])

pca_data$condition <- colData[pca_data$sample,"condition"]

pca_data$mark <- colData[pca_data$sample,"mark"]

custom_colors <- c("CTX" = "#FF9289",
                   "HPP" = "#FF8AFF",
                   "PFC" = "#00DB98",
                   "STR" = "#00CBFF",
                   "VTA" = "#BEC100")

ann_colors <- list(
  condition = c(PreFrontalCortex = "#00DB98",
                Striatum = "#00CBFF",
                VTA = "#BEC100",
                Cortex = "#FF9289",
                Hippocampus = "#FF8AFF"),

  Group = c(PreFrontalCortex = "#00DB98",
            Striatum = "#00CBFF",
            VTA = "#BEC100",
            Cortex = "#FF9289",
            Hippocampus = "#FF8AFF"),

  mark = c(K27ac = "#FF4D00",
           K27me3 = "#9370DB")
)


# Plot PCA

pca_plot <- ggplot2::ggplot(pca_data,
                            ggplot2::aes(x = PC1,
                                         y = PC2,
                                         color = condition,
                                         shape = mark)) +
  ggplot2::geom_point(size = 3) +
  ggrepel::geom_label_repel(ggplot2::aes(label = sample),
                            fill = "white",
                            size = 3,
                            show.legend = FALSE,
                            max.overlaps = Inf) +
  ggplot2::scale_color_manual(values = ann_colors$condition) +
  ggplot2::scale_shape_manual(values = c(K27ac = 16,
                                         K27me3 = 17)) +
  ggplot2::labs(x = paste0("PC1: ", round(percent_var[1], 1), "% variance"),
                y = paste0("PC2: ", round(percent_var[2], 1), "% variance"),
                title = "Principal Components Analysis (PCA)",
                color = "Condition",
                shape = "Histone Mark") +
  ggplot2::theme_bw(base_size = 12)


# Print Results

print(pca_plot)

## Save Results

#pdf(paste0(basepath, "output/CATD_DEPGs/Combined/BRMic_PCA_CATDCombined_DEPGs_Final.pdf"), width = 8, height = 8)

#pca_plot

#dev.off()


```

# Package Versions

```{r Save Package Version Info, echo=TRUE, message=TRUE, warning=FALSE}

projdir <- "/home/avm27/Documents/Raw_Sequencing_Data/BrainRegionMicroglia/RegionalMicroglialTranscriptomicsandEpigenomics"

#Record Package Versions Used in this analysis
index3_packages <- sort(
  unique(
    c(
      "AnnotationDbi",
      "ChIPpeakAnno",
      "ChIPseeker",
      "chromVAR",
      "data.table",
      "dplyr",
      "GenomicRanges",
      "IRanges",
      "org.Mm.eg.db",
      "plyr",
      "S4Vectors",
      "tibble",
      "TxDb.Mmusculus.UCSC.mm10.knownGene",
      "workflowr"
    )
  )
)

# Retrieve Each Package Version
get_package_version <- function(package_name) {

  package_path <- find.package(
    package_name,
    quiet = TRUE
  )

  package_loaded <- package_name %in% loadedNamespaces()

  if (length(package_path) == 0L) {
    return(
      data.frame(
        package = package_name,
        installed = FALSE,
        loaded = FALSE,
        version = NA_character_,
        library_path = NA_character_,
        stringsAsFactors = FALSE
      )
    )
  }

  package_path <- package_path[[1]]

  data.frame(
    package = package_name,
    installed = TRUE,
    loaded = package_loaded,
    version = as.character(
      utils::packageVersion(
        package_name,
        lib.loc = dirname(package_path)
      )
    ),
    library_path = dirname(package_path),
    stringsAsFactors = FALSE
  )
}


# Collect Package and R Environment Versions
index3_package_versions <- do.call(
  rbind,
  lapply(
    index3_packages,
    get_package_version
  )
)

index3_environment_versions <- data.frame(
  R_version = paste(
    R.version$major,
    R.version$minor,
    sep = "."
  ),
  Bioconductor_version = if (
    requireNamespace("BiocManager", quietly = TRUE)
  ) {
    as.character(BiocManager::version())
  } else {
    NA_character_
  },
  platform = R.version$platform,
  stringsAsFactors = FALSE
)


# Save Version Records

utils::write.csv(
  index3_package_versions,
  file = paste0(projdir, "/code/RPackageVersions/index3_package_versions.csv"),
  row.names = FALSE
)

utils::write.csv(
  index3_environment_versions,
  file = paste0(projdir, "/code/RPackageVersions/index3_R_and_Bioconductor_versions.csv"),
  row.names = FALSE
)

capture.output(
  sessionInfo(),
  file = paste0(projdir, "/code/RPackageVersions/index3_sessionInfo.txt")
)



# Print Results
print(index3_environment_versions, row.names = FALSE)
print(index3_package_versions, row.names = FALSE)

```

# Session Info

```{r Print Session Info, echo=TRUE, message=TRUE, warning=FALSE}
sessionInfo()
```