---
title: "IGV Style Plots"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: false
editor_options:
  chunk_output_type: console
---

# Using RtrackLayer to Generate IGV Style Plots for overlays of RNA Seq and CATD DataSets

First we merged bigWig files by biological replicate. As starting material we need the merged BAM files output following SAM conversion and replicate combination from alignment from both the RNA Sequencing and CUT&Tag Data. The script used below details how we obtained such files for visualization.

```{bash, eval=FALSE, engine="sh"}
#!/bin/bash

# This optional preprocessing workflow requires external BAM and reference files.
# Set BRMIC_EXTERNAL_DATA to the directory containing those files before running it manually.

: "${BRMIC_EXTERNAL_DATA:?Set BRMIC_EXTERNAL_DATA before running this optional preprocessing workflow}"

externalDataDir="${BRMIC_EXTERNAL_DATA}"
fastqdir="${externalDataDir}/fastq"
bamdir="${externalDataDir}/BAMs"
bigwigdir="${externalDataDir}/bigwig_withnorm"
referenceDir="${externalDataDir}/reference"

mm10blacklist="${referenceDir}/mm10-blacklist.v2.bed"
chromSizes="${referenceDir}/mm10.chrom.sizes"

bamCoverage="$(command -v bamCoverage)"
bedgraphToBigWig="$(command -v bedGraphToBigWig)"
bigWigMerge="$(command -v bigWigMerge)"

binsize=10
threads=12
effectiveGS=2652783500

if [ -z "${bamCoverage}" ] || [ -z "${bedgraphToBigWig}" ] || [ -z "${bigWigMerge}" ]; then
  echo "Required programs were not found: bamCoverage, bedGraphToBigWig, and/or bigWigMerge"
  exit 1
fi

# Confirm Required Inputs Exist
if [ ! -d "${fastqdir}" ]; then
  echo "FASTQ directory not found: ${fastqdir}"
  exit 1
fi

if [ ! -d "${bamdir}" ]; then
  echo "BAM directory not found: ${bamdir}"
  exit 1
fi

if [ ! -f "${mm10blacklist}" ]; then
  echo "Mouse blacklist file not found: ${mm10blacklist}"
  exit 1
fi

if [ ! -f "${chromSizes}" ]; then
  echo "Mouse chromosome-size file not found: ${chromSizes}"
  exit 1
fi

# Create the initial BigWig output directory before writing files
mkdir -p "${bigwigdir}"

echo "################################################################################
#####										######
##### 				Converting to BigWigs				######
#####			Using the Following Parameters: 			######
#####			Threads = $threads, BinSize = $binsize, 		######
#####			NormalizeUsing = RPGC,					######
#####			Effective genome size = 2652783500			######
#####										######
#######################################################################################"

echo 
echo ""

for histName in $(find "${fastqdir}" -type f -name "*.fastq.gz" | while read F; do basename $F | rev | cut -c 28- | rev; done | sort | uniq)
do

	echo "Beginning BigWig Conversion For ${histName}"

   $bamCoverage --bam $bamdir/${histName}_merged_dupMarked_subsample.sorted.bam -o $bigwigdir/${histName}merged_dupMarked_subsample_raw_norm.bw --verbose --numberOfProcessors $threads --binSize $binsize --blackListFileName $mm10blacklist --normalizeUsing RPGC --effectiveGenomeSize $effectiveGS --ignoreForNormalization chrX --extendReads
	
	echo "Completed BigWig Conversion For ${histName}"
	
done

$bamCoverage --bam $bamdir/ALL_IgG_merged_dupMarked_subsample.sorted.bam -o $bigwigdir/ALL_IgG_merged_dupMarked_subsample_raw_norm.bw --verbose --numberOfProcessors $threads --binSize $binsize --blackListFileName $mm10blacklist --normalizeUsing RPGC --effectiveGenomeSize $effectiveGS --ignoreForNormalization chrX --extendReads

echo "################################################################################
#####										######
##### 		Now beginning to Merge BigWigs for Visualization		######
#####										######
#######################################################################################"

projPath="${bigwigdir}"
outPath="${bigwigdir}/merged"
outPathSort="${outPath}/sorted"
outPathFinal="${outPath}/final_bw"

mkdir -p "${bigwigdir}" "${outPath}" "${outPathSort}" "${outPathFinal}"


for histName in $(find "${bigwigdir}" -type f -name "*H3K27me3_merged_dupMarked_subsample_raw_norm.bw" | while read F; do basename $F | rev | cut -c 50- | rev; done | sort | uniq)
do 

	echo "Beginning BigWig Merge For ${histName} K27me3"
	
	$bigWigMerge $projPath/${histName}8_H3K27me3_merged_dupMarked_subsample_raw_norm.bw $projPath/${histName}9_H3K27me3_merged_dupMarked_subsample_raw_norm.bw $outPath/${histName}_H3K27me3.merged.raw.bedGraph
	
	echo "Completed BigWig Merge For ${histName} K27me3"
	
	echo "Beginning BigWig Merge For ${histName} K27ac"
	
	$bigWigMerge $projPath/${histName}8_H3K27ac_merged_dupMarked_subsample_raw_norm.bw $projPath/${histName}9_H3K27ac_merged_dupMarked_subsample_raw_norm.bw $outPath/${histName}_H3K27ac.merged.raw.bedGraph
	
	echo "Completed BigWig Merge For ${histName} K27ac"

done

for histName in $(find "${outPath}" -type f -name "*.merged.raw.bedGraph" | while read F; do basename $F | rev | cut -c 21- | rev; done | sort | uniq)
do 

	sort -k1,1 -k2,2n ${outPath}/${histName}.merged.raw.bedGraph > ${outPathSort}/${histName}.sorted.merged.raw.bedGraph

done

for histName in $(find "${outPathSort}" -type f -name "*.sorted.merged.raw.bedGraph" | while read F; do basename $F | rev | cut -c 28- | rev; done | sort | uniq)
do 

	$bedgraphToBigWig $outPathSort/${histName}.sorted.merged.raw.bedGraph "${chromSizes}" $outPathFinal/${histName}.final.merged.bw

done


echo "################################################################################
#####										######
##### 		Now beginning to Make BigWigs for Visualization			######
#####			RNA-Sequencing Data					######
#######################################################################################"

projPath="${externalDataDir}/FASTQ"
rnaBigWigDir="${projPath}/bigwig_new"
outPath="${rnaBigWigDir}/merged"
outPathSort="${outPath}/sorted"
outPathFinal="${rnaBigWigDir}/final_bw"
cores=12

mkdir -p "${rnaBigWigDir}" "${outPath}" "${outPathSort}" "${outPathFinal}"

echo "
       Using SizeFactors Calculated by DESEQ2 (Use the inverse i.e. 1/[DESEQ2 Size Factor])

	MCTX8     MCTX9     MHPP8     MHPP9     MPFC8     MPFC9     MSTR8     MSTR9     MVTA8     MVTA9 
	0.9080702 1.1063354 1.1725299 1.0557908 0.8499803 1.2347647 0.9207111 1.1399865 0.8419090 0.9005661 

"

$bamCoverage --numberOfProcessors $cores -bs 1 --scaleFactor 1.101236446 --skipNonCoveredRegions --verbose -b $projPath/MCTX8.bam -o $projPath/bigwig_new/MCTX8_new.bw
$bamCoverage --numberOfProcessors $cores -bs 1 --scaleFactor 0.903885024 --skipNonCoveredRegions --verbose -b $projPath/MCTX9.bam -o $projPath/bigwig_new/MCTX9_new.bw
$bamCoverage --numberOfProcessors $cores -bs 1 --scaleFactor 0.852856716 --skipNonCoveredRegions --verbose -b $projPath/MHPP8.bam -o $projPath/bigwig_new/MHPP8_new.bw
$bamCoverage --numberOfProcessors $cores -bs 1 --scaleFactor 0.947157335 --skipNonCoveredRegions --verbose -b $projPath/MHPP9.bam -o $projPath/bigwig_new/MHPP9_new.bw
$bamCoverage --numberOfProcessors $cores -bs 1 --scaleFactor 1.176497855 --skipNonCoveredRegions --verbose -b $projPath/MPFC8.bam -o $projPath/bigwig_new/MPFC8_new.bw
$bamCoverage --numberOfProcessors $cores -bs 1 --scaleFactor 0.809870901 --skipNonCoveredRegions --verbose -b $projPath/MPFC9.bam -o $projPath/bigwig_new/MPFC9_new.bw
$bamCoverage --numberOfProcessors $cores -bs 1 --scaleFactor 1.086117024 --skipNonCoveredRegions --verbose -b $projPath/MSTR8.bam -o $projPath/bigwig_new/MSTR8_new.bw
$bamCoverage --numberOfProcessors $cores -bs 1 --scaleFactor 0.87720337 --skipNonCoveredRegions --verbose -b $projPath/MSTR9.bam -o $projPath/bigwig_new/MSTR9_new.bw
$bamCoverage --numberOfProcessors $cores -bs 1 --scaleFactor 1.187776826 --skipNonCoveredRegions --verbose -b $projPath/MVTA8.bam -o $projPath/bigwig_new/MVTA8_new.bw
$bamCoverage --numberOfProcessors $cores -bs 1 --scaleFactor 1.110412662 --skipNonCoveredRegions --verbose -b $projPath/MVTA9.bam -o $projPath/bigwig_new/MVTA9_new.bw




for regionName in $(find "${rnaBigWigDir}" -type f -name "M*8_new.bw" | while read F; do basename $F | rev | cut -c 9- | rev; done | sort | uniq)
do 

	$bigWigMerge $projPath/bigwig_new/${regionName}8_new.bw $projPath/bigwig_new/${regionName}9_new.bw $outPath/${regionName}.merged_new.bedGraph

done


for regionName in $(find "${rnaBigWigDir}" -type f -name "M*8_new.bw" | while read F; do basename $F | rev | cut -c 9- | rev; done | sort | uniq)
do 

	sort -k1,1 -k2,2n $outPath/${regionName}.merged_new.bedGraph > $outPathSort/${regionName}.sorted.merged_new.bedGraph

done

for regionName in $(find "${rnaBigWigDir}" -type f -name "M*8_new.bw" | while read F; do basename $F | rev | cut -c 9- | rev; done | sort | uniq)
do

	$bedgraphToBigWig $outPathSort/${regionName}.sorted.merged_new.bedGraph "${chromSizes}" $outPathFinal/${regionName}.merged_new.bw

done

```

## Read in the necessary BigWig Files Generated Above

```{r Read BigWig Files, eval=FALSE, include=FALSE}

# Load Required Packages
library(ggplot2)
library(patchwork)
library(rtracklayer)
library(TrackPlotR)

# Locate Externally Stored Sequencing Files
externalDataDir <- Sys.getenv("BRMIC_EXTERNAL_DATA")

if (!nzchar(externalDataDir)) {
  stop(
    paste(
      "The BRMIC_EXTERNAL_DATA environment variable is not set.",
      "Set it to the directory containing the generated BigWig",
      "and reference files before running this optional analysis."
    )
  )
}

externalDataDir <- normalizePath(externalDataDir, winslash = "/", mustWork = TRUE)

# Define External Data Directories
catdBigWigDir <- file.path(externalDataDir, "bigwig_withnorm", "merged", "final_bw")
rnaBigWigDir <- file.path(externalDataDir, "FASTQ", "bigwig_new", "final_bw")
referenceDir <- file.path(externalDataDir, "reference")

# Define H3K27ac BigWig Files
bigWigs_ac <- file.path(catdBigWigDir, c("CTX_H3K27ac.final.merged.bw", "HPP_H3K27ac.final.merged.bw", "PFC_H3K27ac.final.merged.bw", "STR_H3K27ac.final.merged.bw", "VTA_H3K27ac.final.merged.bw"))

# Define H3K27me3 BigWig Files
bigWigs_me3 <- file.path(catdBigWigDir, c("CTX_H3K27me3.final.merged.bw", "HPP_H3K27me3.final.merged.bw", "PFC_H3K27me3.final.merged.bw", "STR_H3K27me3.final.merged.bw", "VTA_H3K27me3.final.merged.bw"))

# Define IgG BigWig File
bigWigs_IgG <- file.path(externalDataDir, "bigwig_withnorm", "ALL_IgG_merged_dupMarked_subsample_raw_norm.bw")

# Define RNA-seq BigWig Files
coverage_info_RNA <- file.path(rnaBigWigDir, c("MCTX.merged_new.bw", "MHPP.merged_new.bw", "MPFC.merged_new.bw", "MSTR.merged_new.bw", "MVTA.merged_new.bw"))

# Define Genome Annotation File
gtf_file <- file.path(referenceDir, "gencode.vM10.annotation.gff3")

# Confirm Required Files Exist
required_files <- c(bigWigs_ac, bigWigs_me3, bigWigs_IgG, coverage_info_RNA, gtf_file)
missing_files <- required_files[!file.exists(required_files)]

if (length(missing_files) > 0L) {
  stop(
    paste(
      "The following required external files were not found:",
      paste(missing_files, collapse = "\n")
    )
  )
}

# Load BigWig Files
bigWigs_ac <- TrackPlotR::load_BigWig(file_path = bigWigs_ac, file_name = c("CTX_ac", "HPP_ac", "PFC_ac", "STR_ac", "VTA_ac"))
bigWigs_me3 <- TrackPlotR::load_BigWig(file_path = bigWigs_me3, file_name = c("CTX_me3", "HPP_me3", "PFC_me3", "STR_me3", "VTA_me3"))
bigWigs_IgG <- TrackPlotR::load_BigWig(file_path = bigWigs_IgG, file_name = "IgG")
coverage_info_RNA <- TrackPlotR::load_BigWig(file_path = coverage_info_RNA, file_name = c("CTX_rna", "HPP_rna", "PFC_rna", "STR_rna", "VTA_rna"))

# Load Genome Annotation
mouse_anno <- rtracklayer::import(gtf_file, format = "gff3")

```


## Individual plots


```{r eval=FALSE, include=FALSE}

# Identify the repository root from the opened RStudio project
projdir <- normalizePath(".", winslash = "/", mustWork = TRUE)

project_file <- file.path(projdir, "RegionalMicroglialTranscriptomicsandEpigenomics.Rproj")

if (!file.exists(project_file)) {
  stop(
    paste(
      "The repository root could not be identified.",
      "Open RegionalMicroglialTranscriptomicsandEpigenomics.Rproj",
      "before running this analysis."
    )
  )
}

# Define the optional plot output directory
plotOutputDir <- file.path(projdir, "CATD_IGV")
dir.create(plotOutputDir, recursive = TRUE, showWarnings = FALSE)


###########################################
###                                   #####
###         Plotting TNFa             #####
###                                   #####
###########################################

p1_bigWigs_ac_Tnf <- coverage_vis_gene(coverage_table = bigWigs_ac, gene_anno = mouse_anno, column_name = 'gene_name',gene = 'Tnf',y_lim = 220, up_extend = 2000,down_extend = 250,sample_order = c("CTX_ac","HPP_ac","PFC_ac", "STR_ac", "VTA_ac"),
                                   col_pal = c("#FF9289","#FF8AFF","#00DB98","#00CBFF","#BEC100"))
p1_bigWigs_me3_Tnf <- coverage_vis_gene(coverage_table = bigWigs_me3,gene_anno = mouse_anno, column_name = 'gene_name',gene = 'Tnf',y_lim = 220, up_extend = 2000, down_extend = 250,sample_order = c("CTX_me3", "HPP_me3","PFC_me3","STR_me3","VTA_me3"),
                                    col_pal = c("#FF9289","#FF8AFF","#00DB98","#00CBFF","#BEC100"))
p1_bigWigs_IgG_Tnf <- coverage_vis_gene(coverage_table = bigWigs_IgG,gene_anno = mouse_anno, column_name = 'gene_name',gene = 'Tnf',y_lim = 220, up_extend = 2000, down_extend = 250,sample_order = c("IgG"),
                                        col_pal = c("black"))
p1_coverage_info_RNA_Tnf <- coverage_vis_gene(coverage_table = coverage_info_RNA,gene_anno = mouse_anno, column_name = 'gene_name',gene = 'Tnf',up_extend = 2000,down_extend = 250, y_lim = 15000,sample_order = c("CTX_rna",  "HPP_rna", "PFC_rna", "STR_rna", "VTA_rna"),
                                      col_pal = c("#FF9289","#FF8AFF","#00DB98","#00CBFF","#BEC100"))
Tnf <- gene_track_vis(gene_anno = mouse_anno,column_name = 'gene_name',gene = 'Tnf',up_extend = 2000,down_extend = 250,show_only = FALSE)
p1_Tnf <- p1_bigWigs_ac_Tnf + theme(axis.ticks.x = element_blank(),axis.text.x = element_blank(),axis.title.x = element_blank())
p2_Tnf <- p1_bigWigs_me3_Tnf + theme(axis.ticks.x = element_blank(),axis.text.x = element_blank(),axis.title.x = element_blank(),legend.position = 'none')
p3_Tnf <- p1_bigWigs_IgG_Tnf + theme(axis.ticks.x = element_blank(),axis.text.x = element_blank(),axis.title.x = element_blank(),legend.position = 'none')
p4_Tnf <- p1_coverage_info_RNA_Tnf + theme(axis.ticks.x = element_blank(),axis.text.x = element_blank(),axis.title.x = element_blank())



TNFPlot <- print(p1_Tnf + p2_Tnf + p3_Tnf + p4_Tnf + Tnf + plot_layout(ncol = 1,heights = c(0.3,0.3,0.05,0.3,0.05)))

#grDevices::pdf(file.path(plotOutputDir, "IGVPlots_Tnfa.pdf"), width = 8, height = 8)
TNFPlot
#grDevices::dev.off()

###########################################
###                                   #####
###         Plotting Msx1             #####
###                                   #####
###########################################

p1_bigWigs_ac_Msx1 <- coverage_vis_gene(coverage_table = bigWigs_ac, 
                                          gene_anno = mouse_anno, 
                                          column_name = 'gene_name',
                                          gene = 'Msx1',
                                          y_lim = 50, 
                                          up_extend = 50,
                                          down_extend = 50,
                                          sample_order = c("CTX_ac","HPP_ac","PFC_ac", "STR_ac", "VTA_ac"),
                                          col_pal = c("#FF9289","#FF8AFF","#00DB98","#00CBFF","#BEC100"))

p1_bigWigs_me3_Msx1 <- coverage_vis_gene(coverage_table = bigWigs_me3,
                                           gene_anno = mouse_anno, 
                                           column_name = 'gene_name',
                                           gene = 'Msx1',
                                           y_lim = 50, 
                                           up_extend = 50, 
                                           down_extend = 50,
                                           sample_order = c("CTX_me3", "HPP_me3","PFC_me3","STR_me3","VTA_me3"),
                                           col_pal = c("#FF9289","#FF8AFF","#00DB98","#00CBFF","#BEC100"))

p1_bigWigs_IgG_Msx1 <- coverage_vis_gene(coverage_table = bigWigs_IgG,
                                           gene_anno = mouse_anno, 
                                           column_name = 'gene_name',
                                           gene = 'Msx1',
                                           y_lim = 50, 
                                           up_extend = 50, 
                                           down_extend = 50,
                                           sample_order = c("IgG"),
                                           col_pal = c("black"))

p1_coverage_info_RNA_Msx1 <- coverage_vis_gene(coverage_table = coverage_info_RNA,
                                                 gene_anno = mouse_anno, 
                                                 column_name = 'gene_name',
                                                 gene = 'Msx1',
                                                 up_extend = 50,
                                                 down_extend = 50, 
                                                 y_lim = 20000,
                                                 sample_order = c("CTX_rna",  "HPP_rna", "PFC_rna", "STR_rna", "VTA_rna"),
                                                 col_pal = c("#FF9289","#FF8AFF","#00DB98","#00CBFF","#BEC100"))


Msx1 <- gene_track_vis(gene_anno = mouse_anno,column_name = 'gene_name',gene = 'Msx1',up_extend = 50,down_extend = 50,show_only = FALSE)
p1_Msx1 <- p1_bigWigs_ac_Msx1 + theme(axis.ticks.x = element_blank(),axis.text.x = element_blank(),axis.title.x = element_blank(),legend.position = 'none')
p2_Msx1 <- p1_bigWigs_me3_Msx1 + theme(axis.ticks.x = element_blank(),axis.text.x = element_blank(),axis.title.x = element_blank(),legend.position = 'none')
p3_Msx1 <- p1_bigWigs_IgG_Msx1 + theme(axis.ticks.x = element_blank(),axis.text.x = element_blank(),axis.title.x = element_blank(),legend.position = 'none')
p4_Msx1 <- p1_coverage_info_RNA_Msx1 + theme(axis.ticks.x = element_blank(),axis.text.x = element_blank(),axis.title.x = element_blank())

Msx1Plot <- print(p1_Msx1 + p2_Msx1 + p3_Msx1 + p4_Msx1 + Msx1 + plot_layout(ncol = 1,heights = c(0.3,0.3,0.05,0.3,0.05)))


#grDevices::pdf(file.path(plotOutputDir, "IGVPlots_Msx1.pdf"), width = 8, height = 8)
Msx1Plot
#grDevices::dev.off()

###########################################
###                                   #####
###         Plotting Rbfox3           #####
###                                   #####
###########################################

p1_bigWigs_ac_Rbfox3 <- coverage_vis_gene(coverage_table = bigWigs_ac, 
                                           gene_anno = mouse_anno, 
                                           column_name = 'gene_name',
                                           gene = 'Rbfox3',
                                           y_lim = 100, 
                                           up_extend = 0,
                                           down_extend = 0,
                                           sample_order = c("CTX_ac","HPP_ac","PFC_ac", "STR_ac", "VTA_ac"),
                                           col_pal = c("#FF9289","#FF8AFF","#00DB98","#00CBFF","#BEC100"))

p1_bigWigs_me3_Rbfox3 <- coverage_vis_gene(coverage_table = bigWigs_me3,
                                            gene_anno = mouse_anno, 
                                            column_name = 'gene_name',
                                            gene = 'Rbfox3',
                                            y_lim = 100, 
                                            up_extend = 0, 
                                            down_extend = 0,
                                            sample_order = c("CTX_me3", "HPP_me3","PFC_me3","STR_me3","VTA_me3"),
                                            col_pal = c("#FF9289","#FF8AFF","#00DB98","#00CBFF","#BEC100"))

p1_bigWigs_IgG_Rbfox3 <- coverage_vis_gene(coverage_table = bigWigs_IgG,
                                            gene_anno = mouse_anno, 
                                            column_name = 'gene_name',
                                            gene = 'Rbfox3',
                                            y_lim = 100, 
                                            up_extend = 0, 
                                            down_extend = 0,
                                            sample_order = c("IgG"),
                                            col_pal = c("black"))

p1_coverage_info_RNA_Rbfox3 <- coverage_vis_gene(coverage_table = coverage_info_RNA,
                                                  gene_anno = mouse_anno, 
                                                  column_name = 'gene_name',
                                                  gene = 'Rbfox3',
                                                  up_extend = 0,
                                                  down_extend = 0, 
                                                  y_lim = 250,
                                                  sample_order = c("CTX_rna",  "HPP_rna", "PFC_rna", "STR_rna", "VTA_rna"),
                                                  col_pal = c("#FF9289","#FF8AFF","#00DB98","#00CBFF","#BEC100"))


Rbfox3 <- gene_track_vis(gene_anno = mouse_anno,column_name = 'gene_name',gene = 'Rbfox3',up_extend = 0,down_extend = 0,show_only = FALSE)
p1_Rbfox3 <- p1_bigWigs_ac_Rbfox3 + theme(axis.ticks.x = element_blank(),axis.text.x = element_blank(),axis.title.x = element_blank(),legend.position = 'none')
p2_Rbfox3 <- p1_bigWigs_me3_Rbfox3 + theme(axis.ticks.x = element_blank(),axis.text.x = element_blank(),axis.title.x = element_blank(),legend.position = 'none')
p3_Rbfox3 <- p1_bigWigs_IgG_Rbfox3 + theme(axis.ticks.x = element_blank(),axis.text.x = element_blank(),axis.title.x = element_blank(),legend.position = 'none')
p4_Rbfox3 <- p1_coverage_info_RNA_Rbfox3 + theme(axis.ticks.x = element_blank(),axis.text.x = element_blank(),axis.title.x = element_blank())

Rbfox3Plot <- print(p1_Rbfox3 + p2_Rbfox3 + p3_Rbfox3 + p4_Rbfox3 + Rbfox3 + plot_layout(ncol = 1,heights = c(0.3,0.3,0.05,0.3,0.1)))

#grDevices::pdf(file.path(plotOutputDir, "IGVPlots_Rbfox3.pdf"), width = 8, height = 8)
Rbfox3Plot
#grDevices::dev.off()


###########################################
###                                   #####
###         Plotting Il1a           #####
###                                   #####
###########################################

p1_bigWigs_ac_Il1a <- coverage_vis_gene(coverage_table = bigWigs_ac, 
                                          gene_anno = mouse_anno, 
                                          column_name = 'gene_name',
                                          gene = 'Il1a',
                                          y_lim = 400, 
                                          up_extend = 1000,
                                          down_extend = 1000,
                                          sample_order = c("CTX_ac","HPP_ac","PFC_ac", "STR_ac", "VTA_ac"),
                                          col_pal = c("#FF9289","#FF8AFF","#00DB98","#00CBFF","#BEC100"))

p1_bigWigs_me3_Il1a <- coverage_vis_gene(coverage_table = bigWigs_me3,
                                           gene_anno = mouse_anno, 
                                           column_name = 'gene_name',
                                           gene = 'Il1a',
                                           y_lim = 400, 
                                           up_extend = 1000, 
                                           down_extend = 1000,
                                           sample_order = c("CTX_me3", "HPP_me3","PFC_me3","STR_me3","VTA_me3"),
                                           col_pal = c("#FF9289","#FF8AFF","#00DB98","#00CBFF","#BEC100"))

p1_bigWigs_IgG_Il1a <- coverage_vis_gene(coverage_table = bigWigs_IgG,
                                           gene_anno = mouse_anno, 
                                           column_name = 'gene_name',
                                           gene = 'Il1a',
                                           y_lim = 400, 
                                           up_extend = 1000, 
                                           down_extend = 1000,
                                           sample_order = c("IgG"),
                                           col_pal = c("black"))

p1_coverage_info_RNA_Il1a <- coverage_vis_gene(coverage_table = coverage_info_RNA,
                                                 gene_anno = mouse_anno, 
                                                 column_name = 'gene_name',
                                                 gene = 'Il1a',
                                                 up_extend = 1000,
                                                 down_extend = 1000, 
                                                 y_lim = 50000,
                                                 sample_order = c("CTX_rna",  "HPP_rna", "PFC_rna", "STR_rna", "VTA_rna"),
                                                 col_pal = c("#FF9289","#FF8AFF","#00DB98","#00CBFF","#BEC100"))


Il1a <- gene_track_vis(gene_anno = mouse_anno,column_name = 'gene_name',gene = 'Il1a',up_extend = 1000,down_extend = 1000,show_only = FALSE)
p1_Il1a <- p1_bigWigs_ac_Il1a + theme(axis.ticks.x = element_blank(),axis.text.x = element_blank(),axis.title.x = element_blank(),legend.position = 'none')
p2_Il1a <- p1_bigWigs_me3_Il1a + theme(axis.ticks.x = element_blank(),axis.text.x = element_blank(),axis.title.x = element_blank(),legend.position = 'none')
p3_Il1a <- p1_bigWigs_IgG_Il1a + theme(axis.ticks.x = element_blank(),axis.text.x = element_blank(),axis.title.x = element_blank(),legend.position = 'none')
p4_Il1a <- p1_coverage_info_RNA_Il1a + theme(axis.ticks.x = element_blank(),axis.text.x = element_blank(),axis.title.x = element_blank())

Il1aPlot <- print(p1_Il1a + p2_Il1a + p3_Il1a + p4_Il1a + Il1a + plot_layout(ncol = 1,heights = c(0.3,0.3,0.05,0.3,0.1)))

#grDevices::pdf(file.path(plotOutputDir, "IGVPlots_Il1a.pdf"), width = 8, height = 8)
Il1aPlot
#grDevices::dev.off()

```

# Package Versions

```{r Save Package Version Info, echo=TRUE, message=TRUE, warning=FALSE}

projdir <- "/home/avm27/Documents/Raw_Sequencing_Data/BrainRegionMicroglia/RegionalMicroglialTranscriptomicsandEpigenomics"

#Record Package Versions Used in this analysis
index8_packages <- c(
  "ggplot2",
  "knitr",
  "patchwork",
  "rtracklayer",
  "TrackPlotR",
  "workflowr"
)

# Retrieve Each Package Version
get_package_version <- function(package_name) {

  package_path <- find.package(
    package_name,
    quiet = TRUE
  )

  package_loaded <- package_name %in% loadedNamespaces()

  if (length(package_path) == 0L) {
    return(
      data.frame(
        package = package_name,
        installed = FALSE,
        loaded = FALSE,
        version = NA_character_,
        library_path = NA_character_,
        stringsAsFactors = FALSE
      )
    )
  }

  package_path <- package_path[[1]]

  data.frame(
    package = package_name,
    installed = TRUE,
    loaded = package_loaded,
    version = as.character(
      utils::packageVersion(
        package_name,
        lib.loc = dirname(package_path)
      )
    ),
    library_path = dirname(package_path),
    stringsAsFactors = FALSE
  )
}


# Collect Package and R Environment Versions
index8_package_versions <- do.call(
  rbind,
  lapply(
    index8_packages,
    get_package_version
  )
)

index8_environment_versions <- data.frame(
  R_version = paste(
    R.version$major,
    R.version$minor,
    sep = "."
  ),
  Bioconductor_version = if (
    requireNamespace("BiocManager", quietly = TRUE)
  ) {
    as.character(BiocManager::version())
  } else {
    NA_character_
  },
  platform = R.version$platform,
  stringsAsFactors = FALSE
)


# Save Version Records

utils::write.csv(
  index8_package_versions,
  file = paste0(projdir, "/code/RPackageVersions/index8_package_versions.csv"),
  row.names = FALSE
)

utils::write.csv(
  index8_environment_versions,
  file = paste0(projdir, "/code/RPackageVersions/index8_R_and_Bioconductor_versions.csv"),
  row.names = FALSE
)

capture.output(
  sessionInfo(),
  file = paste0(projdir, "/code/RPackageVersions/index8_sessionInfo.txt")
)



# Print Results
print(index8_environment_versions, row.names = FALSE)
print(index8_package_versions, row.names = FALSE)

```

# Session Info

```{r Print Session Info, echo=TRUE, message=TRUE, warning=FALSE}
sessionInfo()
```
