---
title: "BRMic WGCNA Workflow"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: false
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE, include = FALSE)

library(BiocParallel)
library(DESeq2)
library(SummarizedExperiment)
library(WGCNA)
library(dynamicTreeCut)
library(fastcluster)
library(conflicted)
library(dplyr)
library(tidyr)
library(AnnotationDbi)
library(org.Mm.eg.db)
library(clusterProfiler)
library(ReactomePA)
library(enrichplot)
library(ggplot2)
library(igraph)

register(DoparParam())
register(MulticoreParam())
registered()

options(warn = 0)
options(stringsAsFactors = FALSE)

allowWGCNAThreads()

```


# Load and Setup Data
## Setting up Working Directory
```{r Read In Files, message=FALSE, warning=FALSE, include=FALSE}
# Identify the repository root from the opened RStudio project
projdir <- normalizePath(".", winslash = "/", mustWork = TRUE)

project_file <- file.path(projdir, "RegionalMicroglialTranscriptomicsandEpigenomics.Rproj")

if (!file.exists(project_file)) {
  stop(
    paste(
      "The repository root could not be identified.",
      "Open RegionalMicroglialTranscriptomicsandEpigenomics.Rproj",
      "before running this analysis."
    )
  )
}

# Define Output Directories
plots_dir <- file.path(projdir, "output", "WGCNA", "plots")
results_dir <- file.path(projdir, "output", "WGCNA", "results")
rdata_dir <- file.path(projdir, "output", "WGCNA", "r_data")

# Create Output Directories
dir.create(plots_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(results_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(rdata_dir, recursive = TRUE, showWarnings = FALSE)

# Define Input Files
data_dir <- file.path(projdir, "data", "RNASeq_WGCNA")
data_file <- file.path(data_dir, "BRMIC_gene_count_matrix.csv")
metadata_file <- file.path(data_dir, "BRMIC_Metadata.tsv")

# Confirm Required Input Files Exist
file.exists(data_file)
file.exists(metadata_file)

```


## Import and Set Up Data

```{r pressure, include=FALSE}
# Read in metadata TSV file
metadata <- readr::read_tsv(metadata_file)

# Read in data TSV file
df <- readr::read_csv(data_file, show_col_types = TRUE) %>%
  tibble::column_to_rownames("gene_id")

head(df)

# Make the data in the order of the metadata
df <- df %>%
  dplyr::select(metadata$refinebio_accession_code)

# Check if this is in the same order
all.equal(colnames(df), metadata$refinebio_accession_code)

```

```{r Prepare Data for DESeq2, include=FALSE}
# The next DESeq2 functions need the values to be converted to integers
df <- round(df) %>%
  # The next steps require a data frame and round() returns a matrix
  as.data.frame() %>%
  # Only keep rows that have total counts above the cutoff
  dplyr::filter(rowSums(.) >= 50)


metadata <- metadata %>%
  dplyr::mutate(
    time_point = dplyr::case_when(
      stringr::str_detect(refinebio_title, "Cortex") ~ "CTX",
      stringr::str_detect(refinebio_title, "Hippocampus") ~ "HPP",
      stringr::str_detect(refinebio_title, "PreFrontalCtx") ~ "PFC",
      stringr::str_detect(refinebio_title, "Striatum") ~ "STR",
      stringr::str_detect(refinebio_title, "VentralTegmentalArea") ~ "VTA"
    ),
    time_point = as.factor(time_point)
  )

levels(metadata$time_point)

```

```{r Create DESeq2 Object, include=FALSE}

# Create a `DESeqDataSet` object
dds <- DESeqDataSetFromMatrix(
  countData = df, # Our prepped data frame with counts
  colData = metadata, # Data frame with annotation for our samples
  design = ~1
)

# Normalize and transform the data in the `DESeqDataSet` object using the `vst()`
# function from the `DESEq2` R package
dds_norm <- vst(dds)

df <- assay(dds_norm) %>% as.data.frame

datExpr0 = as.data.frame(t(df));
names(datExpr0) = rownames(df);
rownames(datExpr0) = names(df);

```

# WCGNA

## Set Up
```{r Check if samples are good to run, echo=TRUE}

gsg = goodSamplesGenes(datExpr0, verbose = 3);
gsg$allOK

sampleTree = hclust(dist(datExpr0), method = "average");
##pdf(file = paste0(plots_dir, "/sampleClustering--withoutCuts--PreOutlierRemoval.pdf"), width = 12, height = 9);
par(cex = 0.6);
par(mar = c(0,4,2,0))
plot(sampleTree, main = "Sample clustering to detect outliers -- Without Cuts", sub="", xlab="", cex.lab = 1.5,
cex.axis = 1.5, cex.main = 2)
#dev.off()

#pdf(file = paste0(plots_dir, "/sampleClustering--withCuts--PreOutlierRemoval.pdf"), width = 12, height = 9);
par(cex = 0.6);
par(mar = c(0,4,2,0))
plot(sampleTree, main = "Sample clustering to detect outliers -- With Cuts", sub="", xlab="", cex.lab = 1.5,
cex.axis = 1.5, cex.main = 2)
abline(h = 50, col = "red");
#dev.off()


clust = cutreeStatic(sampleTree, cutHeight = 40, minSize = 2)
table(clust)


# clust 1 contains the samples we want to keep.
keepSamples = (clust>=1)
datExpr = datExpr0[keepSamples, ]
nGenes = ncol(datExpr)
nSamples = nrow(datExpr)
clust
rownames(datExpr)

sampleTree = hclust(dist(datExpr), method = "average");
#pdf(file = paste0(plots_dir, "/SampleClustering--PreOutlierRemoval..pdf"), width = 12, height = 9);
par(cex = 0.6);
par(mar = c(0,4,2,0))
plot(sampleTree, main = "Sample clustering to detect outliers -- Final", sub="", xlab="", cex.lab = 1.5,
cex.axis = 1.5, cex.main = 2)
#dev.off()



```

## Import and Set Up Data

Based on the above sample clustering, we find that MCTX4 and MCTX7 are outliers to the CTX group as the cluster towards the HPP samples. Furthermore, analysis reveals that these two CTX samples may exhibit infiltration of microglia from other regions, causing their transcriptomes to more closely align with HPP samples. MVTA8 is also an outlier along with MVTA6 and MVTA8. These samples are removed and the data are reloaded to help re-define the paramenters for input into WGCNA.

```{r Setup 1, include=FALSE}
# Read in metadata TSV file
metadata <- readr::read_tsv(metadata_file)

# Read in data TSV file
df <- readr::read_csv(data_file, show_col_types = TRUE) %>%
  # Here we are going to store the gene IDs as row names so that we can have a numeric matrix to perform calculations on later
  tibble::column_to_rownames("gene_id")

head(df)

# Make the data in the order of the metadata
df <- df %>%
  dplyr::select(metadata$refinebio_accession_code)

# Check if this is in the same order
all.equal(colnames(df), metadata$refinebio_accession_code)

```

```{r Prepare Data for DESeq2, echo=TRUE, message=TRUE, warning=FALSE, paged.print=TRUE}
# The next DESeq2 functions need the values to be converted to integers
df <- round(df) %>%
  as.data.frame() %>%
  dplyr::filter(rowSums(.) >= 50)


## Removing MCTX4 MCTX7 MVTA6 and MVTA8 From Analysis
colnames(df)

df <- df[-c(1,4,25,27)]
metadata <- metadata[-c(1,4,25,27), ]

metadata <- metadata %>%
  dplyr::mutate(
    time_point = dplyr::case_when(
      stringr::str_detect(refinebio_title, "Cortex") ~ "CTX",
      stringr::str_detect(refinebio_title, "Hippocampus") ~ "HPP",
      stringr::str_detect(refinebio_title, "PreFrontalCtx") ~ "PFC",
      stringr::str_detect(refinebio_title, "Striatum") ~ "STR",
      stringr::str_detect(refinebio_title, "VentralTegmentalArea") ~ "VTA"
    ),
    time_point = as.factor(time_point)
  )

```

```{r Create DESeq2 Object, echo=TRUE}

# Create a `DESeqDataSet` object
dds <- DESeqDataSetFromMatrix(
  countData = df, # Our prepped data frame with counts
  colData = metadata, # Data frame with annotation for our samples
  design = ~1 
)

# Normalize and transform the data in the `DESeqDataSet` object using the `vst()` function from the `DESEq2` R package
dds_norm <- vst(dds)

# Retrieve the normalized data from the `DESeqDataSet`
normalized_counts_wcgna_mivsa <- assay(dds_norm) %>%
  t() # Transpose this data

df <- assay(dds_norm) %>% as.data.frame

datExpr0 = as.data.frame(t(df));
names(datExpr0) = rownames(df);
rownames(datExpr0) = names(df);


```

# WCGNA after outlier removal

## Set Up
```{r Check if samples are good to run, echo=TRUE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}

gsg = goodSamplesGenes(datExpr0, verbose = 3);
gsg$allOK

sampleTree = hclust(dist(datExpr0), method = "average");
#pdf(file = paste0(plots_dir, "/sampleClustering--withoutCuts-PostOutlierRemoval.pdf"), width = 12, height = 9);
par(cex = 0.6);
par(mar = c(0,4,2,0))
plot(sampleTree, main = "Sample clustering to detect outliers -- Without Cuts", sub="", xlab="", cex.lab = 1.5,
cex.axis = 1.5, cex.main = 2)
#dev.off()

#pdf(file = paste0(plots_dir, "/sampleClustering--withCuts-PostOutlierRemoval.pdf"), width = 12, height = 9);
par(cex = 0.6);
par(mar = c(0,4,2,0))
plot(sampleTree, main = "Sample clustering to detect outliers -- With Cuts", sub="", xlab="", cex.lab = 1.5,
cex.axis = 1.5, cex.main = 2)
abline(h = 50, col = "red");
#dev.off()


clust = cutreeStatic(sampleTree, cutHeight = 50, minSize = 2)
table(clust)


# clust 1 contains the samples we want to keep.
keepSamples = (clust>=1)
datExpr = datExpr0[keepSamples, ]
nGenes = ncol(datExpr)
nSamples = nrow(datExpr)
clust
rownames(datExpr)

sampleTree = hclust(dist(datExpr), method = "average");
#pdf(file = paste0(plots_dir, "/SampleClustering--Final.pdf"), width = 12, height = 9);
par(cex = 0.6);
par(mar = c(0,4,2,0))
plot(sampleTree, main = "Sample clustering to detect outliers -- Final", sub="", xlab="", cex.lab = 1.5,
cex.axis = 1.5, cex.main = 2)
#dev.off()

```


## Checking Various Networks

```{r Automatic Network Detection --- Select Soft Powers, eval=FALSE, include=FALSE}

################################## BICOR Hybrid ######################################
########################### Select this one with a Power of 7 ########################
conflict_prefer("cor", "WGCNA")
temp_cor <- cor
cor <- WGCNA::bicor

# Choose a set of soft-thresholding powers
powers = c(c(1:34), seq(from = 12, to=34, by=2))
# Call the network topology analysis function
sft = pickSoftThreshold(datExpr, powerVector = powers, verbose = 5, corFnc = cor, networkType = "signed hybrid", blockSize = 23000)
# Plot the results:
#sizeGrWindow(9, 5)
par(mfrow = c(1,2));
cex1 = 0.9;
# Scale-free topology fit index as a function of the soft-thresholding power
#pdf(file = paste0(plots_dir, "/AutoDetect-SoftPowerSelection--bicor--hybrid--NOCTX.pdf"), width = 12, height = 9);
plot(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
xlab="Soft Threshold (power)",ylab="Scale Free Topology Model Fit,signed R^2",type="n",
main = paste("Scale independence"));
text(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
labels=powers,cex=cex1,col="red");
abline(h=0.90,col="red")
# Mean connectivity as a function of the soft-thresholding power
plot(sft$fitIndices[,1], sft$fitIndices[,5],
xlab="Soft Threshold (power)",ylab="Mean Connectivity", type="n",
main = paste("Mean connectivity"))
text(sft$fitIndices[,1], sft$fitIndices[,5], labels=powers, cex=cex1,col="red")
#dev.off()

########################## BICOR Unsigned ###########################
# Call the network topology analysis function
sft = pickSoftThreshold(datExpr, powerVector = powers, verbose = 5, corFnc = cor, networkType = "unsigned", blockSize = 23000)
# Plot the results:
#sizeGrWindow(9, 5)
par(mfrow = c(1,2));
cex1 = 0.9;
# Scale-free topology fit index as a function of the soft-thresholding power
#pdf(file = paste0(plots_dir, "/AutoDetect-SoftPowerSelection--bicor--unsigned.pdf"), width = 12, height = 9);
plot(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
xlab="Soft Threshold (power)",ylab="Scale Free Topology Model Fit,signed R^2",type="n",
main = paste("Scale independence"));
text(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
labels=powers,cex=cex1,col="red");
abline(h=0.90,col="red")

# Mean connectivity as a function of the soft-thresholding power
plot(sft$fitIndices[,1], sft$fitIndices[,5],
xlab="Soft Threshold (power)",ylab="Mean Connectivity", type="n",
main = paste("Mean connectivity"))
text(sft$fitIndices[,1], sft$fitIndices[,5], labels=powers, cex=cex1,col="red")
#dev.off()

########################## BICOR Signed ###########################
# Call the network topology analysis function
sft = pickSoftThreshold(datExpr, powerVector = powers, verbose = 5, corFnc = cor, networkType = "signed", blockSize = 23000)
# Plot the results:
#sizeGrWindow(9, 5)
par(mfrow = c(1,2));
cex1 = 0.9;
# Scale-free topology fit index as a function of the soft-thresholding power
#pdf(file = paste0(plots_dir, "/AutoDetect-SoftPowerSelection--bicor--signed.pdf"), width = 12, height = 9);
plot(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
xlab="Soft Threshold (power)",ylab="Scale Free Topology Model Fit,signed R^2",type="n",
main = paste("Scale independence"));
text(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
labels=powers,cex=cex1,col="red");
abline(h=0.90,col="red")

# Mean connectivity as a function of the soft-thresholding power
plot(sft$fitIndices[,1], sft$fitIndices[,5],
xlab="Soft Threshold (power)",ylab="Mean Connectivity", type="n",
main = paste("Mean connectivity"))
text(sft$fitIndices[,1], sft$fitIndices[,5], labels=powers, cex=cex1,col="red")
#dev.off()


########################## COR Hybrid ###########################
cor <- WGCNA::cor
# Choose a set of soft-thresholding powers
powers = c(c(1:34), seq(from = 12, to=34, by=2))
# Call the network topology analysis function
sft = pickSoftThreshold(datExpr, powerVector = powers, verbose = 5, corFnc = cor, networkType = "signed hybrid", blockSize = 23000)
# Plot the results:
#sizeGrWindow(9, 5)
par(mfrow = c(1,2));
cex1 = 0.9;
# Scale-free topology fit index as a function of the soft-thresholding power
#pdf(file = paste0(plots_dir, "/AutoDetect-SoftPowerSelection--cor--hybrid.pdf"), width = 12, height = 9);
plot(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
xlab="Soft Threshold (power)",ylab="Scale Free Topology Model Fit,signed R^2",type="n",
main = paste("Scale independence"));
text(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
labels=powers,cex=cex1,col="red");
abline(h=0.90,col="red")

# Mean connectivity as a function of the soft-thresholding power
plot(sft$fitIndices[,1], sft$fitIndices[,5],
xlab="Soft Threshold (power)",ylab="Mean Connectivity", type="n",
main = paste("Mean connectivity"))
text(sft$fitIndices[,1], sft$fitIndices[,5], labels=powers, cex=cex1,col="red")
#dev.off()

########################## COR Unsigned ###########################
# Call the network topology analysis function
sft = pickSoftThreshold(datExpr, powerVector = powers, verbose = 5, corFnc = cor, networkType = "unsigned", blockSize = 23000)
# Plot the results:
#sizeGrWindow(9, 5)
par(mfrow = c(1,2));
cex1 = 0.9;
# Scale-free topology fit index as a function of the soft-thresholding power
#pdf(file = paste0(plots_dir, "/AutoDetect-SoftPowerSelection--cor--unsigned.pdf"), width = 12, height = 9);
plot(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
xlab="Soft Threshold (power)",ylab="Scale Free Topology Model Fit,signed R^2",type="n",
main = paste("Scale independence"));
text(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
labels=powers,cex=cex1,col="red");
abline(h=0.90,col="red")

# Mean connectivity as a function of the soft-thresholding power
plot(sft$fitIndices[,1], sft$fitIndices[,5],
xlab="Soft Threshold (power)",ylab="Mean Connectivity", type="n",
main = paste("Mean connectivity"))
text(sft$fitIndices[,1], sft$fitIndices[,5], labels=powers, cex=cex1,col="red")
#dev.off()

########################## COR Signed ###########################
# Call the network topology analysis function
sft = pickSoftThreshold(datExpr, powerVector = powers, verbose = 5, corFnc = cor, networkType = "signed", blockSize = 23000)
# Plot the results:
#sizeGrWindow(9, 5)
par(mfrow = c(1,2));
cex1 = 0.9;
# Scale-free topology fit index as a function of the soft-thresholding power
#pdf(file = paste0(plots_dir, "/AutoDetect-SoftPowerSelection--cor--signed.pdf"), width = 12, height = 9);
plot(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
xlab="Soft Threshold (power)",ylab="Scale Free Topology Model Fit,signed R^2",type="n",
main = paste("Scale independence"));
text(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
labels=powers,cex=cex1,col="red");
abline(h=0.90,col="red")

# Mean connectivity as a function of the soft-thresholding power
plot(sft$fitIndices[,1], sft$fitIndices[,5],
xlab="Soft Threshold (power)",ylab="Mean Connectivity", type="n",
main = paste("Mean connectivity"))
text(sft$fitIndices[,1], sft$fitIndices[,5], labels=powers, cex=cex1,col="red")
#dev.off()


```

## Final Network Selection

```{r echo=TRUE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
cor <- WGCNA::bicor

# Choose a set of soft-thresholding powers
powers = c(c(1:10), seq(from = 12, to=20, by=2))
# Call the network topology analysis function
sft = pickSoftThreshold(datExpr, powerVector = powers, verbose = 5, corFnc = cor, networkType = "signed hybrid", blockSize = 23000)
# Plot the results:
#pdf(file = paste0(plots_dir, "/SoftPowerSelection--FinalSelection.pdf"), width = 12, height = 9);
par(mfrow = c(1,2));
cex1 = 0.9;
# Scale-free topology fit index as a function of the soft-thresholding power
plot(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
xlab="Soft Threshold (power)",ylab="Scale Free Topology Model Fit,signed R^2",type="n",
main = paste("Scale independence"));
text(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
labels=powers,cex=cex1,col="red");
abline(h=0.90,col="red")

# Mean connectivity as a function of the soft-thresholding power
plot(sft$fitIndices[,1], sft$fitIndices[,5],
xlab="Soft Threshold (power)",ylab="Mean Connectivity", type="n",
main = paste("Mean connectivity"))
text(sft$fitIndices[,1], sft$fitIndices[,5], labels=powers, cex=cex1,col="red")
#dev.off()

```

## TOM and Adjacency

```{r eval=FALSE, include=FALSE}
gc()
softPower = 7;
adjacency = adjacency(datExpr, power = softPower, corOptions = list(use = 'p'), corFnc = cor, type = "signed hybrid");
gc()
# Turn adjacency into topological overlap
TOM = TOMsimilarity(adjacency, TOMType = "signed");
dissTOM = 1-TOM
gc()
```


## Gene Tree and Calculating Overlaps

```{r eval=FALSE, include=FALSE}
# Call the hierarchical clustering function
geneTree = hclust(as.dist(dissTOM), method = "average");
# Plot the resulting clustering tree (dendrogram)
#pdf(file = paste0(plots_dir, "GeneClusteringTOMS--Final.pdf"), width = 12, height = 9);
plot(geneTree, xlab="", sub="", main = "Gene clustering on TOM-based dissimilarity",
labels = FALSE, hang = 0.04);
#dev.off()
# We like large modules, so we set the minimum module size relatively high:
minModuleSize = 40;
# Module identification using dynamic tree cut:
dynamicMods = cutreeDynamic(dendro = geneTree, distM = dissTOM,
deepSplit = 3, pamRespectsDendro = TRUE,
minClusterSize = minModuleSize);
table(dynamicMods)

# Convert numeric lables into colors
dynamicColors = labels2colors(dynamicMods)
table(dynamicColors)
# Plot the dendrogram and colors underneath
#pdf(file = paste0(plots_dir, "/DendroColors-Final.pdf"), wi = 9, he = 6)
sizeGrWindow(8,6)
plotDendroAndColors(geneTree, dynamicColors, "Dynamic Tree Cut",
dendroLabels = FALSE, hang = 0.03,
addGuide = TRUE, guideHang = 0.05,
main = "Gene dendrogram and module colors")
#dev.off()
# Calculate eigengenes
MEList = moduleEigengenes(datExpr, colors = dynamicColors, softPower = softPower)
MEs = MEList$eigengenes
# Calculate dissimilarity of module eigengenes
MEDiss = 1-cor(MEs);
# Cluster module eigengenes
METree = hclust(as.dist(MEDiss), method = "average");
# Plot the result
#pdf(file = paste0(plots_dir, "/METree-Final.pdf"), width = 12, height = 9);
plot(METree, main = "Clustering of module eigengenes",
xlab = "", sub = "")
MEDissThres = 0.25
# Plot the cut line into the dendrogram
abline(h=MEDissThres, col = "red")
#dev.off()
# Call an automatic merging function
merge = mergeCloseModules(datExpr, dynamicColors, cutHeight = MEDissThres, verbose = 3)
# The merged module colors
mergedColors = merge$colors;
# Eigengenes of the new merged modules:
mergedMEs = merge$newMEs;

#pdf(file = paste0(plots_dir, "/geneDendro-Final.pdf"), wi = 9, he = 6)
plotDendroAndColors(geneTree, cbind(dynamicColors, mergedColors),
c("Dynamic Tree Cut", "Merged dynamic"),
dendroLabels = FALSE, hang = 0.03,
addGuide = TRUE, guideHang = 0.05)
#dev.off()

# Rename to moduleColors
moduleColors = mergedColors
# Construct numerical labels corresponding to the colors
colorOrder = c("grey", standardColors(50));
moduleLabels = match(moduleColors, colorOrder)-1;
MEs = mergedMEs;

###### QC Checks

moduleSizes <- table(moduleColors)
barplot(sort(moduleSizes, decreasing = TRUE), las=2, main="Module size distribution")

plotEigengeneNetworks(MEs, "", marDendro = c(3,3,2,4), marHeatmap = c(3,4,2,2))

```

## Identifying Statistcally Significantly Expressed Modules

```{r eval=FALSE, include=FALSE}
## Check Module Expression
module_colors_df <- MEs %>%
  tibble::rownames_to_column("accession_code") %>%
  dplyr::inner_join(metadata %>%
    dplyr::select(refinebio_accession_code, time_point),
  by = c("accession_code" = "refinebio_accession_code")
  )

## Write Results to a saved file
#write.table(module_colors_df , paste0(results_dir, "/WGCNA_Module_Expression-Final.txt"))

## Ensure that the samples martch the same ones used in the actual calculations
all.equal(metadata$refinebio_accession_code, rownames(MEs))

## Create the model
des_mat <- model.matrix(~-1 + metadata$time_point)
# Fit the model to the dataframes
fit <- limma::lmFit(t(MEs), design = des_mat)
## Run Bayes model to check for module significance
fit <- limma::eBayes(fit)
## Check for module epression significance
stats_df <- limma::topTable(fit, number = ncol(MEs)) %>%
  tibble::rownames_to_column("module")
# Check Results
head(stats_df)


# Sorting 'stats_df' by 'adj.P.Val'
stats_df_sorted <- stats_df[order(stats_df$adj.P.Val), ]
# Filtering rows where 'adj.P.Val' is less than or equal to 0.01
filtered_stats_df <- subset(stats_df_sorted, adj.P.Val <= 0.01)
# Extracting the 'modules' 
modules <- filtered_stats_df$module
modules_significant <- substring(modules, 3)


#write.table(stats_df, paste0(results_dir, "/WCGNA_limma_stats_modules-Final.txt"))
```

## Plotting Module Expression

```{r}

module_colors_df$time_point <- factor(
  module_colors_df$time_point,
  levels = c("CTX","HPP","PFC",
             "STR","VTA")  # Replace with your desired order
)

#pdf(file = paste0(plots_dir, "/Rplots_SignificantModules_WGCNA-Final.pdf"))
for (module in modules) {

  p <- ggplot(
  module_colors_df,
  aes(
    x = time_point,
    y = .data[[module]],
    color = time_point
  )
) +
    geom_boxplot(width = 0.5, outlier.shape = NA) +
    ggforce::geom_sina(maxwidth = 0.3) +
    geom_text(
    aes(label = accession_code),
    position = position_jitter(width = 0.2),  # slight jitter to avoid overlap
    size = 3,  # adjust size as needed
    vjust = -0.5,
    show.legend = FALSE
  ) +
    theme_classic() +
    ggtitle(paste("Expression of Module:", module))
  
  print(p)
}
#dev.off()

```

## Calculate Module Meber and Extract Highly Modular Genes

```{r Module Membership, eval=FALSE, include=FALSE}

# Step 1: Correlate gene expression with module eigengenes
modNames <- substring(names(MEs), 3)
cor <- WGCNA::cor

geneModuleMembership <- as.data.frame(cor(datExpr, MEs, use = "p"))
MMPvalue <- as.data.frame(corPvalueStudent(as.matrix(geneModuleMembership), nSamples))

# Step 2: Extract gene symbols from rownames
name_df <- data.frame(gene_id = rownames(MMPvalue))
name_df <- name_df %>%
  tidyr::separate(gene_id, into = c("ID", "symbol"), sep = "([|])")

name_df_GS <- data.frame(gene_id = rownames(geneModuleMembership))
name_df_GS <- name_df_GS %>%
  tidyr::separate(gene_id, into = c("ID", "symbol"), sep = "([|])")

# Extract rownames again after the separate step
extracted_names <- name_df$ID
extracted_names2 <- name_df_GS$ID

# Compare extracted names to original rownames
all(extracted_names == gsub("([|].*)", "", rownames(MMPvalue)))
all(extracted_names2 == gsub("([|].*)", "", rownames(geneModuleMembership)))

all(extracted_names == MMPvalue$ID)
all(extracted_names2 == geneModuleMembership$ID)

# Step 3: Add ID column to MMPvalue and remove rownames
MMPvalue2 = MMPvalue
MMPvalue2$ID <- name_df$ID
MMPvalue2 <- MMPvalue2[, c(ncol(MMPvalue2), 1:(ncol(MMPvalue2)-1))]  # Move ID to first column
rownames(MMPvalue2) <- NULL

geneModuleMembership2 = geneModuleMembership
geneModuleMembership2$ID <- name_df_GS$ID
geneModuleMembership2 <- geneModuleMembership2[, c(ncol(geneModuleMembership2), 1:(ncol(geneModuleMembership2)-1))]  # Move ID to first column
rownames(geneModuleMembership2) <- NULL

modNames <- substring(names(MMPvalue2)[-1], 3)

### Filter on both MM and p-value #######
selected_gene_list <- list()

for (mod in modNames) {
  cor_col <- paste0("ME", mod)
  pval_col <- paste0("ME", mod)
  
  # genes with abs(MM) > 0.7 and p-value < 0.05
  selected <- geneModuleMembership2$ID[
    geneModuleMembership2[[cor_col]] > 0.8 &
    MMPvalue2[[pval_col]] < 0.05
  ]
  
  selected_gene_list[[mod]] <- selected
}

# Convert gene symbols to Entrez IDs for each module
modulememberGeneSets.Entrez <- lapply(selected_gene_list, function(genes) {
  clusterProfiler::bitr(genes, fromType = "SYMBOL", toType = "ENTREZID", OrgDb = "org.Mm.eg.db")$ENTREZID
})

# Loop through each module and assign the corresponding subset to a new variable
for (mod in modules_significant) {
  var_name <- paste0("modulememberGeneSets.Entrez.New.", tools::toTitleCase(mod))
  assign(var_name, modulememberGeneSets.Entrez[[mod]])
}

modulememberGeneSets.Entrez.New <- list()
for (mod in modules_significant) {
  modulememberGeneSets.Entrez.New[[mod]] <- modulememberGeneSets.Entrez[[mod]]
}

#entrezmoduleassignments <- capture.output(modulememberGeneSets.Entrez.New)
#genemoduleassignments <- capture.output(selected_gene_list)
#writeLines(entrezmoduleassignments, con = paste0(results_dir, "/EntrezModuleAssignments_HighlyModularMembers.txt"))
#writeLines(genemoduleassignments, con = paste0(results_dir, "/GeneModuleAssignments_HighlyModularMembers.txt"))
```

## Pathway Enrichment Analysis of Highly Modular Genes

```{r Gene Enrichment based on High Membership Genes, eval=FALSE, include=FALSE}

## Take out any genes in Grey Module (not grouped) and then create background for functional analysis
restGenes = (moduleColors != "grey")  
datExpr_without_grey <- datExpr[, restGenes]
background_genenames <- (as.data.frame(colnames(datExpr_without_grey)))

background_genenames$symbols <- background_genenames[,1]
newrownames_background <- background_genenames %>% tidyr::separate(symbols, c("id", "symbol"),sep ="([|])")

all(newrownames_background$id == newrownames_background$symbol)
sum(is.na(newrownames_background$symbol))
sum(duplicated(newrownames_background$symbol))


newrownames_background$entrez <- mapIds(x = org.Mm.eg.db,
                      keys = newrownames_background$symbol,
                      column = "ENTREZID",
                      keytype = "SYMBOL",
                      multiVals = "first")

background_mm10_WGCNA <- subset(newrownames_background, is.na(entrez) == FALSE)
gene_matrix_background_WGCNA <- unique(sort(background_mm10_WGCNA$entrez))

#write.csv(gene_matrix_background_WGCNA, paste0(results_dir, "/background_genes_WGCNA-Final.csv"))

######################################################################################################################################################################################################


# Looking at KEGG Geneset Enrichment
ck<-compareCluster(geneCluster=modulememberGeneSets.Entrez.New,
                   fun="enrichKEGG",organism="mmu",pvalueCutoff = 0.05, universe = gene_matrix_background_WGCNA)

# Looking at GO Geneset Enrichment
cg <-compareCluster(geneCluster=modulememberGeneSets.Entrez.New, fun="enrichGO",
                      OrgDb = "org.Mm.eg.db", pvalueCutoff = 0.05,ont = "ALL", readable = T, universe = gene_matrix_background_WGCNA)

# Looking at reactome enrichment
cr <- compareCluster(geneCluster=modulememberGeneSets.Entrez.New,fun="enrichPathway",
                   organism="mouse",pvalueCutoff = 0.05, readable = T, universe = gene_matrix_background_WGCNA)

## Apply Filtering
cg_simplified <- clusterProfiler::simplify(cg, cutoff=0.8, by="p.adjust", select_fun=min)

#pdf(file= paste0(plots_dir,"/BRMicCATD-all-module_geneset_enrichments_HihgModMembersOnly--Final.pdf"),width=20,height=5)
dotplot(ck,showCategory=15)+ggtitle("KEGG geneset enrichment by module")+theme_bw()+ coord_flip()+theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8, color = "black"))
dotplot(cr,showCategory=15)+ggtitle("Reactome geneset enrichment by module")+theme_bw()+ coord_flip()+theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8, color = "black"))
dotplot(cg,showCategory=10)+ggtitle("GO geneset enrichment by module")+theme_bw()+ coord_flip()+theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8, color = "black"))
dotplot(cg_simplified, showCategory = 15, font.size = 12)+ggtitle("GO geneset Simplified enrichment by module")
#dev.off()

#write.table(cg, paste0(results_dir, "/compare_Cluster_enrichGO_ALLONT_MEMEBRSONLY_WGCNA.txt"))
#write.table(ck, paste0(results_dir, "/compare_Cluster_enrichKEGG_MEMEBRSONLY_WGCNA.txt"))
#write.table(cr, paste0(results_dir, "/compare_Cluster_enrichReactome_MEMEBRSONLY_WGCNA.txt"))
#write.table(cg_simplified, paste0(results_dir, "/compare_Cluster_enrichGO_Simplified_ALLONT_MEMEBRSONLY_WGCNA.txt"))

cg.final <-as.data.frame(cg)
ck.final <- as.data.frame(ck)
cg.simplified.final <- as.data.frame(cg_simplified)

# Filter rows where ONTOLOGY column contains "CC" or "BP"
filtered_cg_final <- subset(cg.final, ONTOLOGY == "BP" | ONTOLOGY == "CC")
filtered_cg_simplified_final <- subset(cg.simplified.final, ONTOLOGY == "BP" | ONTOLOGY == "CC")

top5_per_cluster <- filtered_cg_final %>%
  group_by(Cluster) %>%
  arrange(p.adjust, .by_group = TRUE) %>%
  slice_head(n = 5) %>%
  ungroup()

top5_per_cluster_simplified <- filtered_cg_simplified_final %>%
  group_by(Cluster) %>%
  arrange(p.adjust, .by_group = TRUE) %>%
  slice_head(n = 5) %>%
  ungroup()


top5_per_cluster <- top5_per_cluster %>%
  mutate(Description = factor(Description, levels = rev(unique(Description[order(Cluster, p.adjust)]))))

top5_per_cluster_simplified <- top5_per_cluster_simplified %>%
  mutate(Description = factor(Description, levels = rev(unique(Description[order(Cluster, p.adjust)]))))

S1 <- ggplot(
  top5_per_cluster,
  aes(x = Cluster, y = Description, size = Count, color = qvalue)
) +
  geom_point(alpha = 0.8) +
  theme_bw() +
  coord_flip() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 10, color = "black"),
    axis.text.y = element_text(size = 8)
  ) +
  scale_color_gradient(low = "red2", high = "mediumblue", space = "Lab") +
  scale_size(range = c(2, 8))

S1

S1 <- ggplot(top5_per_cluster, aes(x= Cluster, y=Description, size=Count, color=qvalue, group=Cluster)) + geom_point(alpha = 0.8) + 
  theme_bw()+ 
  coord_flip()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 10, color = "black"))
  
S1 = S1+scale_color_gradient(low = "red2",  high = "mediumblue", space = "Lab") 
S1+scale_size(range = c(2, 8))
S1

S2 <- ggplot(
  top5_per_cluster_simplified,
  aes(x = Cluster, y = Description, size = Count, color = qvalue)
) +
  geom_point(alpha = 0.8) +
  theme_bw() +
  coord_flip() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 10, color = "black"),
    axis.text.y = element_text(size = 8)
  ) +
  scale_color_gradient(low = "red2", high = "mediumblue", space = "Lab") +
  scale_size(range = c(2, 8))

S2

S2 <- ggplot(top5_per_cluster_simplified, aes(x= Cluster, y=Description, size=Count, color=qvalue, group=Cluster)) + geom_point(alpha = 0.8) + 
  theme_bw()+ 
  coord_flip()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 10, color = "black"))
  

#pdf(file.path(paste0(plots_dir, "/BRMicCATD-all-module_geneset_enrichments_MEMEBERONLY-SimpandNormal-Final.pdf")),width=15,height=10)
S1 = S1+scale_color_gradient(low = "red2",  high = "mediumblue", space = "Lab") 
S1+scale_size(range = c(2, 8))
#S1

S2 = S2+scale_color_gradient(low = "red2",  high = "mediumblue", space = "Lab") 
S2+scale_size(range = c(2, 8))
#S2
#dev.off()
```

## Making Module Networks

```{r fig.height=15, fig.width=15}

gene.names = names(datExpr)
modGenes <- list()

for (mod in  modules_significant) {
  modGenes[[mod]] <- gene.names[moduleColors == mod]
}

modTOM_list <- list()

for (mod in modules_significant) {
  inModule <- moduleColors == mod
  modGenes <- gene.names[inModule]
  modTOM <- TOM[inModule, inModule]
  dimnames(modTOM) <- list(modGenes, modGenes)
  
  modTOM_list[[mod]] <- modTOM
  
  cat("\n---", mod, "---\n")
  print(dim(modTOM))
  print(head(modTOM[1:5, 1:5]))
}

nTop <- 15
genes <- names(datExpr)

IMConn_list <- list()
top_TOM_list <- list()

for (mod in modules_significant) {
  mod_genes <- genes[moduleColors == mod]
  
  # Compute intramodular connectivity
  IMConn <- softConnectivity(datExpr[, mod_genes])
  IMConn_list[[mod]] <- IMConn
  
  # Identify top genes
  top_genes <- rank(-IMConn) <= nTop
  
  # Subset modTOM matrix (assumes modTOM_list[[mod]] exists)
  top_TOM <- modTOM_list[[mod]][top_genes, top_genes]
  top_TOM_list[[mod]] <- top_TOM
  
  # Optional: show preview
  cat("\n--- Top TOM for", mod, "---\n")
  print(top_TOM[1:min(5, nrow(top_TOM)), 1:min(5, ncol(top_TOM))])
}

genes_top_list <- list()
datExpr_top_list <- list()
graph_list <- list()
vertex_name_tables <- list()

for (mod in modules_significant) {
  # Step 1: Get top genes
  modTOM <- modTOM_list[[mod]]
  IMConn <- IMConn_list[[mod]]
  top_genes <- rank(-IMConn) <= nTop
  gene_names <- rownames(modTOM)[top_genes]
  datExpr_top <- datExpr[, gene_names]
  
  # Step 2: Build graph from correlation matrix
  cor_mat <- cor(datExpr_top, method = "pearson")
  graph <- graph.adjacency(as.matrix(as.dist(cor_mat)),
                            weighted = TRUE, mode = "undirected", diag = FALSE)
  
  graph <- delete_edges(graph, E(graph)[ weight < 0 ])
  
  # Step 3: Simplify graph
  graph <- igraph::simplify(graph, remove.multiple = TRUE, remove.loops = TRUE)
  
  # Step 4: Color edges by sign of correlation
  E(graph)$color <- ifelse(E(graph)$weight < 0.90, "black", "darkred")
  
  # Step 5: Convert edge weights to absolute values
  E(graph)$weight <- abs(E(graph)$weight)
  
  # Step 6: Remove weak edges (< 0.95)
  graph <- delete_edges(graph, E(graph)[weight < 0.80])
  
  # Step 7: Remove orphan vertices
  graph <- delete_vertices(graph, igraph::degree(graph) == 0)
  
  # Step 8: Extract and assign vertex names
  v_names <- V(graph)$name
  vertex_df <- data.frame(name = v_names, new.names = v_names)
  
  # Save everything
  graph_list[[mod]] <- graph
  genes_top_list[[mod]] <- gene_names
  datExpr_top_list[[mod]] <- datExpr_top
  vertex_name_tables[[mod]] <- vertex_df
  
  cat("\nFinished processing module:", mod, "\n")
}


for (mod in modules_significant) {
  # Access name table and graph from lists
  name_df <- vertex_name_tables[[mod]]
  graph_obj <- graph_list[[mod]]
  
  # Separate 'new.names' column into gene_id and symbol using | as separator
  separated <- name_df %>%
    separate(new.names, into = c("gene_id", "symbol"), sep = "\\|")
  
  # Print checks
  cat("Module:", mod, "\n")
  cat("All gene_id == symbol:", all(separated$gene_id == separated$symbol), "\n")
  cat("NA in symbol:", sum(is.na(separated$symbol)), "\n")
  cat("Duplicated symbols:", sum(duplicated(separated$symbol)), "\n")
  cat("All gene_id == symbol again:", all(separated$gene_id == separated$symbol), "\n")
  
  # Add genes column from graph vertex names
  separated$genes <- V(graph_obj)$name
  
  # Check if first column matches genes
  cat("Check separated[1] == genes:", all(separated[[1]] == separated$genes), "\n\n")
  
  # Assign gene_id back to graph vertex names
  V(graph_obj)$name <- separated$gene_id
  
  # Update vertex visual properties
  V(graph_obj)$shape <- "sphere"
  V(graph_obj)$color <- "skyblue"
  V(graph_obj)$vertex.frame.color <- "white"
  
  # Save back into lists
  vertex_name_tables[[mod]] <- separated
  graph_list[[mod]] <- graph_obj

}


scale01 <- function(x) {
  (x - min(x)) / (max(x) - min(x))
}

# Lists to store results
vSizes_list <- list()
edgeweights_list <- list()
mst_edgeweights_list <- list()
mst_list <- list()

for (mod in modules_significant) {
  graph_obj <- graph_list[[mod]]
  expr_mat <- datExpr_top_list[[mod]]  # gene expression matrix for top genes
  
  # Calculate vertex sizes proportional to mean expression (scaled and multiplied by 10)
  mean_expr <- apply(expr_mat, 2, mean)
  vSizes <- (scale01(mean_expr) + 1.0) * 10
  vSizes_list[[mod]] <- vSizes
  
  # Scale edge weights by factor of 2
  edgeweights <- E(graph_obj)$weight * 2.0
  edgeweights_list[[mod]] <- edgeweights
  
  # Assign scaled edge weights back to graph
  E(graph_obj)$weight <- edgeweights
  
  # Compute minimum spanning tree using Prim's algorithm
  mst_graph <- mst(graph_obj, algorithm = "prim")
  mst_list[[mod]] <- mst_graph
  
  mst_edgeweights <- E(mst_graph)$weight * 2.0
  mst_edgeweights_list[[mod]] <- mst_edgeweights
  
  # Update graph_list with weighted edges if needed
  graph_list[[mod]] <- graph_obj 
  
  cat("Processed vertex sizes, edge weights, and MST for module:", mod, "\n")
}

#pdf(file.path(paste0(plots_dir,"/WGCNA_Netwworks_BRMIC_NOCTX--Final.pdf")), width = 15, height = 15)

for (mod in modules_significant) {
  mst_graph <- mst_list[[mod]]
  vSizes_full <- vSizes_list[[mod]]
  names_df<- NULL
  
    # Access name table and graph from lists
  name_df <- as.data.frame(names(vSizes_full))
  
  # Separate 'new.names' column into gene_id and symbol using | as separator
  separated <- name_df %>%
    separate("names(vSizes_full)", into = c("gene_id", "symbol"), sep = "\\|")
  
  # Print checks
  cat("Module:", mod, "\n")
  cat("All gene_id == symbol:", all(separated$gene_id == separated$symbol), "\n")
  cat("NA in symbol:", sum(is.na(separated$symbol)), "\n")
  cat("Duplicated symbols:", sum(duplicated(separated$symbol)), "\n")
  cat("All gene_id == symbol again:", all(separated$gene_id == separated$symbol), "\n")
  
    # Assign gene_id back to graph vertex names
  names(vSizes_full) <- separated$gene_id
  
  vSizes_mst <- vSizes_full[ V(mst_graph)$name ]

  stopifnot(length(vSizes_mst) == vcount(mst_graph))
  edgeweights <- edgeweights_list[[mod]]
  edgeweights_mst <- mst_edgeweights_list[[mod]]
  
  # Community detection
  mst_communities <- cluster_fast_greedy(mst_graph)
  mst_clustering <- make_clusters(mst_graph, membership = mst_communities$membership)
  
  # Assign colors to vertices based on communities
  V(mst_graph)$color <- mst_communities$membership + 1
  
  
  # Plot with clustering layout and vertex/edge sizes
  plot(
    mst_clustering, mst_graph,
    layout = layout.kamada.kawai,
    edge.curved = TRUE,
    vertex.size = vSizes_mst,
    vertex.label.dist = -0.1,
    vertex.label.color = "black",
    asp = FALSE,
    vertex.label.cex = 1,
    edge.width = edgeweights_mst,
    edge.arrow.mode = 0,
    main = paste0(toupper(substr(mod,1,1)), substr(mod,2,nchar(mod)), " Network #1")
  )
  
  # Plot plain MST graph without clustering
  plot(
    mst_graph,
    layout = layout.kamada.kawai,
    edge.curved = TRUE,
    vertex.size = vSizes_mst,
    vertex.label.dist = -0.1,
    vertex.label.color = "black",
    asp = FALSE,
    vertex.label.cex = 1,
    edge.width = edgeweights_mst,
    edge.arrow.mode = 0,
    main = paste0(toupper(substr(mod,1,1)), substr(mod,2,nchar(mod)), " Network #2")
  )
}



#dev.off()

```

# Package Versions

```{r Save Package Version Info, echo=TRUE, message=TRUE, warning=FALSE}

projdir <- "/home/avm27/Documents/Raw_Sequencing_Data/BrainRegionMicroglia/RegionalMicroglialTranscriptomicsandEpigenomics"

#Record Package Versions Used in this analysis
index2_packages <- sort(
  unique(
    c(
      "AnnotationDbi",
      "BiocParallel",
      "clusterProfiler",
      "conflicted",
      "DESeq2",
      "dplyr",
      "dynamicTreeCut",
      "enrichplot",
      "fastcluster",
      "ggforce",
      "ggplot2",
      "igraph",
      "knitr",
      "limma",
      "org.Mm.eg.db",
      "ReactomePA",
      "readr",
      "stringr",
      "SummarizedExperiment",
      "tibble",
      "tidyr",
      "WGCNA",
      "workflowr"
    )
  )
)


# Retrieve Each Package Version
get_package_version <- function(package_name) {

  package_path <- find.package(
    package_name,
    quiet = TRUE
  )

  package_loaded <- package_name %in% loadedNamespaces()

  if (length(package_path) == 0L) {
    return(
      data.frame(
        package = package_name,
        installed = FALSE,
        loaded = FALSE,
        version = NA_character_,
        library_path = NA_character_,
        stringsAsFactors = FALSE
      )
    )
  }

  package_path <- package_path[[1]]

  data.frame(
    package = package_name,
    installed = TRUE,
    loaded = package_loaded,
    version = as.character(
      utils::packageVersion(
        package_name,
        lib.loc = dirname(package_path)
      )
    ),
    library_path = dirname(package_path),
    stringsAsFactors = FALSE
  )
}


# Collect Package and R Environment Versions
index2_package_versions <- do.call(
  rbind,
  lapply(
    index2_packages,
    get_package_version
  )
)

index2_environment_versions <- data.frame(
  R_version = paste(
    R.version$major,
    R.version$minor,
    sep = "."
  ),
  Bioconductor_version = if (
    requireNamespace("BiocManager", quietly = TRUE)
  ) {
    as.character(BiocManager::version())
  } else {
    NA_character_
  },
  platform = R.version$platform,
  stringsAsFactors = FALSE
)


# Save Version Records

utils::write.csv(
  index2_package_versions,
  file = paste0(projdir, "/code/RPackageVersions/index2_package_versions.csv"),
  row.names = FALSE
)

utils::write.csv(
  index2_environment_versions,
  file = paste0(projdir, "/code/RPackageVersions/index2_R_and_Bioconductor_versions.csv"),
  row.names = FALSE
)

capture.output(
  sessionInfo(),
  file = paste0(projdir, "/code/RPackageVersions/index2_sessionInfo.txt")
)



# Print Results
print(index2_environment_versions, row.names = FALSE)
print(index2_package_versions, row.names = FALSE)

```

# Session Info

```{r Print Session Info, echo=TRUE, message=TRUE, warning=FALSE}
sessionInfo()
```

