---
title: "Annotating Peaks For DESeq2"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: false
editor_options:
  chunk_output_type: console
---


```{r}
library(EnsDb.Mmusculus.v75)
library(ChIPseeker)
library(clusterProfiler)
library(AnnotationDbi)
library(org.Mm.eg.db)
library(TxDb.Mmusculus.UCSC.mm10.knownGene)
library(ChIPpeakAnno)
library(BSgenome.Mmusculus.UCSC.mm10)
library(seqinr)
library(dplyr)
library(GenomicRanges)
library(chromVAR)
library(plyr)
library(tibble)
library(data.table)
library(GenomicDistributions)

```

# Please Read Below

In order to run this analysis, you must first download the corresponding peak files from https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE277753. You will need all peak bed files as well as associated BAM files placed into a folder in the data subdirectory, which you will need to create.

To make this easier and less data intensive, we have provided a secondary option, which is to skip to "Skip to here if loading data" section of this script and utilize the RData we generated from the code below.

The third and final option is to download the peak count matrices from the GEO link above.

```{r Extract Significant Peaks, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

#setwd("/home/avm27/Documents/Raw_Sequencing_Data/BrainRegionMicroglia/RegionalMicroglialTranscriptomicsandEpigenomics")

projPath="data/CATD_Peaks"
mPeak = GRanges()


histL =c("PFC8-H3K27ac","PFC9-H3K27ac","STR8-H3K27ac", "STR9-H3K27ac", "HPP8-H3K27ac","HPP9-H3K27ac", "VTA8-H3K27ac","VTA9-H3K27ac", "CTX8-H3K27ac", "CTX9-H3K27ac", "PFC8-H3K27me3","PFC9-H3K27me3","STR8-H3K27me3", "STR9-H3K27me3", "HPP8-H3K27me3","HPP9-H3K27me3", "VTA8-H3K27me3", "VTA9-H3K27me3", "CTX8-H3K27me3", "CTX9-H3K27me3")


for(hist in histL){
    peakRes = read.table(paste0(projPath, "/", hist, "_dupMarked_merge_normalized_spikein_seacr_control.peaks.stringent.bed"), header = FALSE,
                         fill = TRUE)
    mPeak = GRanges(seqnames = peakRes$V1, IRanges(start = peakRes$V2, end = peakRes$V3), strand = "*") %>% append(mPeak, .)
}

masterPeak = GenomicRanges::reduce(mPeak)
masterPeak

```


```{r Annotate Peaks, eval=FALSE, include=FALSE}

annoData <- toGRanges(TxDb.Mmusculus.UCSC.mm10.knownGene, feature="gene")

annot <- annotatePeakInBatch(masterPeak, 
                             AnnotationData=annoData,
                             output="overlapping",
                             PeakLocForDistance = "start",
                             select = "first")

peak.anno = annotatePeak(peak = annot,
                         tssRegion = c(-5000, 5000),
                         TxDb = TxDb.Mmusculus.UCSC.mm10.knownGene,
                         annoDb = "org.Mm.eg.db",
                         level = "gene",
                         overlap = "TSS")


dfPA = as.data.frame(peak.anno)

masterPeak.anno <- makeGRangesFromDataFrame(dfPA,
                                            keep.extra.columns=TRUE,
                                            ignore.strand=FALSE,
                                            seqinfo=NULL,
                                            seqnames.field=c("seqnames", "seqname",
                                                             "chromosome", "chrom",
                                                             "chr", "chromosome_name",
                                                             "seqid"),
                                            start.field="start",
                                            end.field=c("end", "stop"),
                                            strand.field="strand",
                                            starts.in.df.are.0based=FALSE)

plotAnnoPie(peak.anno)

```


```{r Extract Fragments in Peaks, eval=FALSE, include=FALSE}

bamDir="data/CATD_BAMs"
bamFile= paste0(bamDir, "/", "PFC8-H3K27ac_merged_dupMarked_subsample.sorted.bam")
bamFile2= paste0(bamDir, "/", "PFC9-H3K27ac_merged_dupMarked_subsample.sorted.bam")
bamFile3= paste0(bamDir, "/", "STR8-H3K27ac_merged_dupMarked_subsample.sorted.bam")
bamFile4= paste0(bamDir, "/", "STR9-H3K27ac_merged_dupMarked_subsample.sorted.bam")
bamFile5= paste0(bamDir, "/", "HPP8-H3K27ac_merged_dupMarked_subsample.sorted.bam")
bamFile6= paste0(bamDir, "/", "HPP9-H3K27ac_merged_dupMarked_subsample.sorted.bam")
bamFile7= paste0(bamDir, "/", "VTA8-H3K27ac_merged_dupMarked_subsample.sorted.bam")
bamFile8= paste0(bamDir, "/", "VTA9-H3K27ac_merged_dupMarked_subsample.sorted.bam")
bamFile9= paste0(bamDir, "/", "CTX8-H3K27ac_merged_dupMarked_subsample.sorted.bam")
bamFile10= paste0(bamDir, "/", "CTX9-H3K27ac_merged_dupMarked_subsample.sorted.bam")
bamFile11= paste0(bamDir, "/", "PFC8-H3K27me3_merged_dupMarked_subsample.sorted.bam")
bamFile12= paste0(bamDir, "/", "PFC9-H3K27me3_merged_dupMarked_subsample.sorted.bam")
bamFile13= paste0(bamDir, "/", "STR8-H3K27me3_merged_dupMarked_subsample.sorted.bam")
bamFile14= paste0(bamDir, "/", "STR9-H3K27me3_merged_dupMarked_subsample.sorted.bam")
bamFile15= paste0(bamDir, "/", "HPP8-H3K27me3_merged_dupMarked_subsample.sorted.bam")
bamFile16= paste0(bamDir, "/", "HPP9-H3K27me3_merged_dupMarked_subsample.sorted.bam")
bamFile17= paste0(bamDir, "/", "VTA8-H3K27me3_merged_dupMarked_subsample.sorted.bam")
bamFile18= paste0(bamDir, "/", "VTA9-H3K27me3_merged_dupMarked_subsample.sorted.bam")
bamFile19= paste0(bamDir, "/", "CTX8-H3K27me3_merged_dupMarked_subsample.sorted.bam")
bamFile20= paste0(bamDir, "/", "CTX9-H3K27me3_merged_dupMarked_subsample.sorted.bam")


fragment_counts <- chromVAR::getCounts(c(bamFile, bamFile2, bamFile3, bamFile4, 
                                         bamFile5, bamFile6, bamFile7, bamFile8, 
                                         bamFile9, bamFile10, bamFile11, bamFile12, 
                                         bamFile13, bamFile14, bamFile15, bamFile16, 
                                         bamFile17, bamFile18, bamFile19, bamFile20), 
                                         masterPeak.anno, 
                                         paired = TRUE, by_rg = FALSE, format = "bam")


countMat = counts(fragment_counts)
head(countMat)

```

## Skip to here if loading data

```{r Load in Necessary R Data, eval=FALSE, include=FALSE}

#save(countMat, fragment_counts, file="/home/avm27/Documents/Raw_Sequencing_Data/BrainRegionMicroglia/RegionalMicroglialTranscriptomicsandEpigenomics/data/CATD_DESeq_Data/GeneratingPeaksinFragments.RData")

load("data/CATD_DESeq_Data/GeneratingPeaksinFragments.RData")

```


```{r Convert Fragments to Data Frame, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}

#' Convert a GenomicRanges into a data.table.
#'
#' @param GR A Granges object
#' @return A data.table object.
grToDt = function(GR) {
  DF=as.data.frame(elementMetadata(GR))
  if( ncol(DF) > 0) {
    DT = data.table(chr=as.vector(seqnames(GR)), 
                    start=start(GR), end=end(GR), DF)
  } else {
    DT = data.table(chr=as.vector(seqnames(GR)), 
                    start=start(GR), end=end(GR))
  }
  return(DT)
}


frag_counts_ft <- grToDt(fragment_counts)
dup_rows <- duplicated(frag_counts_ft$peak)
frag_counts_ft <- frag_counts_ft[!dup_rows, ]

```

```{r Assign Names and Peak Names to Gene Locations, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=TRUE}

rownames(countMat) = fragment_counts@rowRanges@elementMetadata@listData[["peak"]]

colnames(countMat) = paste(c("PFC8-H3K27ac","PFC9-H3K27ac",
                             "STR8-H3K27ac","STR9-H3K27ac", 
                             "HPP8-H3K27ac","HPP9-H3K27ac",
                             "VTA8-H3K27ac","VTA9-H3K27ac", 
                             "CTX8-H3K27ac", "CTX9-H3K27ac",
                             "PFC8-H3K27me3", "PFC9-H3K27me3",
                             "STR8-H3K27me3", "STR9-H3K27me3", 
                             "HPP8-H3K27me3", "HPP9-H3K27me3",
                             "VTA8-H3K27me3", "VTA9-H3K27me3",
                             "CTX8-H3K27me3", "CTX9-H3K27me3"))

countMatrownames <- data.frame(row.names(countMat))
countMatrownames$peak <- countMatrownames$row.names.countMat.
all(countMatrownames$peak == countMatrownames$row.names.countMat.)
newrownames <- merge(countMatrownames,frag_counts_ft,by="peak")
newrownames <- newrownames %>% dplyr::select(1,14,20,22:24)

dup_rows <- duplicated(newrownames$peak)
newrownames <- newrownames[!dup_rows, ]

countMat_df <- as.data.frame(as.matrix(countMat), rownames = FALSE)
countMat2 <- cbind(countMat_df, newrownames)

countMat_Anno <- countMat2
countMat_Anno_singleGenes <- countMat_Anno[,c(1:20,23,24,25)]

countMat_Anno_singleGenes_final <- plyr::ddply(countMat_Anno_singleGenes, "geneId", numcolwise(sum))

countMat_Anno_singleGenes_final$SYMBOL <- mapIds(x = org.Mm.eg.db,
                     keys = countMat_Anno_singleGenes_final$geneId,
                     column = "SYMBOL",
                     keytype = "ENTREZID",
                     multiVals = "first")

countMat_Anno_singleGenes_final2 <- countMat_Anno_singleGenes_final[complete.cases(countMat_Anno_singleGenes_final), ]
countMat_Anno_singleGenes_final_NOMATCH <- countMat_Anno_singleGenes_final[!complete.cases(countMat_Anno_singleGenes_final), ]

rownames(countMat_Anno_singleGenes_final2) <- countMat_Anno_singleGenes_final2$SYMBOL

countMat_Anno_singleGenes_final_ac <- countMat_Anno_singleGenes_final2[,c(2:11)]
countMat_Anno_singleGenes_final_me3 <- countMat_Anno_singleGenes_final2[,c(12:21)]
countMat_Anno_singleGenes_final_all <- countMat_Anno_singleGenes_final2[,c(2:21)]

dfac <- countMat_Anno_singleGenes_final_ac %>%
  rename_with(~ sub("-H3K27ac$", "", .x)) %>%
  dplyr::arrange(rownames(countMat_Anno_singleGenes_final_ac))


dfme3 <- countMat_Anno_singleGenes_final_me3 %>%
  rename_with(~ sub("-H3K27me3$", "", .x)) %>%
  dplyr::arrange(rownames(countMat_Anno_singleGenes_final_me3))

dfall <- countMat_Anno_singleGenes_final_all %>%
  dplyr::arrange(rownames(countMat_Anno_singleGenes_final_all))

colnames(dfall) <- sub("-", ".", colnames(dfall))

dfme3 <- dfme3 %>% 
  mutate(across(everything(), as.integer))
dfac <- dfac %>% 
  mutate(across(everything(), as.integer))
dfall <- dfall %>% 
  mutate(across(everything(), as.integer)) 

dfac_final_countmat <- dfac %>%
  rownames_to_column(var="gene_id")

dfme3_final_countmat <- dfme3 %>%
  rownames_to_column(var="gene_id")

dfall_final_countmat <- dfall %>%
  rownames_to_column(var="gene_id")

head(dfme3_final_countmat)
head(dfac_final_countmat)
head(dfall_final_countmat)

```

```{r Write Results for Use with DESeq2, eval=FALSE, include=FALSE}

#write.csv(dfac_final_countmat, "data/CATD_DESeq_Data/peak_count_matrix_CATD_Final_K27ac.csv", row.names = FALSE)
#write.csv(dfme3_final_countmat, "data/CATD_DESeq_Data/peak_count_matrix_CATD_Final_K27me3.csv", row.names = FALSE)
#write.csv(dfall_final_countmat, "data/CATD_DESeq_Data/peak_count_matrix_CATD_Final.csv", row.names = FALSE)

```

```{r SessionInfo, echo=TRUE}

sessionInfo()

```